### 2024-12-04 paper/paper.qmd
paper

---
title: "Understanding Subsidy Allocation in Toronto’s Child Care Centres: Insights from a Logistic Regression Analysis"
subtitle: "Non-Profit Governance, Program Participation, and Capacity Drive Funding Decisions"
author: 
  - Claire Ma
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: 2024.12.03
date-format: long
abstract: "This study examines the factors influencing government subsidy allocation to licensed child care centres in Toronto based on Licened child Care Centers from Open Data Toronto. By employing a logistic regression model, we found that non-profit governance, participation in the Canada-Wide Early Learning and Child Care (CWELCC) program, and larger capacity significantly increase a centre's likelihood of receiving subsidies. These findings highlight how funding priorities align with public goals to expand access to high-quality child care, especially for vulnerable populations. By uncovering patterns in subsidy distribution, this research provides critical insights for policymakers to ensure more equitable and effective resource allocation."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
library(opendatatoronto)
library(tidyverse)
library(readr)
library(dplyr)
library(tidyr)
library(stats)
library(ggplot2)
library(glmnet)
library(caret)
library(stats)
library(car)
library(broom)
library(pROC)
library(kableExtra)
library(knitr)
library(modelsummary)

```
# Introduction

Child care subsidies play a critical role in making high-quality early childhood education and care accessible to families and communities. In Toronto, licensed child care centres serve as essential providers, offering regulated and professional environments that support child development. Subsidies for licensed child care centres help close the affordability gap by offsetting the high costs of quality care, making it accessible to more families [@cleveland2009nonprofit]. These subsidies not only ease the financial burden on families but also ensure that children have access to nurturing environments that foster cognitive, social, and emotional growth during their formative years [@vines2020accessing]. Understanding the factors that determine which licensed centres receive subsidies is crucial for policymakers and stakeholders to promote equitable resource allocation and maximize the benefits of early childhood programs.
Licensed child care centres in urban settings like Toronto play a pivotal role in delivering high-quality, structured child care. These centres adhere to stringent regulations, ensuring compliance with standards for safety, staffing, and curriculum. Research highlights that children attending licensed centres, particularly those supported by subsidies, experience better developmental outcomes (Adams et al., 2013). Subsidized centres provide professional environments with trained educators, comprehensive programming, and age-appropriate resources, offering children a strong foundation for lifelong learning and success (Herbst, 2014). Subsidies are a cornerstone of this ecosystem, enabling licensed centres to cover operational costs, retain qualified staff, and maintain compliance with regulatory standards, all of which enhance the quality of care provided [@ryan2011impact].
Despite their importance, disparities in the allocation of subsidies remain a significant concern. Research indicates that centres in certain neighborhoods or serving specific populations may receive fewer subsidies, even when demand is high [@Johnson_Ryan_Brooks_2012]. Additionally, characteristics such as enrollment capacity, accreditation status, and program focus (e.g., infant care versus pre-kindergarten) often influence a centre’s eligibility and prioritization for funding [@vines2020accessin]. These discrepancies highlight the need for a data-driven approach to understanding and improving the distribution of subsidies among licensed child care centres, ensuring that resources are allocated equitably to maximize their impact.
This study utilizes the Toronto Open Data: Licensed Child Care Centres dataset to explore the factors that affect subsidy allocation to licensed centres. By analyzing variables such as ward, operating auspice (Commercial, Non Profit or Public), CWELCC, type of building, and total space, this research aims to uncover the question - “What factors influence the allocation of subsidies to licensed child care centres in Toronto?”. 
The findings will contribute to informing policies that promote equity and efficiency in subsidy allocation, ultimately supporting the goals of accessible and high-quality child care in Toronto. Additionally, these insights can serve as a valuable tool for child care centres to self-assess and enhance their eligibility for subsidies.

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Data Overview
The dataset used in this study was sourced from the [@Childrens_Services] made publicly available by the City of Toronto. This original raw dataset provides detailed information about licensed child care centres, including 20 variables capturing aspects of their location, operating auspice (e.g., non-profit, public, or commercial), space usage, building type, participation in government programs such as the Canada-Wide Early Learning and Child Care (CWELCC) system, and other operational details. These data offer valuable insights into the factors influencing subsidy allocation, a key policy tool for improving access to early childhood education and care. By translating real-world phenomena into structured data entries, this dataset enables a comprehensive exploration of equity and efficiency in child care funding. Detailed data collection analysis is in  appendix

```{r}
data <- read.csv("../data/02-analysis_data/cleaned_data.csv")
```

```{r}
#| label: tbl-overview
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Sample of Cleaned Data"
library(gt)

# Create a GT table with the first 10 rows
data %>%
  head(10) %>%
  gt() %>%
  tab_header(
    title = "Overview of Cleaned Data",
    subtitle = "Displaying the first 10 rows"
  )

```

```{r}
#| label: fig-subsidy
#| fig-cap: "Subsidy Allocation Distribution"
#| echo: false
#| message: false
#| warning: false
# Calculate percentages
data_summary <- data %>%
  group_by(subsidy) %>%
  summarise(count = n()) %>%
  mutate(percentage = round(100 * count / sum(count), 1))  # Calculate percentage

# Create the bar plot with percentage labels
plot1 <- ggplot(data_summary, aes(x = as.factor(subsidy), y = count)) +
  geom_bar(stat = "identity", fill = c("skyblue", "coral"), alpha = 0.8) +
  geom_text(aes(label = paste0(percentage, "%")), vjust = -0.5, size = 3) +  # Add percentage labels
  labs(
    title = "Distribution of Subsidy",
    x = "Subsidy (0 = No, 1 = Yes)",
    y = "Count"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 9),  # Reduce title size
    axis.title = element_text(size = 10),  # Reduce axis title size
    axis.text = element_text(size = 8)    # Reduce axis text size
  )

plot1

```

## Method
The dataset used for this study is the **`Licensed Child Care Centres dataset`**, sourced from the [@citeopendatatoronto] It provides detailed information about licensed child care centres in Toronto, capturing aspects such as their governance, capacity, infrastructure, and subsidy status. The original dataset consisted of 1071 records for all licensed child care centres within the city. For this analysis, the data underwent preprocessing to focus on variables relevant to the study, such as subsidy status, building type, CWELCC participation, total space, and operating auspice. These variables were retained to examine how different factors influence subsidy allocation. The dependent variable **`subsidy`**, originally recorded as "Yes"/"No," was encoded as 1 for subsidized and 0 for non-subsidized centres. Similarly, the **`cwelcc_flag`** variable was converted into a binary format (1 =Y, 0 =N). Categorical variables such as **`bldg_type`** and **`AUSPICE`** were consolidated to simplify analysis and address sparse categories. Additionally, missing and irrelevant records were removed to ensure the dataset was both accurate and meaningful for the research objectives.

The data for this study was systematically downloaded, cleaned, analyzed, and visualized using **`R`** [@citeR], a statistical programming language. The following are major packages used for this study:
**`opendatatoronto`**[@citeopendatatoronto]: Used to access and retrieve the Licensed Child Care Centres dataset directly from the City of Toronto's open data portal.
**`readr`** [@citereadr]: Simplified the import and parsing of raw data into R.
**`tidyverse`** [@citetidyverse]: Streamlined data manipulation, cleaning, and visualization processes.
**`dplyr`** [@citedplyr]: Provided tools for filtering, transforming, and summarizing the dataset effectively.
**`ggplot2`** [@citeggplot2]: Created powerful and flexible visualizations tailored to the analysis needs.
**`car`** [@citecar]: Used for diagnostic tools, including Variance Inflation Factor (VIF) tests, to assess multicollinearity.
**`caret`** [@citecaret]: Enabled the development, validation, and evaluation of machine learning models, including training-test splits and performance metrics.
**`glmnet`** (Friedman et al., 2010): Applied for fitting regularized regression models and feature selection.
**`stargazer`** [@citestagazer]: Generated formatted regression tables for outputs.
**`knitr`** [@citeknitr]: Dynamically integrated code, results, and plots into the final document for seamless reporting.
## Measurement
This analysis focuses on the following variables, with a specific emphasis on subsidy as the dependent variable:
`subsidy`: The binary dependent variable indicating whether a licensed child care centre receives a government subsidy.
1: The centre is subsidized.
0: The centre is not subsidized.
`ward`: `A numeric variable representing the ward number for child care centres.
`AUSPICE`: The operating auspice of the child care centre, describing its governance and operational model. Possible values include:
Non-Profit: Centres operated by non-profit organizations, often reinvesting surplus revenues into quality improvements.
Commercial: For-profit centres operated by private organizations.
Public: Centres run by public agencies or school boards.
`bldg_type`: The type of building where the child care centre operates, reflecting its infrastructure. Examples include:
bldg_typeCommercial Building
bldg_typeCommunity College/University     
bldg_typeCommunity Health Centre
bldg_typeCommunity Rec/Centre - Board Run
bldg_typeCommunity/Rec Centre - City
bldg_typeCommunity/Recreation Centre
bldg_typeHigh Rise Apartment
bldg_typeHospital/Health Centre
bldg_typeHouse
bldg_typeIndustrial Building
bldg_typeLow Rise Apartment
bldg_typeOffice Building
bldg_typeOther
bldg_typePlace of Worship
bldg_typePrivate Elementary School
bldg_typePublic (school closed)
bldg_typePublic Elementary Special
bldg_typePublic High School
bldg_typePublic Middle School
bldg_typePurpose Built
bldg_typeSynagogue
`cwelcc_flag`: A binary variable indicating participation in the Canada-Wide Early Learning and Child Care (CWELCC) program:
1: The centre participates in CWELCC, enabling reduced child care fees.
0: The centre does not participate in CWELCC.
`TOTSPACE`: A numerical variable representing the total licensed capacity (spaces available) for all age groups at a child care centre.
Detailed information about these variables’ information and data structure is presented in @tbl-overview.

The variables were carefully selected based on literature-supported relevance to subsidy allocation and their representation of real-world phenomena

@fig-relationbldgtype illustrates the distribution of subsidy status (1 = Subsidized, 0 = Not Subsidized) across various building types housing licensed child care centres. Notably, Public Schools, Purpose-Built Facilities, and Community Recreation Centres exhibit higher proportions of subsidized centres. These facilities are often designed to meet regulatory requirements for child care, including adequate space, safety standards, and accessibility, aligning closely with subsidy allocation policies [@cleveland2009nonprofit]. Conversely, building types such as Industrial Buildings, Private Elementary Schools, and Office Buildings show lower proportions of subsidized centres, likely due to infrastructure challenges or misalignment with subsidy eligibility criteria, such as limited accessibility or higher operational costs [@yan2011impact]. These patterns suggest that building type significantly influences subsidy distribution. Given the numerous categories of building types, a de tailed analysis is warranted to fully understand these trends.

```{r}
#| label: fig-relationbldgtype
#| fig-cap: "Proportional Distribution of Subsidy Status Across Building Types"
#| echo: false
#| message: false
#| warning: false
ggplot(data, aes(x = bldg_type, fill = as.factor(subsidy))) +
  geom_bar(position = "fill", alpha = 0.8) +
  scale_fill_manual(values = c("blue", "red")) +
  labs(
    x = "Building Type",
    y = "Proportion",
    fill = "Subsidy Status"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 9)
  )

```

@fig-relationAuspice illustrates the proportional distribution of subsidy status (1 = Subsidized, 0 = Not Subsidized) across the different operating auspices of licensed child care centres: Commercial Agency, Non-Profit Agency, and Other. Non-Profit Agencies and "Other" entities are predominantly subsidized, while Commercial Agencies display a more balanced distribution. This aligns with research indicating that non-profits rely heavily on subsidies to deliver public goods and services, as they often operate in markets with limited profitability [@hansmann1979role]. Conversely, commercial entities are less reliant on subsidies due to their revenue-driven models.The dominance of subsidies in the "Other" category suggests this group may include hybrid or public-private organizations aligned with specific government initiatives [@anheier2014nonprofit]. Such reliance reflects the strategic use of subsidies to support services underserved by the private market [@weisbrod2000profit].

```{r}
#| label: fig-relationAuspice
#| fig-cap: "Proportional Distribution of Subsidy Status by Auspice"
#| echo: false
#| message: false
#| warning: false
ggplot(data, aes(x = AUSPICE, fill = as.factor(subsidy))) +
  geom_bar(position = "fill", alpha = 0.8) +
  scale_fill_manual(values = c("blue", "red")) +
  labs(
    x = "Auspice",
    y = "Proportion",
    fill = "Subsidy Status"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for readability
    plot.title = element_text(size = 12),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 9)
  )

```
@fig-key a heatmap illustrates the correlations between three variables: TOTSPACE (likely representing total space or capacity), subsidy (indicating subsidy status or amount), and cwelcc_flag (potentially denoting eligibility for a specific program or funding).  The positive correlation between TOTSPACE and subsidy (0.25) suggests that larger facilities are modestly more likely to receive subsidies, reflecting their capacity to serve larger populations or provide greater public benefits.  This aligns with research indicating that larger organizations often have the resources and visibility to secure subsidies (Hansmann, 1980;  Salamon, 2002).  Additionally, the stronger correlation between subsidy and cwelcc_flag (0.48) highlights that subsidy allocation may target entities meeting specific programmatic or policy criteria, consistent with the literature emphasizing strategic targeting of subsidies to maximize societal impact (Weisbrod, 1998). The weaker correlation between TOTSPACE and cwelcc_flag (0.17) suggests that program eligibility is less dependent on size and more on qualitative factors like service type or demographic focus, which is supported by Anheier’s (2005) analysis of non-profit funding models.  Together, these correlations emphasize the nuanced role of subsidies in balancing operational scale and policy alignment, underscoring the importance of strategic allocation in public funding (Salamon, 1995).

```{r}
#| label: fig-key
#| fig-cap: "Correlation Heatmap of Key Variables: TOTSPACE, Subsidy, and CWELCC Flag"
#| echo: false
#| message: false
#| warning: false
library(ggcorrplot)
cor_matrix <- cor(data %>% select(TOTSPACE, subsidy, cwelcc_flag), use = "complete.obs")
ggcorrplot(cor_matrix, lab = TRUE)

```

# Model
## Model Specification
To investigate the factors influencing subsidy allocation to licensed child care centres, a reduced logistic regression model was specified. The dependent variable,`subsidy`, is a binary indicator representing whether a child care centre receives government subsidy (1 = subsidized, 0 = not subsidized). The model includes three key predictors:
`Operating Auspice (AUSPICE)`: A categorical variable indicating the governance model of the child care centre (e.g., Non-Profit Agency, Other). Non-profit agencies are hypothesized to be positively associated with subsidy allocation, consistent with previous research emphasizing their prioritization in funding schemes (Cleveland & Krashinsky, 2005).
`Participation in the CWELCC Program (cwelcc_flag)`: A binary variable capturing whether the centre participates in the Canada-Wide Early Learning and Child Care program (1 = participates, 0 = does not participate). Centres participating in this initiative are expected to have higher odds of receiving subsidies due to their alignment with government objectives of affordability and accessibility (Friendly & Ballantyne, 2022).
`Total Space (TOTSPACE)`: A continuous variable representing the number of licensed spaces available in the centre. Larger centres are hypothesized to have higher odds of subsidy allocation, as they can accommodate more families and align with policy goals of maximizing access (Forry et al., 2010).
The logistic regression model can be expressed mathematically as follows:
\[
\text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{CWELCC Participation}) + \beta_3 (\text{Total Space}) + \epsilon
\]

Where:
\begin{itemize}
    \item \( P(Y=1) \): The probability that a child care center receives a subsidy (\( Y=1 \)).
    \item \( \text{logit}(P(Y=1)) \): The log-odds of receiving a subsidy, defined as:
    \[
    \text{logit}(P(Y=1)) = \ln\left(\frac{P(Y=1)}{1 - P(Y=1)}\right)
    \]
    This transformation ensures that the predicted probabilities remain between 0 and 1.
\end{itemize}

### Parameters:
1. **\( \beta_0 \) (Intercept):**
   - Represents the baseline log-odds of subsidy allocation when all predictors are set to their reference categories or zero values.
   - It provides the starting point for predicting subsidy probabilities.

2. **\( \beta_1 (\text{Non-Profit Auspice}) \):**
   - Measures the effect of a center being operated as a non-profit compared to the baseline (e.g., commercial auspice) on the log-odds of subsidy allocation.
   - A positive \( \beta_1 \) increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.

3. **\( \beta_2 (\text{CWELCC Participation}) \):**
   - Captures the influence of participating in the Canada-Wide Early Learning and Child Care (CWELCC) program on the log-odds of subsidy allocation.

4. **\( \beta_3 (\text{Total Space}) \):**
   - Represents the effect of the number of licensed child care spaces (a continuous variable) on the log-odds of subsidy allocation.

5. **\( \epsilon \) (Error Term):**
   - Accounts for unexplained variation in the log-odds of subsidy allocation not captured by the predictors.

## Model Justification 
The logistic regression model was chosen for this analysis because it is well-suited to the binary nature of the dependent variable, subsidy status (1 = Subsidized, 0 = Not Subsidized). A logistic regression model using the binomial family is specifically designed to model dichotomous outcomes by estimating the log-odds of the event occurring as a linear function of predictor variables [@hosmer2013applied]. The binomial family is appropriate here because it assumes that the dependent variable follows a Bernoulli distribution, where each observation represents a binary outcome (subsidized or not subsidized). This ensures that the predicted probabilities remain between 0 and 1, aligning with the real-world constraints of the problem. Additionally, logistic regression provides interpretable coefficients, which indicate the direction and magnitude of the relationship between each predictor and the log-odds of subsidy allocation. This makes it particularly useful for guiding policy decisions, as coefficients can be directly converted into odds ratios for actionable insights [@peng2002introduction].
The ward variable was excluded because it lacked statistical significance and added redundancy, as its effects were captured by other predictors like CWELCC participation and total space. Additionally, ward had no strong theoretical justification as a direct determinant of subsidy allocation. The building type variable was removed due to high dimensionality, sparse representation in many categories, and statistical insignificance. Its effects are likely mediated by other variables, such as total space and auspice. Excluding it improved parsimony and interpretability.
The final model retained operating auspice, CWELCC participation, and total space, as these predictors are strongly supported by theory and data. This approach balances simplicity and accuracy, ensuring the model remains relevant for informing equitable subsidy allocation policies.

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# Encode categorical variables
data$AUSPICE <- as.factor(data$AUSPICE)
data$bldg_type <- as.factor(data$bldg_type)

# Split the data into training and testing sets
set.seed(1008047418)
train_index <- createDataPartition(data$subsidy, p = 0.7, list = FALSE)
train_data <- data[train_index, ]
test_data <- data[-train_index, ]

# Fit logistic regression model
log_model <- glm(subsidy ~ ., data = train_data, family = binomial)

# Summary of the model
summary(log_model)

```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# Stepwise selection based on AIC
step_model_aic <- step(log_model, direction = "both", trace = TRUE)

# Summary of models
summary(step_model_aic)  # AIC-based selected model
```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# Create a binary variable for "Non Profit Agency"
train_data$AUSPICE_NonProfit <- ifelse(train_data$AUSPICE == "Non Profit Agency", 1, 0)

# Refit the model with the binary variable for AUSPICE
reduced_model_re2 <- glm(formula = subsidy ~ AUSPICE_NonProfit + bldg_type + cwelcc_flag + TOTSPACE, 
                       family = binomial, data = train_data)

# Summary of the updated model
summary(reduced_model_re2)

```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}

# Refit the best aic model
reduced_model_re <- glm(formula = subsidy ~ AUSPICE + bldg_type + cwelcc_flag + TOTSPACE, 
    family = binomial, data = train_data)
summary(reduced_model_re)

```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# Refit model by removing non-significant variables
reduced_model_2 <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE, 
    family = binomial, data = train_data)
summary(reduced_model_2)
```
## Model Assumptions
To ensure the validity of the logistic regression model, several key assumptions were assessed, including independence of observations, the appropriateness of a binary outcome, the linearity of predictors with the logit and absence of multicollinearity. The analysis integrates results from visual diagnostics, multicollinearity tests, and statistical measures.
1. Independence of Observations
The logistic regression model assumes that the observations are independent of each other. In this analysis, each data point corresponds to an individual child care center, ensuring independence. There is no clustering or repeated measures within the dataset, which validates this assumption.
2. Binary Outcome
The logistic regression model assumes a binary dependent variable. In this case, the outcome variable, `subsidy`, is binary, indicating whether a child care center receives a subsidy (1 = Subsidized, 0 = Not Subsidized). This aligns with the model's requirement, ensuring the suitability of the binomial family for fitting the data.
3. Linearity of Predictors with the Logit
The @fig-cr The component + residual plots evaluate the linearity of the continuous variables and the relationship between categorical predictors and the logit transformation.
graph

```{r}
#| label: fig-cr
#| fig-cap: "CR Plot for Linearity Chekck"
#| echo: false
#| message: false
#| warning: false
crPlots(reduced_model_2)  # Generate Component + Residual plots
```
`TOTSPACE`: The relationship between the total space (TOTSPACE) and the logit appears approximately linear, as indicated by the flat, consistent pattern of residuals around the horizontal axis. This supports the assumption of linearity.
`CWELCC Flag`: The plot for CWELCC participation shows a horizontal trend, suggesting no significant deviation from linearity. The data support the inclusion of this variable as a binary predictor.
`AUSPICE`: The residual patterns for categorical levels of AUSPICE (e.g., "Commercial Agency" and "Other") indicate distinct clusters with consistent variability. This suggests the categorical nature of this variable does not violate linearity assumptions.
Overall, the visual inspection suggests that the linearity assumption for the predictors with the logit is met.

4. Multicollinearity Assessment
Variance Inflation Factor (VIF):
To assess multicollinearity among the predictors, the VIF values for the reduced model variables were calculated.

```{r}
# Calculate VIF
vif_values <- vif(reduced_model_2)
```

All VIF values are below 2, well within the acceptable threshold of 5, indicating minimal multicollinearity among the predictors. The independence of the predictors ensures the stability of the coefficient estimates.

## Alternative Models
Alternative models like decision trees and random forests were considered but were found less interpretable for policy-focused analyses. Logistic regression was chosen for its balance of simplicity, interpretability, and effectiveness.

#Result 
The logistic regression model’s performance metrics are presented in @tbl-coefresult.

```{r}
#| label: tbl-coefresult
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: "Regression Result"
# Regression table with standard errors and p-values
model_list <- list(
  "Final Model" = reduced_model_2
)

modelsummary(
  model_list, 
  output = "markdown", 
  statistic = c("std.error", "p.value")
)

```
The regression model reveals several key observations regarding the predictors and overall goodness of fit.  The intercept, estimated at -4.967, represents the baseline log-odds of the outcome when all predictors are at their reference or zero level.  While not directly interpretable, it serves as a baseline reference for the model.  Among the predictors, the AUSPICE: Non-Profit Agency category significantly increases the log-odds of the outcome, with an estimate of 2.883 and a small standard error of 0.234, indicating a strong and reliable positive effect.  However, the AUSPICE: Other category shows an unusually large coefficient (18.772) paired with a very high standard error (686.847), suggesting instability.  The CWELCC Flag variable also exhibits a strong and reliable positive effect, with an estimate of 3.156 and a standard error of 0.436, indicating that being flagged as CWELCC significantly increases the log-odds of the outcome.  Additionally, the TOTSPACE variable has a small but statistically significant effect, with an estimate of 0.014 and a low standard error of 0.003, reflecting robustness.
@fig-cp further visualizes the significance of predictors.

```{r}
#| label: fig-cp
#| fig-cap: "Coefficient Plot"
#| echo: false
#| message: false
#| warning: false

# Extract coefficients and confidence intervals
tidy_model <- broom::tidy(reduced_model_2, conf.int = TRUE)

# Highlight significant coefficients
tidy_model <- tidy_model %>%
  mutate(significant = ifelse(conf.low > 0 | conf.high < 0, "Significant", "Not Significant"))

# Plot with enhancements
ggplot(tidy_model, aes(x = estimate, y = reorder(term, abs(estimate)), color = significant)) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
  scale_color_manual(values = c("Significant" = "red", "Not Significant" = "black")) +
  labs(
    title = "Coefficient Plot",
    x = "Coefficient Estimate",
    y = "Predictor Variables",
    color = "Significance"
  ) +
  theme_minimal()
```
In terms of model fit, the dataset includes 750 observations, and the model's AIC (528.1) and BIC (551.2) suggest a reasonable balance between goodness of fit and complexity, as lower values are generally preferred [@burnhammodel].  The log-likelihood of -259.035 also supports an adequate fit, with a higher (less negative) value indicating better alignment between the model and the data.  Finally, the RMSE of 0.32 reflects the model's predictive accuracy, with a low value indicating that the model's predictions closely match the observed data.  Overall, the model performs well but may require refinement, particularly in addressing instability in the AUSPICE: Other variable.

The evaluation of the logistic regression model shows strong performance based on McFadden’s R^2 and the Area Under the Receiver Operating Characteristic Curve (AUC). McFadden’s R^2 which is a pseudo-R^2 metric specifically designed for logistic regression, was calculated as 0.454. This value suggests that the model explains 45.4% of the variance in the outcome variable, indicating a well-fitting model. McFadden [@mcfadden1972conditional] proposed this metric as a reliable measure for logistic regression, where values between 0.2 and 0.4 are considered indicative of a good model fit, and values above 0.4 demonstrate an excellent fit. Thus, the model's R^2 value strongly supports its utility in predicting the outcome.
```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# Calculate log-likelihood of the fitted model
log_likelihood_fitted <- logLik(reduced_model_2)
# Fit the null model (model with intercept only)
null_model <- glm(subsidy ~ 1, data = train_data, family = binomial)
log_likelihood_null <- logLik(null_model)
# McFadden's R-squared
mcfadden_r2 <- 1 - as.numeric(log_likelihood_fitted / log_likelihood_null)
# Print the result
print(paste("McFadden's R-squared:", round(mcfadden_r2, 6)))
```

```{r}
#| label: fig-roc
#| fig-cap: "ROC Curve for Model Performance"
#| echo: false
#| message: false
#| warning: false

# ROC Curve and AUC
roc_curve <- roc(test_data$subsidy, predict(reduced_model_2, newdata = test_data, type = "response"))
plot(roc_curve, main = "ROC Curve")
auc(roc_curve)

```
The ROC curve in @fig-roc shown further validates the model's classification ability, with an AUC of 0.8998. An AUC value close to 1 indicates excellent discriminative power, where the model effectively separates true positives from false positives. The AUC of 0.8998 places this model on the borderline of very good and excellent discrimination, underscoring its robust predictive capacity.

```{r}
#| label: fig-pvo
#| fig-cap: " Predicted vs. Observed Probability"
#| echo: false
#| message: false
#| warning: false
# Generate predicted probabilities for the test dataset
test_data$predicted_prob <- predict(reduced_model_2, newdata = test_data, type = "response")

# Predicted vs. Observed Scatterplot
ggplot(test_data, aes(x = predicted_prob, y = subsidy)) +
  geom_jitter(width = 0.02, height = 0.02, alpha = 0.6, color = "blue") +
  geom_smooth(method = "loess", color = "red", se = FALSE) +
  labs(
    x = "Predicted Probability",
    y = "Observed Outcome"
  ) +
  theme_minimal()
```
@fig-pvo provides a visual representation of the alignment between the predicted probabilities generated by the logistic regression model and the actual observed binary outcomes. This diagnostic tool is crucial for assessing the model's calibration and predictive accuracy, as emphasized by Harrell [@harrell2012regression]. The x-axis shows the predicted probabilities ranging from 0 to 1, while the y-axis represents the observed outcomes, where 0 indicates the absence of an event and 1 indicates its presence. The red diagonal line serves as the reference for perfect calibration, where predicted probabilities perfectly match observed outcomes.
The clustering of blue points near 0 and 1 along the y-axis indicates that the model effectively distinguishes between the two classes, a key goal in binary classification modeling. This observation aligns with the high AUC value of 0.8998 observed in the ROC curve, which demonstrates the model’s excellent discriminative ability. Additionally, points near the diagonal line further suggest strong calibration, where the predicted probabilities closely align with actual outcomes. The concentration of blue points at the extremes of 0 and 1 highlights that the model makes confident and accurate predictions in many cases
However, some dispersion is observed at lower predicted probabilities, particularly around 0.25 and 0.5. These deviations may reflect cases where the model struggles to classify outcomes or makes less confident predictions. Such discrepancies could indicate areas where further refinement of the model or predictors is necessary. These deviations could also be linked to specific subgroups or predictor interactions, necessitating additional diagnostics or recalibration, as suggested by Steyerberg et al. [@steyerberg2010assessing].
Overall, this graph demonstrates that the model is well-calibrated and effective in its predictions, with minor limitations at lower probability levels. The close alignment of predictions with observed outcomes supports the model's reliability in classification tasks. This interpretation aligns with other metrics, such as McFadden’s R2R2 [@mcfadden1972conditional] and AUC, which indicate robust overall model performance while pointing to opportunities for refinement. Including this visualization in the results section provides a clear and data-driven assessment of the model's strengths and areas for potential improvement.

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}

# Create a coefficient table
model_list <- list(
  "Full Model" = log_model,
  "AIC Model" = reduced_model_re,
  "Simplified Model" = reduced_model_2
)

# Customize the table to display only AIC and Deviance
modelsummary(
  model_list,
  output = "markdown",
  gof_map = c("AIC", "Deviance")  # Include only AIC and Deviance in the table
)

```

#Discussion

Subsidy allocation to licensed child care centres in Toronto addresses the critical issue of affordability, making high-quality early childhood education accessible to more families as licensed centres must meet strict safety, staffing, and programming standards, which foster children’s cognitive, social, and emotional growth [@cleveland2009nonprofit]. Without subsidies, the cost of regulated care can be prohibitive, particularly for low-income households. This paper undertakes a detailed examination of the factors influencing subsidy allocation to licensed child care centres in Toronto, leveraging the City of Toronto's Licensed Child Care Centres dataset from Open Data porta, which includes detailed information about 1,071 licensed centers[@citeopendatatoronto]. This study employs a logistic regression model-binomial family to identify relationships between key predictor variables and the binary dependent variable – receiving subsidies.

The dataset underwent meticulous preprocessing to ensure reliability and accuracy for analysis. This involved several key steps of data cleaning, variable transformation and training-test Split. Initially, variables of Operating auspice(AUSPICE), ward, building type(bldg_type), total space(TOTSPACE) and participation status in programs(cwelcc_flag) were chosen based their relevance and practical influence subsidy outcomes and forecasting supported by scholar literatures. After fitting and improving the model using stepwise selection based on the Akaike Information Criterion (AIC), non-significant variables (ward and building type(bldg_type)) were removed. The final model retained Operating Auspice, CWELCC Participation, and Total Licensed Capacity as key predictors. The assumptions underpinning the logistic regression model were thoroughly validated, ensuring its statistical rigor and reliability. Independence of observations was confirmed, as each data point corresponds to a unique child care centre, eliminating concerns of clustering or dependency. Linearity between continuous predictors, such as Total Licensed Capacity, and the logit transformation was validated through component + residual plots, which revealed consistent patterns, supporting the appropriateness of the model. Additionally, multicollinearity was minimized, with Variance Inflation Factor (VIF) values well below the critical threshold of 5, indicating that the predictors are independent and the coefficient estimates are stable. Together, these validations affirm the robustness of the model and its suitability for the analysis.

The result coefficients in table the logistic regression model provide a detailed understanding of how key predictors influence the likelihood of subsidy allocation to licensed child care centres in Toronto. By measuring the change in log-odds of subsidy allocation associated with each predictor, the model quantifies the relative importance of governance models, program participation, and operational capacity. The coefficient for Non-Profit Auspice emerged as strongly positive and statistically significant, indicating that non-profit child care centres are far more likely to receive subsidies than commercial or public centres. This is reflective of policy priorities that favor organizations with a social mission over those with profit-oriented objectives. Non-profits are often viewed as better aligned with public goals of equity and accessibility, as they reinvest surplus revenues into improving care quality rather than distributing profits [@hansmann1980role]. This is consistent with research by [@salamon1995partners], who noted that non-profits often fill critical gaps in the provision of public services, making them natural candidates for targeted funding. In the context of child care, non-profits may also be more likely to serve economically vulnerable populations, further justifying their prioritization for subsidies. The odds ratio derived from this coefficient underscores the strength of this relationship, suggesting that non-profit centres are several times more likely to receive subsidies compared to commercial centres. Participation in the Canada-Wide Early Learning and Child Care (CWELCC) program was the most significant predictor in the model, with a highly positive coefficient. This result highlights the critical role of policy alignment in subsidy allocation. Centres participating in CWELCC demonstrate compliance with national and provincial affordability initiatives, making them high-priority recipients of government funding. Research by [@bennett2011working] supports this finding, emphasizing that early childhood programs aligned with broader governmental objectives are often better positioned to secure resources. The odds ratio for CWELCC participation indicates that such centres are substantially more likely to receive subsidies, which is consistent with targeted funding strategies aimed at expanding access to high-quality, affordable child care [@kaga2010caring]. Total Licensed Capacity (TOTSPACE), representing the number of spaces a centre is licensed to operate, was another important predictor, although its coefficient was smaller in magnitude compared to governance and CWELCC participation. This positive coefficient suggests that larger centres are more likely to receive subsidies, likely due to their capacity to serve more families and their operational scale. Larger centres can achieve economies of scale and often have greater visibility, making them attractive candidates for public funding [@weisbrod1998profit]. However, the smaller effect size of this variable indicates that capacity alone is insufficient to determine subsidy allocation. This finding aligns with [@penn2011quality], who argues that while capacity is an important practical consideration, other factors—such as governance and programmatic alignment—carry more weight in funding decisions. Interpreting these coefficients through odds ratios further clarifies their impact. For instance, the odds ratio for CWELCC participation suggests that centres in the program are several times more likely to receive subsidies compared to non-participating centres, holding other factors constant. Similarly, the odds ratio for non-profit governance reinforces the preferential treatment of non-profits in subsidy allocation policies. These findings align with the broader literature on public funding, which emphasizes the strategic use of subsidies to support centres that meet both operational and policy criteria [@penn2011quality]. The statistical significance of these coefficients underscores their reliability as shown in figure. Variables such as Non-Profit Auspice and CWELCC Participation demonstrated small standard errors and strong significance levels, reinforcing their influence on subsidy allocation. In contrast, variables with less consistent effects, such as certain building types or governance categories in the "Other" category, exhibited instability, suggesting that their role in funding decisions may be more context-specific or secondary. The model's findings highlight a strategic approach to subsidy allocation, where funding decisions are guided by alignment with policy goals, operational capacity, and governance structures.

The logistic regression model applied in this research proves to be an ideal tool for analyzing subsidy allocation to licensed child care centres in Toronto, particularly due to its capacity to handle binary outcomes effectively. By modeling the log-odds of an event, logistic regression ensures predicted probabilities remain between 0 and 1, aligning seamlessly with the binary nature of the dependent variable—whether a centre receives a subsidy. This feature makes the model both statistically appropriate and easy to interpret. A notable strength of the model lies in its interpretability. Coefficients can be transformed into odds ratios, providing a clear understanding of how predictors influence the likelihood of receiving subsidies. For example, the positive coefficients for Non-Profit Auspice and CWELCC Participation underscore their significant, policy-relevant impact on subsidy distribution. This clarity makes the model particularly valuable for stakeholders and policymakers who require actionable and easily communicated insights. The model's performance metrics further demonstrate its effectiveness. A McFadden's R² value of 0.454 indicates that the model explains a substantial portion of the variance in subsidy allocation. Additionally, the Area Under the Curve (AUC) of 0.8998 highlights the model’s exceptional discriminative ability, confirming its capacity to accurately differentiate between subsidized and non-subsidized centres. The low Root Mean Squared Error (RMSE) of 0.32 further attests to the model’s strong predictive performance. Together, these metrics validate the model's reliability and robustness. Another key advantage of logistic regression is its simplicity compared to more complex approaches such as random forests or decision trees. While those alternatives might offer marginally higher predictive power, they lack the transparency and interpretability required for policy-focused research. Logistic regression strikes a critical balance between accuracy and clarity, making it a practical choice for guiding equitable subsidy allocation strategies. Moreover, the flexibility of logistic regression allows for extensions to explore more intricate relationships. For instance, incorporating interaction terms or temporal data could provide deeper insights while maintaining the model's usability. This adaptability ensures the model remains relevant and applicable as policy environments evolve.

Our model, while effective, has several limitations that warrant consideration. One of the primary limitations is its reliance on the assumption of linearity between predictors and the log-odds of the outcome. Although this assumption is often reasonable, it may oversimplify complex, non-linear relationships that can exist in real-world phenomena such as subsidy allocation. As [@harrell2015regression] notes, failing to capture these non-linear relationships can lead to biased estimates and limit the model’s predictive power. Another limitation is the model’s dependence on correct specification of predictors. Excluding relevant variables or including irrelevant ones in initial variable selection can result in omitted variable bias or overfitting, respectively. Additionally, the model does not inherently account for higher-order interactions unless explicitly included.  For instance, the combined effect of Non-Profit Auspice and CWELCC Participation could provide valuable insights into how policy and governance jointly influence subsidy allocation. [@hosmer2013applied] highlight that logistic regression can oversimplify complex relationships if interaction terms are not considered, potentially leading to incomplete conclusions. Finally, the static nature of the model is another drawback.  Logistic regression provides a snapshot of relationships at a single point in time, failing to capture temporal dynamics or policy changes that can influence subsidy allocation over time.  As Singer and [@singer2003applied] suggest, incorporating longitudinal data could provide a more nuanced understanding of how these relationships evolve.

Future studies could address the limitations of this research by adopting more advanced modeling techniques and incorporating additional data to better capture the complexities of subsidy allocation. Introducing non-linear models or machine learning approaches, such as random forests or gradient boosting, could uncover hidden patterns and interactions between predictors that logistic regression may overlook. Additionally, exploring interaction terms, such as the joint effects of governance models and program participation, could provide more nuanced insights into policy impacts. Longitudinal data would be particularly valuable for understanding how subsidy allocation evolves over time, especially in response to policy changes or shifts in economic conditions. Incorporating time-series or panel data analysis could reveal temporal dynamics and provide a richer understanding of causal relationships. Geographic disparities, noted but not deeply explored in this study, could also be addressed using spatial regression or multilevel models to account for regional clustering and unobserved local factors influencing subsidy distribution. Finally, integrating additional predictors, such as demographic variables, socio-economic indicators, or quality ratings of child care centres, could enhance the explanatory power of future models. These enhancements would provide a more comprehensive view of subsidy allocation and inform strategies to ensure equitable and effective distribution of resources.

# Appendix A: Observational Data Methodology for Licensed Child Care Centres in Toronto

## A.1 Population, Frame, and Sample
A.1.1 Population
The population includes all licensed child care centres in Toronto as recorded in the publicly available dataset provided by Open Toronto. This population aligns with studies on regulated child care, such as [@morrissey2010childcare], which emphasizes the role of licensing in ensuring quality and safety in early childhood education. However, the dataset excludes unlicensed child care providers, limiting its scope. 
Represented Groups: Centres adhering to provincial licensing requirements, as emphasized by Cleveland and Krashinsky [@cleveland2003benefits], who note that licensed care is generally associated with higher quality standards.
Excluded Groups: Informal and unlicensed providers, which disproportionately to lower-income families and those in rural or underserved urban areas.
A.1.2 Frame
The dataset represents a comprehensive census of licensed child care centres, reflecting administrative records compiled by the city. 
Strengths: Comprehensive coverage reduces selection bias and enhances geographic representativeness.
Limitations: Static data may fail to capture temporal variations or operational changes, a common limitation noted in administrative datasets.
A.1.3 Sample
The dataset uses census sampling of licensed child care centres, ensuring inclusion of all facilities within the licensing framework.
Advantages: Census data minimizes sampling error and provides a reliable basis for spatial and capacity analysis.
Drawbacks: Lack of informal care data may lead to underrepresentation of actual child care resources, echoing findings by [@tekin2007childcare] that informal care plays a critical role in many families’ child care arrangements.

## A.2 Data Collection Methodology
A.2.1 Observational Data Compilation
The dataset is derived from municipal administrative records, which are considered reliable for policy analysis [@cleveland2003benefits]. Licensing authorities collect this data as part of routine compliance monitoring, ensuring high accuracy.
Strengths: Administrative data is less prone to recall bias compared to survey data.
Weaknesses: Lack of qualitative insights into service quality or user satisfaction.
A.2.2 Non-response Handling
While the dataset does not involve survey non-response, its exclusion of unlicensed providers creates a systematic gap. Research by Fuller et al. [@fuller1996family] shows that informal care often fills critical voids in underserved areas, and its exclusion may understate the full scope of child care provision.

## A.3 Sampling Approach and Trade-offs
A.3.1 Strengths
Comprehensive Coverage: Census sampling ensures no licensed centres are omitted.
Geospatial Precision: Geographic coordinates support advanced spatial analysis, aligning with studies like [@larsen2015accessibility] on urban accessibility.
High Validity: Licensing records provide robust validity, as they are subject to regulatory verification [@cleveland2003benefits].
A.3.2 Limitations
Exclusion of Informal Care: Research by Morrissey [@morrissey2010childcare] highlights that informal care is often preferred for flexibility or affordability, making its exclusion a significant limitation.
Static Nature: The lack of longitudinal data limits the ability to analyze trends.
Regulatory Bias: Centers excluded due to non-compliance may disproportionately represent marginalized communities.

## A.4 Observational Bias and Measurement Challenges
A.4.1 Observational Bias
Biases inherent in observational datasets include selection bias (due to licensing criteria) and survivorship bias (exclusion of closed centres). 
A.4.2 Measurement Challenges
Geographic Aggregation: Aggregating data to broader areas can obscure micro-level disparities.
Capacity Limitations: Reported capacities may not reflect actual utilization or unmet demand, as noted by [@blau2006preschool].

## A.5 Methodological Enhancements and Recommendations
A.5.1 Enhancements
Incorporating Temporal Data: Adding longitudinal data could enable trend analysis, echoing the approach of [@fuller1996family].
Integration with Demographics: Linking with census data would allow for equity analysis, consistent with the methodology used by [@larsen2015accessibility].
A.5.2 Recommendations
Addressing Informal Care: Future studies should integrate data from community surveys to include informal providers, as suggested by [@morrissey2010childcare].
Dynamic Updates: Regular updates to administrative records would enhance relevance, a recommendation supported.
Geospatial Enhancements: Including data on transit access or neighborhood socioeconomic conditions could enrich spatial analyses, aligning with findings by [@tekin2007childcare]

# References

### 2024-12-04 paper/paper.tex
paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{anyfontsize}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{rotating}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={First author; Another author},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
\url{https://github.com/RohanAlexander/starter_folder}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{First author \and Another author}
\date{December 3, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}

\section{Introduction}\label{introduction}

Child care subsidies play a critical role in making high-quality early
childhood education and care accessible to families and communities. In
Toronto, licensed child care centres serve as essential providers,
offering regulated and professional environments that support child
development. Subsidies for licensed child care centres help close the
affordability gap by offsetting the high costs of quality care, making
it accessible to more families (Cleveland and Krashinsky 2009). These
subsidies not only ease the financial burden on families but also ensure
that children have access to nurturing environments that foster
cognitive, social, and emotional growth during their formative years
(Vines 2020). Understanding the factors that determine which licensed
centres receive subsidies is crucial for policymakers and stakeholders
to promote equitable resource allocation and maximize the benefits of
early childhood programs. Licensed child care centres in urban settings
like Toronto play a pivotal role in delivering high-quality, structured
child care. These centres adhere to stringent regulations, ensuring
compliance with standards for safety, staffing, and curriculum. Research
highlights that children attending licensed centres, particularly those
supported by subsidies, experience better developmental outcomes (Adams
et al., 2013). Subsidized centres provide professional environments with
trained educators, comprehensive programming, and age-appropriate
resources, offering children a strong foundation for lifelong learning
and success (Herbst, 2014). Subsidies are a cornerstone of this
ecosystem, enabling licensed centres to cover operational costs, retain
qualified staff, and maintain compliance with regulatory standards, all
of which enhance the quality of care provided (Ryan et al. 2011).
Despite their importance, disparities in the allocation of subsidies
remain a significant concern. Research indicates that centres in certain
neighborhoods or serving specific populations may receive fewer
subsidies, even when demand is high (Johnson, Ryan, and Brooks‐Gunn
2012). Additionally, characteristics such as enrollment capacity,
accreditation status, and program focus (e.g., infant care versus
pre-kindergarten) often influence a centre's eligibility and
prioritization for funding (\textbf{vines2020accessin?}). These
discrepancies highlight the need for a data-driven approach to
understanding and improving the distribution of subsidies among licensed
child care centres, ensuring that resources are allocated equitably to
maximize their impact. This study utilizes the Toronto Open Data:
Licensed Child Care Centres dataset to explore the factors that affect
subsidy allocation to licensed centres. By analyzing variables such as
ward, operating auspice (Commercial, Non Profit or Public), CWELCC, type
of building, and total space, this research aims to uncover the question
- ``What factors influence the allocation of subsidies to licensed child
care centres in Toronto?''. The findings will contribute to informing
policies that promote equity and efficiency in subsidy allocation,
ultimately supporting the goals of accessible and high-quality child
care in Toronto. Additionally, these insights can serve as a valuable
tool for child care centres to self-assess and enhance their eligibility
for subsidies.

Telegraphing paragraph: The remainder of this paper is structured as
follows. Section~\ref{sec-data}\ldots.

\section{Data}\label{sec-data}

\subsection{Data Overview}\label{data-overview}

The dataset used in this study was sourced from the
(\textbf{Childrens\_Services?}) made publicly available by the City of
Toronto. This original raw dataset provides detailed information about
licensed child care centres, including 20 variables capturing aspects of
their location, operating auspice (e.g., non-profit, public, or
commercial), space usage, building type, participation in government
programs such as the Canada-Wide Early Learning and Child Care (CWELCC)
system, and other operational details. These data offer valuable
insights into the factors influencing subsidy allocation, a key policy
tool for improving access to early childhood education and care. By
translating real-world phenomena into structured data entries, this
dataset enables a comprehensive exploration of equity and efficiency in
child care funding. Detailed data collection analysis is in appendix

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\StringTok{"../data/02{-}analysis\_data/cleaned\_data.csv"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tbl-overview}Sample of Cleaned Data}

\centering{

\caption*{
{\large Overview of Cleaned Data} \\ 
{\small Displaying the first 10 rows}
} 
\fontsize{12.0pt}{14.4pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}rllrrr}
\toprule
ward & AUSPICE & bldg\_type & cwelcc\_flag & TOTSPACE & subsidy \\ 
\midrule\addlinespace[2.5pt]
3 & Non Profit Agency & Public Elementary School & 1 & 164 & 1 \\ 
8 & Non Profit Agency & Public Elementary School & 1 & 83 & 1 \\ 
25 & Non Profit Agency & Catholic Elementary School & 1 & 102 & 1 \\ 
10 & Non Profit Agency & Other & 1 & 65 & 1 \\ 
20 & Non Profit Agency & High Rise Apartment & 1 & 26 & 1 \\ 
24 & Non Profit Agency & Community College/University & 1 & 62 & 1 \\ 
6 & Non Profit Agency & Public High School & 1 & 49 & 1 \\ 
24 & Commercial Agency & High Rise Apartment & 1 & 46 & 1 \\ 
19 & Non Profit Agency & Public Elementary School & 1 & 51 & 1 \\ 
8 & Non Profit Agency & Public Elementary School & 1 & 153 & 1 \\ 
\bottomrule
\end{tabular*}

}

\end{table}%

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-subsidy-1.pdf}

}

\caption{\label{fig-subsidy}Subsidy Allocation Distribution}

\end{figure}%

\subsection{Method}\label{method}

The dataset used for this study is the
\textbf{\texttt{Licensed\ Child\ Care\ Centres\ dataset}}, sourced from
the (Gelfand 2022) It provides detailed information about licensed child
care centres in Toronto, capturing aspects such as their governance,
capacity, infrastructure, and subsidy status. The original dataset
consisted of 1071 records for all licensed child care centres within the
city. For this analysis, the data underwent preprocessing to focus on
variables relevant to the study, such as subsidy status, building type,
CWELCC participation, total space, and operating auspice. These
variables were retained to examine how different factors influence
subsidy allocation. The dependent variable \textbf{\texttt{subsidy}},
originally recorded as ``Yes''/``No,'' was encoded as 1 for subsidized
and 0 for non-subsidized centres. Similarly, the
\textbf{\texttt{cwelcc\_flag}} variable was converted into a binary
format (1 =Y, 0 =N). Categorical variables such as
\textbf{\texttt{bldg\_type}} and \textbf{\texttt{AUSPICE}} were
consolidated to simplify analysis and address sparse categories.
Additionally, missing and irrelevant records were removed to ensure the
dataset was both accurate and meaningful for the research objectives.

The data for this study was systematically downloaded, cleaned,
analyzed, and visualized using \textbf{\texttt{R}} (R Core Team 2023), a
statistical programming language. The following are major packages used
for this study: \textbf{\texttt{opendatatoronto}}(Gelfand 2022): Used to
access and retrieve the Licensed Child Care Centres dataset directly
from the City of Toronto's open data portal. \textbf{\texttt{readr}}
(Wickham, Hester, and Bryan 2024): Simplified the import and parsing of
raw data into R. \textbf{\texttt{tidyverse}} (Wickham et al. 2019):
Streamlined data manipulation, cleaning, and visualization processes.
\textbf{\texttt{dplyr}} (Wickham et al. 2023): Provided tools for
filtering, transforming, and summarizing the dataset effectively.
\textbf{\texttt{ggplot2}} (Wickham 2016): Created powerful and flexible
visualizations tailored to the analysis needs. \textbf{\texttt{car}}
(Fox and Weisberg 2019): Used for diagnostic tools, including Variance
Inflation Factor (VIF) tests, to assess multicollinearity.
\textbf{\texttt{caret}} (Kuhn and Max 2008): Enabled the development,
validation, and evaluation of machine learning models, including
training-test splits and performance metrics. \textbf{\texttt{glmnet}}
(Friedman et al., 2010): Applied for fitting regularized regression
models and feature selection. \textbf{\texttt{stargazer}} (Hlavac 2022):
Generated formatted regression tables for outputs.
\textbf{\texttt{knitr}} (Xie 2021): Dynamically integrated code,
results, and plots into the final document for seamless reporting. \#\#
Measurement This analysis focuses on the following variables, with a
specific emphasis on subsidy as the dependent variable:
\texttt{subsidy}: The binary dependent variable indicating whether a
licensed child care centre receives a government subsidy. 1: The centre
is subsidized. 0: The centre is not subsidized. \texttt{ward}:
\texttt{A\ numeric\ variable\ representing\ the\ ward\ number\ for\ child\ care\ centres.}AUSPICE\texttt{:\ The\ operating\ auspice\ of\ the\ child\ care\ centre,\ describing\ its\ governance\ and\ operational\ model.\ Possible\ values\ include:\ Non-Profit:\ Centres\ operated\ by\ non-profit\ organizations,\ often\ reinvesting\ surplus\ revenues\ into\ quality\ improvements.\ Commercial:\ For-profit\ centres\ operated\ by\ private\ organizations.\ Public:\ Centres\ run\ by\ public\ agencies\ or\ school\ boards.}bldg\_type\texttt{:\ The\ type\ of\ building\ where\ the\ child\ care\ centre\ operates,\ reflecting\ its\ infrastructure.\ Examples\ include:\ bldg\_typeCommercial\ Building\ bldg\_typeCommunity\ College/University\ \ \ \ \ \ bldg\_typeCommunity\ Health\ Centre\ bldg\_typeCommunity\ Rec/Centre\ -\ Board\ Run\ bldg\_typeCommunity/Rec\ Centre\ -\ City\ bldg\_typeCommunity/Recreation\ Centre\ bldg\_typeHigh\ Rise\ Apartment\ bldg\_typeHospital/Health\ Centre\ bldg\_typeHouse\ bldg\_typeIndustrial\ Building\ bldg\_typeLow\ Rise\ Apartment\ bldg\_typeOffice\ Building\ bldg\_typeOther\ bldg\_typePlace\ of\ Worship\ bldg\_typePrivate\ Elementary\ School\ bldg\_typePublic\ (school\ closed)\ bldg\_typePublic\ Elementary\ Special\ bldg\_typePublic\ High\ School\ bldg\_typePublic\ Middle\ School\ bldg\_typePurpose\ Built\ bldg\_typeSynagogue}cwelcc\_flag\texttt{:\ A\ binary\ variable\ indicating\ participation\ in\ the\ Canada-Wide\ Early\ Learning\ and\ Child\ Care\ (CWELCC)\ program:\ 1:\ The\ centre\ participates\ in\ CWELCC,\ enabling\ reduced\ child\ care\ fees.\ 0:\ The\ centre\ does\ not\ participate\ in\ CWELCC.}TOTSPACE`:
A numerical variable representing the total licensed capacity (spaces
available) for all age groups at a child care centre. Detailed
information about these variables' information and data structure is
presented in Table~\ref{tbl-overview}.

The variables were carefully selected based on literature-supported
relevance to subsidy allocation and their representation of real-world
phenomena

Figure~\ref{fig-relationbldgtype} illustrates the distribution of
subsidy status (1 = Subsidized, 0 = Not Subsidized) across various
building types housing licensed child care centres. Notably, Public
Schools, Purpose-Built Facilities, and Community Recreation Centres
exhibit higher proportions of subsidized centres. These facilities are
often designed to meet regulatory requirements for child care, including
adequate space, safety standards, and accessibility, aligning closely
with subsidy allocation policies (Cleveland and Krashinsky 2009).
Conversely, building types such as Industrial Buildings, Private
Elementary Schools, and Office Buildings show lower proportions of
subsidized centres, likely due to infrastructure challenges or
misalignment with subsidy eligibility criteria, such as limited
accessibility or higher operational costs (\textbf{yan2011impact?}).
These patterns suggest that building type significantly influences
subsidy distribution. Given the numerous categories of building types, a
de tailed analysis is warranted to fully understand these trends.

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-relationbldgtype-1.pdf}

}

\caption{\label{fig-relationbldgtype}Proportional Distribution of
Subsidy Status Across Building Types}

\end{figure}%

Figure~\ref{fig-relationAuspice} illustrates the proportional
distribution of subsidy status (1 = Subsidized, 0 = Not Subsidized)
across the different operating auspices of licensed child care centres:
Commercial Agency, Non-Profit Agency, and Other. Non-Profit Agencies and
``Other'' entities are predominantly subsidized, while Commercial
Agencies display a more balanced distribution. This aligns with research
indicating that non-profits rely heavily on subsidies to deliver public
goods and services, as they often operate in markets with limited
profitability (Hansmann 1979). Conversely, commercial entities are less
reliant on subsidies due to their revenue-driven models.The dominance of
subsidies in the ``Other'' category suggests this group may include
hybrid or public-private organizations aligned with specific government
initiatives (Anheier 2014). Such reliance reflects the strategic use of
subsidies to support services underserved by the private market
(Weisbrod 2000).

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-relationAuspice-1.pdf}

}

\caption{\label{fig-relationAuspice}Proportional Distribution of Subsidy
Status by Auspice}

\end{figure}%

Figure~\ref{fig-key} a heatmap illustrates the correlations between
three variables: TOTSPACE (likely representing total space or capacity),
subsidy (indicating subsidy status or amount), and cwelcc\_flag
(potentially denoting eligibility for a specific program or funding).
The positive correlation between TOTSPACE and subsidy (0.25) suggests
that larger facilities are modestly more likely to receive subsidies,
reflecting their capacity to serve larger populations or provide greater
public benefits. This aligns with research indicating that larger
organizations often have the resources and visibility to secure
subsidies (Hansmann, 1980; Salamon, 2002). Additionally, the stronger
correlation between subsidy and cwelcc\_flag (0.48) highlights that
subsidy allocation may target entities meeting specific programmatic or
policy criteria, consistent with the literature emphasizing strategic
targeting of subsidies to maximize societal impact (Weisbrod, 1998). The
weaker correlation between TOTSPACE and cwelcc\_flag (0.17) suggests
that program eligibility is less dependent on size and more on
qualitative factors like service type or demographic focus, which is
supported by Anheier's (2005) analysis of non-profit funding models.
Together, these correlations emphasize the nuanced role of subsidies in
balancing operational scale and policy alignment, underscoring the
importance of strategic allocation in public funding (Salamon, 1995).

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-key-1.pdf}

}

\caption{\label{fig-key}Correlation Heatmap of Key Variables: TOTSPACE,
Subsidy, and CWELCC Flag}

\end{figure}%

\section{Model}\label{model}

\subsection{Model Specification}\label{model-specification}

To investigate the factors influencing subsidy allocation to licensed
child care centres, a reduced logistic regression model was specified.
The dependent variable,\texttt{subsidy}, is a binary indicator
representing whether a child care centre receives government subsidy (1
= subsidized, 0 = not subsidized). The model includes three key
predictors: \texttt{Operating\ Auspice\ (AUSPICE)}: A categorical
variable indicating the governance model of the child care centre (e.g.,
Non-Profit Agency, Other). Non-profit agencies are hypothesized to be
positively associated with subsidy allocation, consistent with previous
research emphasizing their prioritization in funding schemes (Cleveland
\& Krashinsky, 2005).
\texttt{Participation\ in\ the\ CWELCC\ Program\ (cwelcc\_flag)}: A
binary variable capturing whether the centre participates in the
Canada-Wide Early Learning and Child Care program (1 = participates, 0 =
does not participate). Centres participating in this initiative are
expected to have higher odds of receiving subsidies due to their
alignment with government objectives of affordability and accessibility
(Friendly \& Ballantyne, 2022). \texttt{Total\ Space\ (TOTSPACE)}: A
continuous variable representing the number of licensed spaces available
in the centre. Larger centres are hypothesized to have higher odds of
subsidy allocation, as they can accommodate more families and align with
policy goals of maximizing access (Forry et al., 2010). The logistic
regression model can be expressed mathematically as follows:

\subsection{Model Justification}\label{model-justification}

The logistic regression model was chosen for this analysis because it is
well-suited to the binary nature of the dependent variable, subsidy
status (1 = Subsidized, 0 = Not Subsidized). A logistic regression model
using the binomial family is specifically designed to model dichotomous
outcomes by estimating the log-odds of the event occurring as a linear
function of predictor variables (Hosmer Jr, Lemeshow, and Sturdivant
2013). The binomial family is appropriate here because it assumes that
the dependent variable follows a Bernoulli distribution, where each
observation represents a binary outcome (subsidized or not subsidized).
This ensures that the predicted probabilities remain between 0 and 1,
aligning with the real-world constraints of the problem. Additionally,
logistic regression provides interpretable coefficients, which indicate
the direction and magnitude of the relationship between each predictor
and the log-odds of subsidy allocation. This makes it particularly
useful for guiding policy decisions, as coefficients can be directly
converted into odds ratios for actionable insights (Peng, Lee, and
Ingersoll 2002). The ward variable was excluded because it lacked
statistical significance and added redundancy, as its effects were
captured by other predictors like CWELCC participation and total space.
Additionally, ward had no strong theoretical justification as a direct
determinant of subsidy allocation. The building type variable was
removed due to high dimensionality, sparse representation in many
categories, and statistical insignificance. Its effects are likely
mediated by other variables, such as total space and auspice. Excluding
it improved parsimony and interpretability. The final model retained
operating auspice, CWELCC participation, and total space, as these
predictors are strongly supported by theory and data. This approach
balances simplicity and accuracy, ensuring the model remains relevant
for informing equitable subsidy allocation policies.

\subsection{Model Assumptions}\label{model-assumptions}

To ensure the validity of the logistic regression model, several key
assumptions were assessed, including independence of observations, the
appropriateness of a binary outcome, the linearity of predictors with
the logit and absence of multicollinearity. The analysis integrates
results from visual diagnostics, multicollinearity tests, and
statistical measures. 1. Independence of Observations The logistic
regression model assumes that the observations are independent of each
other. In this analysis, each data point corresponds to an individual
child care center, ensuring independence. There is no clustering or
repeated measures within the dataset, which validates this assumption.
2. Binary Outcome The logistic regression model assumes a binary
dependent variable. In this case, the outcome variable,
\texttt{subsidy}, is binary, indicating whether a child care center
receives a subsidy (1 = Subsidized, 0 = Not Subsidized). This aligns
with the model's requirement, ensuring the suitability of the binomial
family for fitting the data. 3. Linearity of Predictors with the Logit
The Figure~\ref{fig-cr} The component + residual plots evaluate the
linearity of the continuous variables and the relationship between
categorical predictors and the logit transformation. graph

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-cr-1.pdf}

}

\caption{\label{fig-cr}CR Plot for Linearity Chekck}

\end{figure}%

\texttt{TOTSPACE}: The relationship between the total space (TOTSPACE)
and the logit appears approximately linear, as indicated by the flat,
consistent pattern of residuals around the horizontal axis. This
supports the assumption of linearity. \texttt{CWELCC\ Flag}: The plot
for CWELCC participation shows a horizontal trend, suggesting no
significant deviation from linearity. The data support the inclusion of
this variable as a binary predictor. \texttt{AUSPICE}: The residual
patterns for categorical levels of AUSPICE (e.g., ``Commercial Agency''
and ``Other'') indicate distinct clusters with consistent variability.
This suggests the categorical nature of this variable does not violate
linearity assumptions. Overall, the visual inspection suggests that the
linearity assumption for the predictors with the logit is met.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Multicollinearity Assessment Variance Inflation Factor (VIF): To
  assess multicollinearity among the predictors, the VIF values for the
  reduced model variables were calculated.
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Calculate VIF}
\NormalTok{vif\_values }\OtherTok{\textless{}{-}} \FunctionTok{vif}\NormalTok{(reduced\_model\_2)}
\end{Highlighting}
\end{Shaded}

All VIF values are below 2, well within the acceptable threshold of 5,
indicating minimal multicollinearity among the predictors. The
independence of the predictors ensures the stability of the coefficient
estimates.

\subsection{Alternative Models}\label{alternative-models}

Alternative models like decision trees and random forests were
considered but were found less interpretable for policy-focused
analyses. Logistic regression was chosen for its balance of simplicity,
interpretability, and effectiveness.

\#Result The logistic regression model's performance metrics are
presented in Table~\ref{tbl-coefresult}.

\begin{table}

\caption{\label{tbl-coefresult}Regression Result}

\centering{

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]},
column{1}={halign=l,},
column{2}={halign=c,},
hline{17}={1,2}{solid, 0.05em, black},
}                     %% tabularray inner close
\toprule
& Final Model \\ \midrule %% TinyTableHeader
(Intercept)              & -4.967    \\
& (0.496)   \\
& (<0.001)  \\
AUSPICENon Profit Agency & 2.883     \\
& (0.234)   \\
& (<0.001)  \\
AUSPICEOther             & 18.772    \\
& (686.847) \\
& (0.978)   \\
cwelcc_flag              & 3.156     \\
& (0.436)   \\
& (<0.001)  \\
TOTSPACE                 & 0.014     \\
& (0.003)   \\
& (<0.001)  \\
Num.Obs.                 & 750       \\
AIC                      & 528.1     \\
BIC                      & 551.2     \\
Log.Lik.                 & -259.035  \\
RMSE                     & 0.32      \\
\bottomrule
\end{tblr}

}

\end{table}%

The regression model reveals several key observations regarding the
predictors and overall goodness of fit. The intercept, estimated at
-4.967, represents the baseline log-odds of the outcome when all
predictors are at their reference or zero level. While not directly
interpretable, it serves as a baseline reference for the model. Among
the predictors, the AUSPICE: Non-Profit Agency category significantly
increases the log-odds of the outcome, with an estimate of 2.883 and a
small standard error of 0.234, indicating a strong and reliable positive
effect. However, the AUSPICE: Other category shows an unusually large
coefficient (18.772) paired with a very high standard error (686.847),
suggesting instability. The CWELCC Flag variable also exhibits a strong
and reliable positive effect, with an estimate of 3.156 and a standard
error of 0.436, indicating that being flagged as CWELCC significantly
increases the log-odds of the outcome. Additionally, the TOTSPACE
variable has a small but statistically significant effect, with an
estimate of 0.014 and a low standard error of 0.003, reflecting
robustness.

In terms of model fit, the dataset includes 750 observations, and the
model's AIC (528.1) and BIC (551.2) suggest a reasonable balance between
goodness of fit and complexity, as lower values are generally preferred
(Burnham and Anderson, n.d.). The log-likelihood of -259.035 also
supports an adequate fit, with a higher (less negative) value indicating
better alignment between the model and the data. Finally, the RMSE of
0.32 reflects the model's predictive accuracy, with a low value
indicating that the model's predictions closely match the observed data.
Overall, the model performs well but may require refinement,
particularly in addressing instability in the AUSPICE: Other variable.

The evaluation of the logistic regression model shows strong performance
based on McFadden's R\^{}2 and the Area Under the Receiver Operating
Characteristic Curve (AUC). McFadden's R\^{}2 which is a pseudo-R\^{}2
metric specifically designed for logistic regression, was calculated as
0.454. This value suggests that the model explains 45.4\% of the
variance in the outcome variable, indicating a well-fitting model.
McFadden (\textbf{mcfadden1972conditional?}) proposed this metric as a
reliable measure for logistic regression, where values between 0.2 and
0.4 are considered indicative of a good model fit, and values above 0.4
demonstrate an excellent fit. Thus, the model's R\^{}2 value strongly
supports its utility in predicting the outcome.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Extract coefficients and confidence intervals}
\NormalTok{tidy\_model }\OtherTok{\textless{}{-}}\NormalTok{ broom}\SpecialCharTok{::}\FunctionTok{tidy}\NormalTok{(reduced\_model\_2, }\AttributeTok{conf.int =} \ConstantTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Highlight significant coefficients}
\NormalTok{tidy\_model }\OtherTok{\textless{}{-}}\NormalTok{ tidy\_model }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{significant =} \FunctionTok{ifelse}\NormalTok{(conf.low }\SpecialCharTok{\textgreater{}} \DecValTok{0} \SpecialCharTok{|}\NormalTok{ conf.high }\SpecialCharTok{\textless{}} \DecValTok{0}\NormalTok{, }\StringTok{"Significant"}\NormalTok{, }\StringTok{"Not Significant"}\NormalTok{))}

\CommentTok{\# Plot with enhancements}
\FunctionTok{ggplot}\NormalTok{(tidy\_model, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ estimate, }\AttributeTok{y =} \FunctionTok{reorder}\NormalTok{(term, }\FunctionTok{abs}\NormalTok{(estimate)), }\AttributeTok{color =}\NormalTok{ significant)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{geom\_errorbarh}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xmin =}\NormalTok{ conf.low, }\AttributeTok{xmax =}\NormalTok{ conf.high), }\AttributeTok{height =} \FloatTok{0.2}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\StringTok{"Significant"} \OtherTok{=} \StringTok{"red"}\NormalTok{, }\StringTok{"Not Significant"} \OtherTok{=} \StringTok{"black"}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Coefficient Plot"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Coefficient Estimate"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Predictor Variables"}\NormalTok{,}
    \AttributeTok{color =} \StringTok{"Significance"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-16-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Calculate log{-}likelihood of the fitted model}
\NormalTok{log\_likelihood\_fitted }\OtherTok{\textless{}{-}} \FunctionTok{logLik}\NormalTok{(reduced\_model\_2)}
\CommentTok{\# Fit the null model (model with intercept only)}
\NormalTok{null\_model }\OtherTok{\textless{}{-}} \FunctionTok{glm}\NormalTok{(subsidy }\SpecialCharTok{\textasciitilde{}} \DecValTok{1}\NormalTok{, }\AttributeTok{data =}\NormalTok{ train\_data, }\AttributeTok{family =}\NormalTok{ binomial)}
\NormalTok{log\_likelihood\_null }\OtherTok{\textless{}{-}} \FunctionTok{logLik}\NormalTok{(null\_model)}
\CommentTok{\# McFadden\textquotesingle{}s R{-}squared}
\NormalTok{mcfadden\_r2 }\OtherTok{\textless{}{-}} \DecValTok{1} \SpecialCharTok{{-}} \FunctionTok{as.numeric}\NormalTok{(log\_likelihood\_fitted }\SpecialCharTok{/}\NormalTok{ log\_likelihood\_null)}
\CommentTok{\# Print the result}
\FunctionTok{print}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"McFadden\textquotesingle{}s R{-}squared:"}\NormalTok{, }\FunctionTok{round}\NormalTok{(mcfadden\_r2, }\DecValTok{6}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] "McFadden's R-squared: 0.454164"
\end{verbatim}

\begin{verbatim}
Area under the curve: 0.8998
\end{verbatim}

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-roc-1.pdf}

}

\caption{\label{fig-roc}ROC Curve for Model Performance}

\end{figure}%

The ROC curve in Figure~\ref{fig-roc} shown further validates the
model's classification ability, with an AUC of 0.8998. An AUC value
close to 1 indicates excellent discriminative power, where the model
effectively separates true positives from false positives. The AUC of
0.8998 places this model on the borderline of very good and excellent
discrimination, underscoring its robust predictive capacity. These
results collectively suggest that the logistic regression model not only
fits the data well but also performs strongly in classification tasks.
However, as suggested by Harrell (Harrell 2012), care must be taken to
ensure the model is not overfitted, particularly given the high AUC
value. Cross-validation or testing on an independent dataset is
recommended to confirm the model's generalizability. Additionally,
assessing the contribution of individual predictors can enhance the
interpretability of the model, as overly complex models may inflate
performance metrics without offering meaningful insights. Overall, the
model's performance metrics strongly support its use for prediction in
practical settings while aligning with academic standards for model
evaluation.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Generate predicted probabilities for the test dataset}
\NormalTok{test\_data}\SpecialCharTok{$}\NormalTok{predicted\_prob }\OtherTok{\textless{}{-}} \FunctionTok{predict}\NormalTok{(reduced\_model\_2, }\AttributeTok{newdata =}\NormalTok{ test\_data, }\AttributeTok{type =} \StringTok{"response"}\NormalTok{)}

\CommentTok{\# Predicted vs. Observed Scatterplot}
\FunctionTok{ggplot}\NormalTok{(test\_data, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ predicted\_prob, }\AttributeTok{y =}\NormalTok{ subsidy)) }\SpecialCharTok{+}
  \FunctionTok{geom\_jitter}\NormalTok{(}\AttributeTok{width =} \FloatTok{0.02}\NormalTok{, }\AttributeTok{height =} \FloatTok{0.02}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\AttributeTok{color =} \StringTok{"blue"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"loess"}\NormalTok{, }\AttributeTok{color =} \StringTok{"red"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Predicted vs. Observed Probability"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Predicted Probability"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Observed Outcome"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
`geom_smooth()` using formula = 'y ~ x'
\end{verbatim}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-19-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Create a coefficient table}
\NormalTok{model\_list }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(}
  \StringTok{"Full Model"} \OtherTok{=}\NormalTok{ log\_model,}
  \StringTok{"AIC Model"} \OtherTok{=}\NormalTok{ reduced\_model\_re,}
  \StringTok{"Simplified Model"} \OtherTok{=}\NormalTok{ reduced\_model\_2}
\NormalTok{)}

\CommentTok{\# Customize the table to display only AIC and Deviance}
\FunctionTok{modelsummary}\NormalTok{(}
\NormalTok{  model\_list,}
  \AttributeTok{output =} \StringTok{"markdown"}\NormalTok{,}
  \AttributeTok{gof\_map =} \FunctionTok{c}\NormalTok{(}\StringTok{"AIC"}\NormalTok{, }\StringTok{"Deviance"}\NormalTok{)  }\CommentTok{\# Include only AIC and Deviance in the table}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}
\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]Q[]},
column{1}={halign=l,},
column{2}={halign=c,},
column{3}={halign=c,},
column{4}={halign=c,},
}                     %% tabularray inner close
\toprule
& Full Model & AIC Model & Simplified Model \\ \midrule %% TinyTableHeader
(Intercept)                               & 10.717     & 10.655     & -4.967    \\
& (2454.170) & (2457.796) & (0.496)   \\
ward                                      & -0.007     &            &           \\
& (0.021)    &            &           \\
AUSPICENon Profit Agency                  & 2.752      & 2.753      & 2.883     \\
& (0.339)    & (0.339)    & (0.234)   \\
AUSPICEOther                              & 19.252     & 19.261     & 18.772    \\
& (1009.264) & (1008.865) & (686.847) \\
bldg_typeCatholic Elementary School       & -14.928    & -14.930    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typeCatholic High School             & 1.120      & 1.037      &           \\
& (6969.058) & (6970.335) &           \\
bldg_typeChurch                           & -16.826    & -16.826    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typeCommercial Building              & -18.590    & -18.616    &           \\
& (2454.171) & (2457.796) &           \\
bldg_typeCommunity College/University     & 1.009      & 0.989      &           \\
& (4488.740) & (4490.254) &           \\
bldg_typeCommunity Health Centre          & 1.092      & 1.037      &           \\
& (6969.058) & (6970.335) &           \\
bldg_typeCommunity Rec/Centre - Board Run & -35.148    & -35.072    &           \\
& (6969.058) & (6970.335) &           \\
bldg_typeCommunity/Rec Centre - City      & 1.053      & 1.077      &           \\
& (4061.162) & (4063.980) &           \\
bldg_typeCommunity/Recreation Centre      & -16.003    & -16.013    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typeHigh Rise Apartment              & -12.625    & -12.631    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typeHospital/Health Centre           & 1.367      & 1.354      &           \\
& (6969.058) & (6970.335) &           \\
bldg_typeHouse                            & -14.939    & -14.920    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typeIndustrial Building              & -32.542    & -32.470    &           \\
& (4618.831) & (4622.295) &           \\
bldg_typeLow Rise Apartment               & -14.884    & -14.852    &           \\
& (2454.173) & (2457.798) &           \\
bldg_typeOffice Building                  & -16.708    & -16.695    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typeOther                            & -16.973    & -16.963    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typePlace of Worship                 & -16.929    & -16.931    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typePrivate Elementary School        & -34.849    & -34.836    &           \\
& (3381.477) & (3387.732) &           \\
bldg_typePublic (school closed)           & -16.221    & -16.188    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typePublic Elementary School         & -13.716    & -13.712    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typePublic Elementary Special        & -0.010     & 0.007      &           \\
& (6969.058) & (6970.335) &           \\
bldg_typePublic High School               & -15.904    & -15.871    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typePublic Middle School             & 1.045      & 1.117      &           \\
& (6969.058) & (6970.335) &           \\
bldg_typePurpose Built                    & -14.567    & -14.572    &           \\
& (2454.170) & (2457.796) &           \\
bldg_typeSynagogue                        & -18.451    & -18.405    &           \\
& (2454.170) & (2457.796) &           \\
cwelcc_flag                               & 3.504      & 3.473      & 3.156     \\
& (0.519)    & (0.510)    & (0.436)   \\
TOTSPACE                                  & 0.013      & 0.013      & 0.014     \\
& (0.004)    & (0.004)    & (0.003)   \\
\bottomrule
\end{tblr}
\end{table}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-anheier2014nonprofit}
Anheier, Helmut K. 2014. \emph{Nonprofit Organizations: Theory,
Management, Policy}. Routledge.

\bibitem[\citeproctext]{ref-burnhammodel}
Burnham, KP, and DR Anderson. n.d. {``Model Selection and Multimodel
Inference: A Practical Information-Theoretic Approach2nd Ed.
2002Springer-Verlag.''} \emph{New York}.

\bibitem[\citeproctext]{ref-cleveland2009nonprofit}
Cleveland, Gordon, and Michael Krashinsky. 2009. {``The Nonprofit
Advantage: Producing Quality in Thick and Thin Child Care Markets.''}
\emph{Journal of Policy Analysis and Management} 28 (3): 440--62.

\bibitem[\citeproctext]{ref-citecar}
Fox, John, and Sanford Weisberg. 2019. \emph{An {R} Companion to Applied
Regression}. Third. Thousand Oaks {CA}: Sage.
\url{https://www.john-fox.ca/Companion/}.

\bibitem[\citeproctext]{ref-citeopendatatoronto}
Gelfand, Sharla. 2022. \emph{Opendatatoronto: Access the City of Toronto
Open Data Portal}.
\url{https://CRAN.R-project.org/package=opendatatoronto}.

\bibitem[\citeproctext]{ref-hansmann1979role}
Hansmann, Henry B. 1979. {``The Role of Nonprofit Enterprise.''}
\emph{Yale LJ} 89: 835.

\bibitem[\citeproctext]{ref-harrell2012regression}
Harrell, Frank E. 2012. {``Regression Modeling Strategies.''} \emph{R
Package Version}, 6--2.

\bibitem[\citeproctext]{ref-citestagazer}
Hlavac, Marek. 2022. \emph{Stargazer: Well-Formatted Regression and
Summary Statistics Tables}. Bratislava, Slovakia: Social Policy
Institute. \url{https://CRAN.R-project.org/package=stargazer}.

\bibitem[\citeproctext]{ref-hosmer2013applied}
Hosmer Jr, David W, Stanley Lemeshow, and Rodney X Sturdivant. 2013.
\emph{Applied Logistic Regression}. John Wiley \& Sons.

\bibitem[\citeproctext]{ref-Johnson_Ryan_Brooks_2012}
Johnson, Anna D., Rebecca M. Ryan, and Jeanne Brooks‐Gunn. 2012.
{``Child‐care Subsidies: Do They Impact the Quality of Care Children
Experience?''} \emph{Child Development} 83 (4): 1444--61.
\url{https://doi.org/10.1111/j.1467-8624.2012.1780.x}.

\bibitem[\citeproctext]{ref-citecaret}
Kuhn, and Max. 2008. {``Building Predictive Models in r Using the Caret
Package.''} \emph{Journal of Statistical Software} 28 (5): 1--26.
\url{https://doi.org/10.18637/jss.v028.i05}.

\bibitem[\citeproctext]{ref-peng2002introduction}
Peng, Chao-Ying Joanne, Kuk Lida Lee, and Gary M Ingersoll. 2002. {``An
Introduction to Logistic Regression Analysis and Reporting.''} \emph{The
Journal of Educational Research} 96 (1): 3--14.

\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\bibitem[\citeproctext]{ref-ryan2011impact}
Ryan, Rebecca M, Anna Johnson, Elizabeth Rigby, and Jeanne Brooks-Gunn.
2011. {``The Impact of Child Care Subsidy Use on Child Care Quality.''}
\emph{Early Childhood Research Quarterly} 26 (3): 320--31.

\bibitem[\citeproctext]{ref-vines2020accessing}
Vines, Shere'lle Ramsey. 2020. {``Accessing Equity: Challenges
Middle-Income Families Face Finding High Quality Childcare.''}

\bibitem[\citeproctext]{ref-weisbrod2000profit}
Weisbrod, Burton A. 2000. \emph{To Profit or Not to Profit: The
Commercial Transformation of the Nonprofit Sector}. Cambridge University
Press.

\bibitem[\citeproctext]{ref-citeggplot2}
Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data
Analysis}. Springer-Verlag New York.
\url{https://ggplot2.tidyverse.org}.

\bibitem[\citeproctext]{ref-citetidyverse}
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.

\bibitem[\citeproctext]{ref-citedplyr}
Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis
Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.
\url{https://CRAN.R-project.org/package=dplyr}.

\bibitem[\citeproctext]{ref-citereadr}
Wickham, Hadley, Jim Hester, and Jennifer Bryan. 2024. \emph{Readr: Read
Rectangular Text Data}. \url{https://CRAN.R-project.org/package=readr}.

\bibitem[\citeproctext]{ref-citeknitr}
Xie, Yihui. 2021. \emph{Knitr: A General-Purpose Package for Dynamic
Report Generation in r}. \url{https://yihui.org/knitr/}.

\end{CSLReferences}

\end{document}

### 2024-12-04 paper/paper_副本.qmd
paper

--- 2024-12-04 paper/paper.qmd
@@
 ---
-title: "Understanding Subsidy Allocation in Toronto’s Child Care Centres: Insights from a Logistic Regression Analysis"
-subtitle: "Non-Profit Governance, Program Participation, and Capacity Drive Funding Decisions"
+title: "My title"
+subtitle: "My subtitle if needed"
 author: 
-  - Claire Ma
+  - First author
+  - Another author
 thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
@@
 date-format: long
-abstract: "This study examines the factors influencing government subsidy allocation to licensed child care centres in Toronto based on Licened child Care Centers from Open Data Toronto.
-By employing a logistic regression model, we found that non-profit governance, participation in the Canada-Wide Early Learning and Child Care (CWELCC) program, and larger capacity significantly increase a centre's likelihood of receiving subsidies.
-These findings highlight how funding priorities align with public goals to expand access to high-quality child care, especially for vulnerable populations.
-By uncovering patterns in subsidy distribution, this research provides critical insights for policymakers to ensure more equitable and effective resource allocation."
+abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
 format: pdf
@@
 library(stats)
-library(car)
-library(broom)
-library(pROC)
-library(kableExtra)
-library(knitr)
 library(modelsummary)
-
 ```
@@
 
-@fig-relationbldgtype illustrates the distribution of subsidy status (1 = Subsidized, 0 = Not Subsidized) across various building types housing licensed child care centres.
+@fig-relation_bldgtype illustrates the distribution of subsidy status (1 = Subsidized, 0 = Not Subsidized) across various building types housing licensed child care centres.
 Notably, Public Schools, Purpose-Built Facilities, and Community Recreation Centres exhibit higher proportions of subsidized centres.
@@
 ```{r}
-#| label: fig-relationbldgtype
+#| label: fig-relation_bldgtype
 #| fig-cap: "Proportional Distribution of Subsidy Status Across Building Types"
@@
 
-@fig-relationAuspice illustrates the proportional distribution of subsidy status (1 = Subsidized, 0 = Not Subsidized) across the different operating auspices of licensed child care centres: Commercial Agency, Non-Profit Agency, and Other.
+@fig-relation_Auspice illustrates the proportional distribution of subsidy status (1 = Subsidized, 0 = Not Subsidized) across the different operating auspices of licensed child care centres: Commercial Agency, Non-Profit Agency, and Other.
 Non-Profit Agencies and "Other" entities are predominantly subsidized, while Commercial Agencies display a more balanced distribution.
@@
 ```{r}
-#| label: fig-relationAuspice
+#| label: fig-relation_Auspice
 #| fig-cap: "Proportional Distribution of Subsidy Status by Auspice"
@@
 ```
-@fig-key a heatmap illustrates the correlations between three variables: TOTSPACE (likely representing total space or capacity), subsidy (indicating subsidy status or amount), and cwelcc_flag (potentially denoting eligibility for a specific program or funding).
+@fig-cor_key a heatmap illustrates the correlations between three variables: TOTSPACE (likely representing total space or capacity), subsidy (indicating subsidy status or amount), and cwelcc_flag (potentially denoting eligibility for a specific program or funding).
 The positive correlation between TOTSPACE and subsidy (0.25) suggests that larger facilities are modestly more likely to receive subsidies, reflecting their capacity to serve larger populations or provide greater public benefits.
@@
 ```{r}
-#| label: fig-key
+#| label: fig-cor_key
 #| fig-cap: "Correlation Heatmap of Key Variables: TOTSPACE, Subsidy, and CWELCC Flag"
@@
 \]
-
 Where:
-\begin{itemize}
-    \item \( P(Y=1) \): The probability that a child care center receives a subsidy (\( Y=1 \)).
-    \item \( \text{logit}(P(Y=1)) \): The log-odds of receiving a subsidy, defined as:
+- \( P(Y=1) \): The probability that a child care center receives a subsidy (\( Y=1 \)).
+- \( \text{logit}(P(Y=1)) \): The log-odds of receiving a subsidy, which is the logarithm of the odds ratio:
 \[
@@
 This transformation ensures that the predicted probabilities remain between 0 and 1.
-\end{itemize}
-
 ### Parameters:
@@
    - It provides the starting point for predicting subsidy probabilities.
-
 2. **\( \beta_1 (\text{Non-Profit Auspice}) \):**
@@
    - A positive \( \beta_1 \) increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.
-
 3. **\( \beta_2 (\text{CWELCC Participation}) \):**
    - Captures the influence of participating in the Canada-Wide Early Learning and Child Care (CWELCC) program on the log-odds of subsidy allocation.
-
+   - A positive \( \beta_2 \) indicates that centers participating in CWELCC are more likely to receive subsidies compared to non-participating centers.
 4. **\( \beta_3 (\text{Total Space}) \):**
    - Represents the effect of the number of licensed child care spaces (a continuous variable) on the log-odds of subsidy allocation.
-
+   - A positive \( \beta_3 \) suggests that centers with larger capacities are more likely to receive subsidies.
 5. **\( \epsilon \) (Error Term):**
@@
 ```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
+
+library(caret)
+library(ggplot2)
 # Encode categorical variables
@@
 #| warning: false
+library(car)
 crPlots(reduced_model_2)  # Generate Component + Residual plots
@@
 Variance Inflation Factor (VIF):
-To assess multicollinearity among the predictors, the VIF values for the reduced model variables were calculated.
+To assess multicollinearity among the predictors, the VIF values for the reduced model variables were calculated, shown in @tbl-vif:
 
 ```{r}
+#| label: tbl-vif
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "VIF values for predictor variables."
+
+library(car)
+library(knitr)
+library(kableExtra)
 # Calculate VIF
 vif_values <- vif(reduced_model_2)
+
+# Convert VIF to a data frame for easier manipulation
+vif_table <- as.data.frame(vif_values)
+vif_table$Variable <- rownames(vif_table)
+rownames(vif_table) <- NULL
+
+# Rename columns for clarity
+colnames(vif_table) <- c("GVIF", "Df", "GVIF^(1/(2*Df))", "Variable")
+
+# Rearrange columns to make Variable the first column
+vif_table <- vif_table[, c("Variable", "GVIF", "Df", "GVIF^(1/(2*Df))")]
+
+# Display VIF table
+vif_table %>%
+  kable(format = "markdown", align = "lccc", booktabs = TRUE, linesep = "") %>%
+  kable_styling(latex_options = c("hold_position"), full_width = FALSE) %>%
+  column_spec(2:4, bold = TRUE)
 ```
-
 All VIF values are below 2, well within the acceptable threshold of 5, indicating minimal multicollinearity among the predictors.
@@
 Additionally, the TOTSPACE variable has a small but statistically significant effect, with an estimate of 0.014 and a low standard error of 0.003, reflecting robustness.
-@fig-cp further visualizes the significance of predictors.
 
+In terms of model fit, the dataset includes 750 observations, and the model's AIC (528.1) and BIC (551.2) suggest a reasonable balance between goodness of fit and complexity, as lower values are generally preferred [@burnhammodel].
+The log-likelihood of -259.035 also supports an adequate fit, with a higher (less negative) value indicating better alignment between the model and the data.
+Finally, the RMSE of 0.32 reflects the model's predictive accuracy, with a low value indicating that the model's predictions closely match the observed data.
+Overall, the model performs well but may require refinement, particularly in addressing instability in the AUSPICE: Other variable.
+
+The evaluation of the logistic regression model shows strong performance based on McFadden’s R^2 and the Area Under the Receiver Operating Characteristic Curve (AUC).
+McFadden’s R^2 which is a pseudo-R^2 metric specifically designed for logistic regression, was calculated as 0.454.
+This value suggests that the model explains 45.4% of the variance in the outcome variable, indicating a well-fitting model.
+McFadden [@mcfadden1972conditional] proposed this metric as a reliable measure for logistic regression, where values between 0.2 and 0.4 are considered indicative of a good model fit, and values above 0.4 demonstrate an excellent fit.
+Thus, the model's R^2 value strongly supports its utility in predicting the outcome.
 ```{r}
-#| label: fig-cp
-#| fig-cap: "Coefficient Plot"
-#| echo: false
-#| message: false
-#| warning: false
+library(ggplot2)
+library(broom)  # To tidy the model output
 
@@
 ```
-In terms of model fit, the dataset includes 750 observations, and the model's AIC (528.1) and BIC (551.2) suggest a reasonable balance between goodness of fit and complexity, as lower values are generally preferred [@burnhammodel].
-The log-likelihood of -259.035 also supports an adequate fit, with a higher (less negative) value indicating better alignment between the model and the data.
-Finally, the RMSE of 0.32 reflects the model's predictive accuracy, with a low value indicating that the model's predictions closely match the observed data.
-Overall, the model performs well but may require refinement, particularly in addressing instability in the AUSPICE: Other variable.
 
-The evaluation of the logistic regression model shows strong performance based on McFadden’s R^2 and the Area Under the Receiver Operating Characteristic Curve (AUC).
-McFadden’s R^2 which is a pseudo-R^2 metric specifically designed for logistic regression, was calculated as 0.454.
-This value suggests that the model explains 45.4% of the variance in the outcome variable, indicating a well-fitting model.
-McFadden [@mcfadden1972conditional] proposed this metric as a reliable measure for logistic regression, where values between 0.2 and 0.4 are considered indicative of a good model fit, and values above 0.4 demonstrate an excellent fit.
-Thus, the model's R^2 value strongly supports its utility in predicting the outcome.
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
+```{r}
 # Calculate log-likelihood of the fitted model
@@
 #| warning: false
+library(pROC)
 
@@
 The AUC of 0.8998 places this model on the borderline of very good and excellent discrimination, underscoring its robust predictive capacity.
+These results collectively suggest that the logistic regression model not only fits the data well but also performs strongly in classification tasks.
+However, as suggested by Harrell [@harrell2012regression], care must be taken to ensure the model is not overfitted, particularly given the high AUC value.
+Cross-validation or testing on an independent dataset is recommended to confirm the model’s generalizability.
+Additionally, assessing the contribution of individual predictors can enhance the interpretability of the model, as overly complex models may inflate performance metrics without offering meaningful insights.
+Overall, the model’s performance metrics strongly support its use for prediction in practical settings while aligning with academic standards for model evaluation.
 
 ```{r}
-#| label: fig-pvo
-#| fig-cap: " Predicted vs. Observed Probability"
-#| echo: false
-#| message: false
-#| warning: false
 # Generate predicted probabilities for the test dataset
@@
   labs(
+    title = "Predicted vs. Observed Probability",
     x = "Predicted Probability",
@@
 ```
-@fig-pvo provides a visual representation of the alignment between the predicted probabilities generated by the logistic regression model and the actual observed binary outcomes.
-This diagnostic tool is crucial for assessing the model's calibration and predictive accuracy, as emphasized by Harrell [@harrell2012regression].
-The x-axis shows the predicted probabilities ranging from 0 to 1, while the y-axis represents the observed outcomes, where 0 indicates the absence of an event and 1 indicates its presence.
-The red diagonal line serves as the reference for perfect calibration, where predicted probabilities perfectly match observed outcomes.
-The clustering of blue points near 0 and 1 along the y-axis indicates that the model effectively distinguishes between the two classes, a key goal in binary classification modeling.
-This observation aligns with the high AUC value of 0.8998 observed in the ROC curve, which demonstrates the model’s excellent discriminative ability.
-Additionally, points near the diagonal line further suggest strong calibration, where the predicted probabilities closely align with actual outcomes.
-The concentration of blue points at the extremes of 0 and 1 highlights that the model makes confident and accurate predictions in many cases
-However, some dispersion is observed at lower predicted probabilities, particularly around 0.25 and 0.5.
-These deviations may reflect cases where the model struggles to classify outcomes or makes less confident predictions.
-Such discrepancies could indicate areas where further refinement of the model or predictors is necessary.
-These deviations could also be linked to specific subgroups or predictor interactions, necessitating additional diagnostics or recalibration, as suggested by Steyerberg et al.
-[@steyerberg2010assessing].
-Overall, this graph demonstrates that the model is well-calibrated and effective in its predictions, with minor limitations at lower probability levels.
-The close alignment of predictions with observed outcomes supports the model's reliability in classification tasks.
-This interpretation aligns with other metrics, such as McFadden’s R2R2 [@mcfadden1972conditional] and AUC, which indicate robust overall model performance while pointing to opportunities for refinement.
-Including this visualization in the results section provides a clear and data-driven assessment of the model's strengths and areas for potential improvement.
 
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
+```{r}
+# Load the modelsummary package
+library(modelsummary)
 
@@
 
-#Discussion
-
-Subsidy allocation to licensed child care centres in Toronto addresses the critical issue of affordability, making high-quality early childhood education accessible to more families as licensed centres must meet strict safety, staffing, and programming standards, which foster children’s cognitive, social, and emotional growth [@cleveland2009nonprofit].
-Without subsidies, the cost of regulated care can be prohibitive, particularly for low-income households.
-This paper undertakes a detailed examination of the factors influencing subsidy allocation to licensed child care centres in Toronto, leveraging the City of Toronto's Licensed Child Care Centres dataset from Open Data porta, which includes detailed information about 1,071 licensed centers[@citeopendatatoronto].
-This study employs a logistic regression model-binomial family to identify relationships between key predictor variables and the binary dependent variable – receiving subsidies.
-
-The dataset underwent meticulous preprocessing to ensure reliability and accuracy for analysis.
-This involved several key steps of data cleaning, variable transformation and training-test Split.
-Initially, variables of Operating auspice(AUSPICE), ward, building type(bldg_type), total space(TOTSPACE) and participation status in programs(cwelcc_flag) were chosen based their relevance and practical influence subsidy outcomes and forecasting supported by scholar literatures.
-After fitting and improving the model using stepwise selection based on the Akaike Information Criterion (AIC), non-significant variables (ward and building type(bldg_type)) were removed.
-The final model retained Operating Auspice, CWELCC Participation, and Total Licensed Capacity as key predictors.
-The assumptions underpinning the logistic regression model were thoroughly validated, ensuring its statistical rigor and reliability.
-Independence of observations was confirmed, as each data point corresponds to a unique child care centre, eliminating concerns of clustering or dependency.
-Linearity between continuous predictors, such as Total Licensed Capacity, and the logit transformation was validated through component + residual plots, which revealed consistent patterns, supporting the appropriateness of the model.
-Additionally, multicollinearity was minimized, with Variance Inflation Factor (VIF) values well below the critical threshold of 5, indicating that the predictors are independent and the coefficient estimates are stable.
-Together, these validations affirm the robustness of the model and its suitability for the analysis.
-
-The result coefficients in table the logistic regression model provide a detailed understanding of how key predictors influence the likelihood of subsidy allocation to licensed child care centres in Toronto.
-By measuring the change in log-odds of subsidy allocation associated with each predictor, the model quantifies the relative importance of governance models, program participation, and operational capacity.
-The coefficient for Non-Profit Auspice emerged as strongly positive and statistically significant, indicating that non-profit child care centres are far more likely to receive subsidies than commercial or public centres.
-This is reflective of policy priorities that favor organizations with a social mission over those with profit-oriented objectives.
-Non-profits are often viewed as better aligned with public goals of equity and accessibility, as they reinvest surplus revenues into improving care quality rather than distributing profits [@hansmann1980role].
-This is consistent with research by [@salamon1995partners], who noted that non-profits often fill critical gaps in the provision of public services, making them natural candidates for targeted funding.
-In the context of child care, non-profits may also be more likely to serve economically vulnerable populations, further justifying their prioritization for subsidies.
-The odds ratio derived from this coefficient underscores the strength of this relationship, suggesting that non-profit centres are several times more likely to receive subsidies compared to commercial centres.
-Participation in the Canada-Wide Early Learning and Child Care (CWELCC) program was the most significant predictor in the model, with a highly positive coefficient.
-This result highlights the critical role of policy alignment in subsidy allocation.
-Centres participating in CWELCC demonstrate compliance with national and provincial affordability initiatives, making them high-priority recipients of government funding.
-Research by [@bennett2011working] supports this finding, emphasizing that early childhood programs aligned with broader governmental objectives are often better positioned to secure resources.
-The odds ratio for CWELCC participation indicates that such centres are substantially more likely to receive subsidies, which is consistent with targeted funding strategies aimed at expanding access to high-quality, affordable child care [@kaga2010caring].
-Total Licensed Capacity (TOTSPACE), representing the number of spaces a centre is licensed to operate, was another important predictor, although its coefficient was smaller in magnitude compared to governance and CWELCC participation.
-This positive coefficient suggests that larger centres are more likely to receive subsidies, likely due to their capacity to serve more families and their operational scale.
-Larger centres can achieve economies of scale and often have greater visibility, making them attractive candidates for public funding [@weisbrod1998profit].
-However, the smaller effect size of this variable indicates that capacity alone is insufficient to determine subsidy allocation.
-This finding aligns with [@penn2011quality], who argues that while capacity is an important practical consideration, other factors—such as governance and programmatic alignment—carry more weight in funding decisions.
-Interpreting these coefficients through odds ratios further clarifies their impact.
-For instance, the odds ratio for CWELCC participation suggests that centres in the program are several times more likely to receive subsidies compared to non-participating centres, holding other factors constant.
-Similarly, the odds ratio for non-profit governance reinforces the preferential treatment of non-profits in subsidy allocation policies.
-These findings align with the broader literature on public funding, which emphasizes the strategic use of subsidies to support centres that meet both operational and policy criteria [@penn2011quality].
-The statistical significance of these coefficients underscores their reliability as shown in figure.
-Variables such as Non-Profit Auspice and CWELCC Participation demonstrated small standard errors and strong significance levels, reinforcing their influence on subsidy allocation.
-In contrast, variables with less consistent effects, such as certain building types or governance categories in the "Other" category, exhibited instability, suggesting that their role in funding decisions may be more context-specific or secondary.
-The model's findings highlight a strategic approach to subsidy allocation, where funding decisions are guided by alignment with policy goals, operational capacity, and governance structures.
-
-The logistic regression model applied in this research proves to be an ideal tool for analyzing subsidy allocation to licensed child care centres in Toronto, particularly due to its capacity to handle binary outcomes effectively.
-By modeling the log-odds of an event, logistic regression ensures predicted probabilities remain between 0 and 1, aligning seamlessly with the binary nature of the dependent variable—whether a centre receives a subsidy.
-This feature makes the model both statistically appropriate and easy to interpret.
-A notable strength of the model lies in its interpretability.
-Coefficients can be transformed into odds ratios, providing a clear understanding of how predictors influence the likelihood of receiving subsidies.
-For example, the positive coefficients for Non-Profit Auspice and CWELCC Participation underscore their significant, policy-relevant impact on subsidy distribution.
-This clarity makes the model particularly valuable for stakeholders and policymakers who require actionable and easily communicated insights.
-The model's performance metrics further demonstrate its effectiveness.
-A McFadden's R² value of 0.454 indicates that the model explains a substantial portion of the variance in subsidy allocation.
-Additionally, the Area Under the Curve (AUC) of 0.8998 highlights the model’s exceptional discriminative ability, confirming its capacity to accurately differentiate between subsidized and non-subsidized centres.
-The low Root Mean Squared Error (RMSE) of 0.32 further attests to the model’s strong predictive performance.
-Together, these metrics validate the model's reliability and robustness.
-Another key advantage of logistic regression is its simplicity compared to more complex approaches such as random forests or decision trees.
-While those alternatives might offer marginally higher predictive power, they lack the transparency and interpretability required for policy-focused research.
-Logistic regression strikes a critical balance between accuracy and clarity, making it a practical choice for guiding equitable subsidy allocation strategies.
-Moreover, the flexibility of logistic regression allows for extensions to explore more intricate relationships.
-For instance, incorporating interaction terms or temporal data could provide deeper insights while maintaining the model's usability.
-This adaptability ensures the model remains relevant and applicable as policy environments evolve.
-
-Our model, while effective, has several limitations that warrant consideration.
-One of the primary limitations is its reliance on the assumption of linearity between predictors and the log-odds of the outcome.
-Although this assumption is often reasonable, it may oversimplify complex, non-linear relationships that can exist in real-world phenomena such as subsidy allocation.
-As [@harrell2015regression] notes, failing to capture these non-linear relationships can lead to biased estimates and limit the model’s predictive power.
-Another limitation is the model’s dependence on correct specification of predictors.
-Excluding relevant variables or including irrelevant ones in initial variable selection can result in omitted variable bias or overfitting, respectively.
-Additionally, the model does not inherently account for higher-order interactions unless explicitly included.
-For instance, the combined effect of Non-Profit Auspice and CWELCC Participation could provide valuable insights into how policy and governance jointly influence subsidy allocation.
-[@hosmer2013applied] highlight that logistic regression can oversimplify complex relationships if interaction terms are not considered, potentially leading to incomplete conclusions.
-Finally, the static nature of the model is another drawback.
-Logistic regression provides a snapshot of relationships at a single point in time, failing to capture temporal dynamics or policy changes that can influence subsidy allocation over time.
-As Singer and [@singer2003applied] suggest, incorporating longitudinal data could provide a more nuanced understanding of how these relationships evolve.
-
-Future studies could address the limitations of this research by adopting more advanced modeling techniques and incorporating additional data to better capture the complexities of subsidy allocation.
-Introducing non-linear models or machine learning approaches, such as random forests or gradient boosting, could uncover hidden patterns and interactions between predictors that logistic regression may overlook.
-Additionally, exploring interaction terms, such as the joint effects of governance models and program participation, could provide more nuanced insights into policy impacts.
-Longitudinal data would be particularly valuable for understanding how subsidy allocation evolves over time, especially in response to policy changes or shifts in economic conditions.
-Incorporating time-series or panel data analysis could reveal temporal dynamics and provide a richer understanding of causal relationships.
-Geographic disparities, noted but not deeply explored in this study, could also be addressed using spatial regression or multilevel models to account for regional clustering and unobserved local factors influencing subsidy distribution.
-Finally, integrating additional predictors, such as demographic variables, socio-economic indicators, or quality ratings of child care centres, could enhance the explanatory power of future models.
-These enhancements would provide a more comprehensive view of subsidy allocation and inform strategies to ensure equitable and effective distribution of resources.
-
-# Appendix A: Observational Data Methodology for Licensed Child Care Centres in Toronto
-
-## A.1 Population, Frame, and Sample
-A.1.1 Population
-The population includes all licensed child care centres in Toronto as recorded in the publicly available dataset provided by Open Toronto.
-This population aligns with studies on regulated child care, such as [@morrissey2010childcare], which emphasizes the role of licensing in ensuring quality and safety in early childhood education.
-However, the dataset excludes unlicensed child care providers, limiting its scope.
-Represented Groups: Centres adhering to provincial licensing requirements, as emphasized by Cleveland and Krashinsky [@cleveland2003benefits], who note that licensed care is generally associated with higher quality standards.
-Excluded Groups: Informal and unlicensed providers, which disproportionately to lower-income families and those in rural or underserved urban areas.
-A.1.2 Frame
-The dataset represents a comprehensive census of licensed child care centres, reflecting administrative records compiled by the city. 
-Strengths: Comprehensive coverage reduces selection bias and enhances geographic representativeness.
-Limitations: Static data may fail to capture temporal variations or operational changes, a common limitation noted in administrative datasets.
-A.1.3 Sample
-The dataset uses census sampling of licensed child care centres, ensuring inclusion of all facilities within the licensing framework.
-Advantages: Census data minimizes sampling error and provides a reliable basis for spatial and capacity analysis.
-Drawbacks: Lack of informal care data may lead to underrepresentation of actual child care resources, echoing findings by [@tekin2007childcare] that informal care plays a critical role in many families’ child care arrangements.
-
-## A.2 Data Collection Methodology
-A.2.1 Observational Data Compilation
-The dataset is derived from municipal administrative records, which are considered reliable for policy analysis [@cleveland2003benefits].
-Licensing authorities collect this data as part of routine compliance monitoring, ensuring high accuracy.
-Strengths: Administrative data is less prone to recall bias compared to survey data.
-Weaknesses: Lack of qualitative insights into service quality or user satisfaction.
-A.2.2 Non-response Handling
-While the dataset does not involve survey non-response, its exclusion of unlicensed providers creates a systematic gap.
-Research by Fuller et al.
-[@fuller1996family] shows that informal care often fills critical voids in underserved areas, and its exclusion may understate the full scope of child care provision.
-
-## A.3 Sampling Approach and Trade-offs
-A.3.1 Strengths
-Comprehensive Coverage: Census sampling ensures no licensed centres are omitted.
-Geospatial Precision: Geographic coordinates support advanced spatial analysis, aligning with studies like [@larsen2015accessibility] on urban accessibility.
-High Validity: Licensing records provide robust validity, as they are subject to regulatory verification [@cleveland2003benefits].
-A.3.2 Limitations
-Exclusion of Informal Care: Research by Morrissey [@morrissey2010childcare] highlights that informal care is often preferred for flexibility or affordability, making its exclusion a significant limitation.
-Static Nature: The lack of longitudinal data limits the ability to analyze trends.
-Regulatory Bias: Centers excluded due to non-compliance may disproportionately represent marginalized communities.
-
-## A.4 Observational Bias and Measurement Challenges
-A.4.1 Observational Bias
-Biases inherent in observational datasets include selection bias (due to licensing criteria) and survivorship bias (exclusion of closed centres). 
-A.4.2 Measurement Challenges
-Geographic Aggregation: Aggregating data to broader areas can obscure micro-level disparities.
-Capacity Limitations: Reported capacities may not reflect actual utilization or unmet demand, as noted by [@blau2006preschool].
-
-## A.5 Methodological Enhancements and Recommendations
-A.5.1 Enhancements
-Incorporating Temporal Data: Adding longitudinal data could enable trend analysis, echoing the approach of [@fuller1996family].
-Integration with Demographics: Linking with census data would allow for equity analysis, consistent with the methodology used by [@larsen2015accessibility].
-A.5.2 Recommendations
-Addressing Informal Care: Future studies should integrate data from community surveys to include informal providers, as suggested by [@morrissey2010childcare].
-Dynamic Updates: Regular updates to administrative records would enhance relevance, a recommendation supported.
-Geospatial Enhancements: Including data on transit access or neighborhood socioeconomic conditions could enrich spatial analyses, aligning with findings by [@tekin2007childcare]
-
 # References

### 2024-12-04 scripts/00-simulate_data.R
simulating data, downloading data, cleaning data, testing data, EDA & model

@@ -1,0 +1,55 @@
+#### Preamble ####
+# Purpose: Simulate Licened Child Care Centers dataset 
+# Author: Claire Ma
+# Date: 25 November 2024 
+# Contact: minglu.ma@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: The `dplyr` package must be installed and loaded
+# Any other information needed? Make sure you are in the `starter_folder` rproj
+
+
+#### Workspace setup ####
+
+# Load necessary library
+library(dplyr)
+
+
+#### Simulate data ####
+
+# Set seed for reproducibility
+set.seed(1008047418)
+
+# Simulate dataset
+n <- 1000  # Number of observations
+simulated_data <- data.frame(
+  ward = sample(1:25, n, replace = TRUE),  # Wards ranging from 1 to 25
+  AUSPICE = sample(
+    c("Non Profit Agency", "Commercial Agency", "Other"), 
+    n, replace = TRUE, prob = c(0.7, 0.2, 0.1)  # Adjust probabilities for three categories
+  ),  # AUSPICE categories
+  bldg_type = sample(
+    c("Catholic Elementary (French)", "Catholic Elementary School", 
+      "Catholic High School", "Church", "Commercial Building", 
+      "Community College/University", "Community Health Centre", 
+      "Community Rec/Centre - Board Run", "Community/Rec Centre - City", 
+      "Community/Recreation Centre", "High Rise Apartment", "Hospital/Health Centre",
+      "House", "Industrial Building", "Low Rise Apartment", "Office Building", "Other", 
+      "Place of Worship", "Private Elementary School", "Public (school closed)", 
+      "Public Elementary School", "Public Elementary Special", "Public High School", 
+      "Public Middle School", "Purpose Built", "Synagogue"),
+    n, replace = TRUE
+  ),  # Building types
+  cwelcc_flag = sample(0:1, n, replace = TRUE, prob = c(0.2, 0.8)),  # CWELCC flag (mostly 1)
+  TOTSPACE = round(runif(n, 14, 200)),  # Total space (random range 20 to 200)
+  subsidy = sample(0:1, n, replace = TRUE, prob = c(0.3, 0.7))  # Subsidy (mostly 1)
+)
+
+# Display first few rows of the simulated dataset
+head(simulated_data)
+
+
+
+
+
+#### Save data ####
+write_csv(simulated_data, "../data/00-simulated_data/simulated_data1.csv")

### 2024-12-04 scripts/01-test_simulated_data.R

@@ -1,0 +1,49 @@
+#### Preamble ####
+# Purpose: Tests the structure and validity of the simulated Licened Child Care Centers
+# Author: Claire Ma
+# Date: 25 November 2024
+# Contact: minglu.ma@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+  # - The `tidyverse` package must be installed and loaded
+  # - 00-simulate_data.R must have been run
+# Any other information needed? Make sure you are in the `starter_folder` rproj
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+data <- read_csv("../data/00-simulated_data/simulated_data1.csv")
+
+# Test if the data was successfully loaded
+if (exists("data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
+
+
+#### Test data ####
+
+# 1. Test if values in `ward` are greater than 0
+ward_test <- all(data$ward > 0)
+cat("Test 1: All values in 'ward' are greater than 0:", ward_test, "\n")
+
+# 2. Test if values in `TOTSPACE` (Total Space) are greater than 0
+totspace_test <- all(data$TOTSPACE > 0)
+cat("Test 2: All values in 'TOTSPACE' are greater than 0:", totspace_test, "\n")
+
+# 3. Test if values in `subsidy` are either 0 or 1
+subsidy_test <- all(data$subsidy %in% c(0, 1))
+cat("Test 3: All values in 'subsidy' are either 0 or 1:", subsidy_test, "\n")
+
+# 4. Test if values in `cwelcc_flag` are either 0 or 1
+cwelcc_flag_test <- all(data$cwelcc_flag %in% c(0, 1))
+cat("Test 4: All values in 'cwelcc_flag' are either 0 or 1:", cwelcc_flag_test, "\n")
+
+# Combine results
+if (ward_test & totspace_test & subsidy_test & cwelcc_flag_test) {
+  cat("All tests passed! The dataset meets the specified conditions.\n")
+} else {
+  cat("One or more tests failed. Please inspect the dataset for issues.\n")
+}

### 2024-12-04 scripts/02-download_data.R

@@ -1,0 +1,37 @@
+#### Preamble ####
+# Purpose: Downloads and saves the Licened Child Care Centers dataset from Open Data Toronto
+# Author: Claire Ma
+# Date: 25 November 2024
+# Contact: minglu.ma@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: The `opendatatoronto` and 'tidyverse' packages must be installed and loaded
+# Any other information needed? None
+
+
+#### Workspace setup ####
+library(opendatatoronto)
+library(tidyverse)
+library(readr)
+
+
+#### Download data ####
+# Search for a specific package on OpenDataToronto by keyword ("Marriage Licence Statistics")
+marriage_licence_packages <- search_packages("Licensed Child Care Centres")
+marriage_licence_packages
+# Retrieve a list of all resources (datasets) available within the found package
+marriage_licence_resources <- marriage_licence_packages %>%
+  list_package_resources()
+# Display the list of resources available in the "Marriage Licence Statistics" package
+marriage_licence_resources
+# Download the .csv dataset
+marriage_licence_statistics <- marriage_licence_resources[3,] %>%
+  get_resource()
+marriage_licence_statistics
+write_csv(marriage_licence_statistics, "../data/01-raw_data/raw_data.csv")
+
+
+#### Save data ####
+marriage_licence_statistics
+write_csv(marriage_licence_statistics, "../data/01-raw_data/raw_data.csv")
+
+         

### 2024-12-04 scripts/03-clean_data.R

@@ -1,0 +1,42 @@
+#### Preamble ####
+# Purpose: Cleans the raw data 
+# Author: Claire Ma
+# Date: 25 November 2024 
+# Contact: minglu.ma@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: The `dplyr` and 'readr' packages must be installed and loaded
+# Any other information needed? Make sure you are in the `starter_folder` rproj
+
+#### Workspace setup ####
+library(dplyr)
+library(readr)
+#### Clean data ####
+data <- read.csv("../data/01-raw_data/raw_data.csv")
+
+
+# Relevant columns
+relevant_columns <- c("ward", "AUSPICE", "bldg_type", "cwelcc_flag", "TOTSPACE", "subsidy")
+
+# Data Cleaning: Select, clean, and encode data
+cleaned_data <- data %>%
+  select(all_of(relevant_columns)) %>%
+  drop_na() %>%
+  mutate(
+    # Collapse sparse levels in bldg_type
+    bldg_type = case_when(
+      bldg_type %in% c("Public Elementary (French)", "Community/Rec Centre - Private", 
+                       "Community/Rec Centre AOCC", "Multi Human Services Facility") ~ "Other",
+      TRUE ~ bldg_type
+    ),
+    # Collapse sparse levels in AUSPICE
+    AUSPICE = case_when(
+      AUSPICE == "Public (City Operated) Agency" ~ "Other",
+      TRUE ~ AUSPICE
+    ),
+    # Convert binary flags to numeric
+    cwelcc_flag = ifelse(cwelcc_flag == "Y", 1, 0),  # Convert to numeric 0/1
+    subsidy = ifelse(subsidy == "Y", 1, 0)           # Ensure numeric 0/1 encoding for subsidy
+  )
+
+#### Save data ####
+write_csv(cleaned_data, "../data/02-analysis_data/cleaned_data.csv")

### 2024-12-04 scripts/04-test_analysis_data.R

@@ -1,0 +1,49 @@
+#### Preamble ####
+# Purpose: Tests the structure and validity of the cleaned Licened Child Care Centers dataset
+# Author: Claire Ma
+# Date: 25 November 2024
+# Contact: minglu.ma@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - The `readr` package must be installed and loaded
+# - 03-clean_data.R must have been run
+# Any other information needed? Make sure you are in the `starter_folder` rproj
+
+#### Workspace setup ####
+library("readr")
+data <- read_csv("../data/02-analysis_data/cleaned.csv")
+
+
+#### Test data ####
+# Test if the data was successfully loaded
+if (exists("data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
+
+
+#### Test data ####
+
+# 1. Test if values in `ward` are greater than 0
+ward_test <- all(data$ward > 0)
+cat("Test 1: All values in 'ward' are greater than 0:", ward_test, "\n")
+
+# 2. Test if values in `TOTSPACE` (Total Space) are greater than 0
+totspace_test <- all(data$TOTSPACE > 0)
+cat("Test 2: All values in 'TOTSPACE' are greater than 0:", totspace_test, "\n")
+
+# 3. Test if values in `subsidy` are either 0 or 1
+subsidy_test <- all(data$subsidy %in% c(0, 1))
+cat("Test 3: All values in 'subsidy' are either 0 or 1:", subsidy_test, "\n")
+
+# 4. Test if values in `cwelcc_flag` are either 0 or 1
+cwelcc_flag_test <- all(data$cwelcc_flag %in% c(0, 1))
+cat("Test 4: All values in 'cwelcc_flag' are either 0 or 1:", cwelcc_flag_test, "\n")
+
+# Combine results
+if (ward_test & totspace_test & subsidy_test & cwelcc_flag_test) {
+  cat("All tests passed! The dataset meets the specified conditions.\n")
+} else {
+  cat("One or more tests failed. Please inspect the dataset for issues.\n")
+}

### 2024-12-04 scripts/05-exploratory_data_analysis.R

@@ -1,0 +1,86 @@
+#### Preamble ####
+# Purpose: EDA 
+# Author: Claire Ma
+# Date: 25 November 2024 
+# Contact: minglu.ma@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: The `dplyr`,'readr', 'ggplot2', 'reshape' and 'gridExtra'packages must be installed and loaded
+# Any other information needed? Make sure you are in the `starter_folder` rproj
+
+
+#### Workspace setup ####
+library(dplyr)
+library(readr)
+library(ggplot2)
+library(reshape2)
+library(gridExtra)
+#### Read data ####
+data <- read_csv("../data/02-analysis_data/cleaned_data.csv")
+
+### EDA ####
+head(data)
+summary(data)
+
+# 1. Distribution of the Target Variable (subsidy)
+plot1 <- ggplot(data, aes(x = as.factor(subsidy))) +
+  geom_bar(fill = c("skyblue", "coral"), alpha = 0.8) +
+  labs(title = "Distribution of Subsidy",
+       x = "Subsidy (0 = No, 1 = Yes)",
+       y = "Count") +
+  theme_minimal() +
+  theme(plot.title = element_text(size = 9),  # Reduce title size
+        axis.title = element_text(size = 10),  # Reduce axis title size
+        axis.text = element_text(size = 8))    # Reduce axis text size
+
+# 2. Distribution of TOTSPACE (Histogram + Density)
+plot2 <- ggplot(data, aes(x = TOTSPACE)) +
+  geom_histogram(aes(y = ..density..), bins = 30, fill = "skyblue", alpha = 0.8) +
+  geom_density(color = "blue", size = 1) +
+  labs(title = "Distribution of TOTSPACE",
+       x = "TOTSPACE",
+       y = "Density") +
+  theme_minimal() +
+  theme(plot.title = element_text(size = 9),
+        axis.title = element_text(size = 10),
+        axis.text = element_text(size = 8))
+
+# 3. Distribution of AUSPICE (Bar Plot)
+plot3 <- ggplot(data, aes(x = reorder(AUSPICE, -table(AUSPICE)[AUSPICE]))) +
+  geom_bar(fill = "skyblue", alpha = 0.8) +
+  coord_flip() +
+  labs(title = "Distribution of AUSPICE",
+       x = "AUSPICE",
+       y = "Count") +
+  theme_minimal() +
+  theme(plot.title = element_text(size = 9),
[…]

### 2024-12-04 scripts/06-model_data.R

@@ -1,0 +1,41 @@
+#### Preamble ####
+# Purpose: Models
+# Author: Minglu Ma
+# Date: 28 November 2024 
+# Contact: minglu.ma@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: The `caret` and 'ggplot2' package must be installed and loaded
+# Any other information needed? Make sure you are in the `starter_folder` rproj
+
+#### Workspace setup ####
+library(caret)
+library(ggplot2)
+data <- read.csv("../data/02-analysis_data/cleaned_data.csv")
+#full model
+# Encode categorical variables
+data$AUSPICE <- as.factor(data$AUSPICE)
+data$bldg_type <- as.factor(data$bldg_type)
+
+# Split the data into training and testing sets
+set.seed(1008047418)
+train_index <- createDataPartition(data$subsidy, p = 0.7, list = FALSE)
+train_data <- data[train_index, ]
+test_data <- data[-train_index, ]
+
+# Fit logistic regression model
+log_model <- glm(subsidy ~ ., data = train_data, family = binomial)
+
+# Summary of the model
+summary(log_model)
+
+# Stepwise selection based on AIC
+step_model_aic <- step(log_model, direction = "both", trace = TRUE)
+
+# Summary of models
+summary(step_model_aic)  # AIC-based selected model
+
+# Refit model by removing non-significant variables
+reduced_model_2 <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE, 
+                       family = binomial, data = train_data)
+summary(reduced_model_2)
+

### 2024-12-04 paper/paper.tex
paper with title

@@
 \hypersetup{
-  pdftitle={My title},
-  pdfauthor={First author; Another author},
+  pdftitle={Understanding Subsidy Allocation in Toronto's Child Care Centres: Insights from a Logistic Regression Analysis},
+  pdfauthor={Claire Ma},
   colorlinks=true,
@@
 
-\title{My title\thanks{Code and data are available at:
-\url{https://github.com/RohanAlexander/starter_folder}.}}
+\title{Understanding Subsidy Allocation in Toronto's Child Care Centres:
+Insights from a Logistic Regression Analysis\thanks{Code and data are
+available at: \url{https://github.com/RohanAlexander/starter_folder}.}}
 \usepackage{etoolbox}
@@
 \makeatother
-\subtitle{My subtitle if needed}
-\author{First author \and Another author}
+\subtitle{Non-Profit Governance, Program Participation, and Capacity
+Drive Funding Decisions}
+\author{Claire Ma}
 \date{December 3, 2024}
@@
 \begin{abstract}
-First sentence. Second sentence. Third sentence. Fourth sentence.
+This study examines the factors influencing government subsidy
+allocation to licensed child care centres in Toronto based on Licened
+child Care Centers from Open Data Toronto. By employing a logistic
+regression model, we found that non-profit governance, participation in
+the Canada-Wide Early Learning and Child Care (CWELCC) program, and
+larger capacity significantly increase a centre's likelihood of
+receiving subsidies. These findings highlight how funding priorities
+align with public goals to expand access to high-quality child care,
+especially for vulnerable populations. By uncovering patterns in subsidy
+distribution, this research provides critical insights for policymakers
+to ensure more equitable and effective resource allocation.
 \end{abstract}
@@
 policy goals of maximizing access (Forry et al., 2010). The logistic
-regression model can be expressed mathematically as follows:
+regression model can be expressed mathematically as follows: {[}
+\text{logit}(P(Y=1)) = \beta\_0 + \beta\_1 (\text{Non-Profit Auspice}) +
+\beta\_2 (\text{CWELCC Participation}) + \beta\_3 (\text{Total Space}) +
+\epsilon {]}
+
+Where:
+
+\begin{itemize}
+    \item \( P(Y=1) \): The probability that a child care center receives a subsidy (\( Y=1 \)).
+    \item \( \text{logit}(P(Y=1)) \): The log-odds of receiving a subsidy, defined as:
+    \[
+    \text{logit}(P(Y=1)) = \ln\left(\frac{P(Y=1)}{1 - P(Y=1)}\right)
+    \]
+    This transformation ensures that the predicted probabilities remain between 0 and 1.
+\end{itemize}
+
+\subsubsection{Parameters:}\label{parameters}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  **( \beta\_0 ) (Intercept):**
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Represents the baseline log-odds of subsidy allocation when all
+    predictors are set to their reference categories or zero values.
+  \item
+    It provides the starting point for predicting subsidy probabilities.
+  \end{itemize}
+\item
+  **( \beta\_1 (\text{Non-Profit Auspice}) ):**
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Measures the effect of a center being operated as a non-profit
+    compared to the baseline (e.g., commercial auspice) on the log-odds
+    of subsidy allocation.
+  \item
+    A positive ( \beta\_1 ) increases the likelihood of receiving a
+    subsidy for non-profit centers relative to the reference group.
+  \end{itemize}
+\item
+  **( \beta\_2 (\text{CWELCC Participation}) ):**
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Captures the influence of participating in the Canada-Wide Early
+    Learning and Child Care (CWELCC) program on the log-odds of subsidy
+    allocation.
+  \end{itemize}
+\item
+  **( \beta\_3 (\text{Total Space}) ):**
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Represents the effect of the number of licensed child care spaces (a
+    continuous variable) on the log-odds of subsidy allocation.
+  \end{itemize}
+\item
+  \textbf{( \epsilon ) (Error Term):}
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Accounts for unexplained variation in the log-odds of subsidy
+    allocation not captured by the predictors.
+  \end{itemize}
+\end{enumerate}
 
@@
 estimate of 0.014 and a low standard error of 0.003, reflecting
-robustness.
+robustness. Figure~\ref{fig-cp} further visualizes the significance of
+predictors.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-cp-1.pdf}
+
+}
+
+\caption{\label{fig-cp}Coefficient Plot}
+
+\end{figure}%
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Extract coefficients and confidence intervals}
-\NormalTok{tidy\_model }\OtherTok{\textless{}{-}}\NormalTok{ broom}\SpecialCharTok{::}\FunctionTok{tidy}\NormalTok{(reduced\_model\_2, }\AttributeTok{conf.int =} \ConstantTok{TRUE}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Highlight significant coefficients}
-\NormalTok{tidy\_model }\OtherTok{\textless{}{-}}\NormalTok{ tidy\_model }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{significant =} \FunctionTok{ifelse}\NormalTok{(conf.low }\SpecialCharTok{\textgreater{}} \DecValTok{0} \SpecialCharTok{|}\NormalTok{ conf.high }\SpecialCharTok{\textless{}} \DecValTok{0}\NormalTok{, }\StringTok{"Significant"}\NormalTok{, }\StringTok{"Not Significant"}\NormalTok{))}
-
-\CommentTok{\# Plot with enhancements}
-\FunctionTok{ggplot}\NormalTok{(tidy\_model, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ estimate, }\AttributeTok{y =} \FunctionTok{reorder}\NormalTok{(term, }\FunctionTok{abs}\NormalTok{(estimate)), }\AttributeTok{color =}\NormalTok{ significant)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
-  \FunctionTok{geom\_errorbarh}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xmin =}\NormalTok{ conf.low, }\AttributeTok{xmax =}\NormalTok{ conf.high), }\AttributeTok{height =} \FloatTok{0.2}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values =} \FunctionTok{c}\NormalTok{(}\StringTok{"Significant"} \OtherTok{=} \StringTok{"red"}\NormalTok{, }\StringTok{"Not Significant"} \OtherTok{=} \StringTok{"black"}\NormalTok{)) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}
-    \AttributeTok{title =} \StringTok{"Coefficient Plot"}\NormalTok{,}
-    \AttributeTok{x =} \StringTok{"Coefficient Estimate"}\NormalTok{,}
-    \AttributeTok{y =} \StringTok{"Predictor Variables"}\NormalTok{,}
-    \AttributeTok{color =} \StringTok{"Significance"}
-\NormalTok{  ) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{paper_files/figure-pdf/unnamed-chunk-16-1.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Calculate log{-}likelihood of the fitted model}
-\NormalTok{log\_likelihood\_fitted }\OtherTok{\textless{}{-}} \FunctionTok{logLik}\NormalTok{(reduced\_model\_2)}
-\CommentTok{\# Fit the null model (model with intercept only)}
-\NormalTok{null\_model }\OtherTok{\textless{}{-}} \FunctionTok{glm}\NormalTok{(subsidy }\SpecialCharTok{\textasciitilde{}} \DecValTok{1}\NormalTok{, }\AttributeTok{data =}\NormalTok{ train\_data, }\AttributeTok{family =}\NormalTok{ binomial)}
-\NormalTok{log\_likelihood\_null }\OtherTok{\textless{}{-}} \FunctionTok{logLik}\NormalTok{(null\_model)}
-\CommentTok{\# McFadden\textquotesingle{}s R{-}squared}
-\NormalTok{mcfadden\_r2 }\OtherTok{\textless{}{-}} \DecValTok{1} \SpecialCharTok{{-}} \FunctionTok{as.numeric}\NormalTok{(log\_likelihood\_fitted }\SpecialCharTok{/}\NormalTok{ log\_likelihood\_null)}
-\CommentTok{\# Print the result}
-\FunctionTok{print}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"McFadden\textquotesingle{}s R{-}squared:"}\NormalTok{, }\FunctionTok{round}\NormalTok{(mcfadden\_r2, }\DecValTok{6}\NormalTok{)))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-[1] "McFadden's R-squared: 0.454164"
-\end{verbatim}
-
 \begin{verbatim}
@@
 0.8998 places this model on the borderline of very good and excellent
-discrimination, underscoring its robust predictive capacity. These
-results collectively suggest that the logistic regression model not only
-fits the data well but also performs strongly in classification tasks.
-However, as suggested by Harrell (Harrell 2012), care must be taken to
-ensure the model is not overfitted, particularly given the high AUC
-value. Cross-validation or testing on an independent dataset is
-recommended to confirm the model's generalizability. Additionally,
-assessing the contribution of individual predictors can enhance the
-interpretability of the model, as overly complex models may inflate
-performance metrics without offering meaningful insights. Overall, the
-model's performance metrics strongly support its use for prediction in
-practical settings while aligning with academic standards for model
-evaluation.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Generate predicted probabilities for the test dataset}
-\NormalTok{test\_data}\SpecialCharTok{$}\NormalTok{predicted\_prob }\OtherTok{\textless{}{-}} \FunctionTok{predict}\NormalTok{(reduced\_model\_2, }\AttributeTok{newdata =}\NormalTok{ test\_data, }\AttributeTok{type =} \StringTok{"response"}\NormalTok{)}
-
-\CommentTok{\# Predicted vs. Observed Scatterplot}
-\FunctionTok{ggplot}\NormalTok{(test\_data, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ predicted\_prob, }\AttributeTok{y =}\NormalTok{ subsidy)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_jitter}\NormalTok{(}\AttributeTok{width =} \FloatTok{0.02}\NormalTok{, }\AttributeTok{height =} \FloatTok{0.02}\NormalTok{, }\AttributeTok{alpha =} \FloatTok{0.6}\NormalTok{, }\AttributeTok{color =} \StringTok{"blue"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"loess"}\NormalTok{, }\AttributeTok{color =} \StringTok{"red"}\NormalTok{, }\AttributeTok{se =} \ConstantTok{FALSE}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}
-    \AttributeTok{title =} \StringTok{"Predicted vs. Observed Probability"}\NormalTok{,}
-    \AttributeTok{x =} \StringTok{"Predicted Probability"}\NormalTok{,}
-    \AttributeTok{y =} \StringTok{"Observed Outcome"}
-\NormalTok{  ) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-`geom_smooth()` using formula = 'y ~ x'
-\end{verbatim}
-
-\includegraphics{paper_files/figure-pdf/unnamed-chunk-19-1.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Create a coefficient table}
-\NormalTok{model\_list }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(}
-  \StringTok{"Full Model"} \OtherTok{=}\NormalTok{ log\_model,}
-  \StringTok{"AIC Model"} \OtherTok{=}\NormalTok{ reduced\_model\_re,}
-  \StringTok{"Simplified Model"} \OtherTok{=}\NormalTok{ reduced\_model\_2}
-\NormalTok{)}
-
-\CommentTok{\# Customize the table to display only AIC and Deviance}
-\FunctionTok{modelsummary}\NormalTok{(}
-\NormalTok{  model\_list,}
-  \AttributeTok{output =} \StringTok{"markdown"}\NormalTok{,}
-  \AttributeTok{gof\_map =} \FunctionTok{c}\NormalTok{(}\StringTok{"AIC"}\NormalTok{, }\StringTok{"Deviance"}\NormalTok{)  }\CommentTok{\# Include only AIC and Deviance in the table}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{table}
-\centering
-\begin{tblr}[         %% tabularray outer open
-]                     %% tabularray outer close
-{                     %% tabularray inner open
-colspec={Q[]Q[]Q[]Q[]},
-column{1}={halign=l,},
-column{2}={halign=c,},
-column{3}={halign=c,},
-column{4}={halign=c,},
-}                     %% tabularray inner close
-\toprule
-& Full Model & AIC Model & Simplified Model \\ \midrule %% TinyTableHeader
-(Intercept)                               & 10.717     & 10.655     & -4.967    \\
-& (2454.170) & (2457.796) & (0.496)   \\
-ward                                      & -0.007     &            &           \\
-& (0.021)    &            &           \\
-AUSPICENon Profit Agency                  & 2.752      & 2.753      & 2.883     \\
-& (0.339)    & (0.339)    & (0.234)   \\
-AUSPICEOther                              & 19.252     & 19.261     & 18.772    \\
-& (1009.264) & (1008.865) & (686.847) \\
-bldg_typeCatholic Elementary School       & -14.928    & -14.930    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typeCatholic High School             & 1.120      & 1.037      &           \\
-& (6969.058) & (6970.335) &           \\
-bldg_typeChurch                           & -16.826    & -16.826    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typeCommercial Building              & -18.590    & -18.616    &           \\
-& (2454.171) & (2457.796) &           \\
-bldg_typeCommunity College/University     & 1.009      & 0.989      &           \\
-& (4488.740) & (4490.254) &           \\
-bldg_typeCommunity Health Centre          & 1.092      & 1.037      &           \\
-& (6969.058) & (6970.335) &           \\
-bldg_typeCommunity Rec/Centre - Board Run & -35.148    & -35.072    &           \\
-& (6969.058) & (6970.335) &           \\
-bldg_typeCommunity/Rec Centre - City      & 1.053      & 1.077      &           \\
-& (4061.162) & (4063.980) &           \\
-bldg_typeCommunity/Recreation Centre      & -16.003    & -16.013    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typeHigh Rise Apartment              & -12.625    & -12.631    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typeHospital/Health Centre           & 1.367      & 1.354      &           \\
-& (6969.058) & (6970.335) &           \\
-bldg_typeHouse                            & -14.939    & -14.920    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typeIndustrial Building              & -32.542    & -32.470    &           \\
-& (4618.831) & (4622.295) &           \\
-bldg_typeLow Rise Apartment               & -14.884    & -14.852    &           \\
-& (2454.173) & (2457.798) &           \\
-bldg_typeOffice Building                  & -16.708    & -16.695    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typeOther                            & -16.973    & -16.963    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typePlace of Worship                 & -16.929    & -16.931    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typePrivate Elementary School        & -34.849    & -34.836    &           \\
-& (3381.477) & (3387.732) &           \\
-bldg_typePublic (school closed)           & -16.221    & -16.188    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typePublic Elementary School         & -13.716    & -13.712    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typePublic Elementary Special        & -0.010     & 0.007      &           \\
-& (6969.058) & (6970.335) &           \\
-bldg_typePublic High School               & -15.904    & -15.871    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typePublic Middle School             & 1.045      & 1.117      &           \\
-& (6969.058) & (6970.335) &           \\
-bldg_typePurpose Built                    & -14.567    & -14.572    &           \\
-& (2454.170) & (2457.796) &           \\
-bldg_typeSynagogue                        & -18.451    & -18.405    &           \\
-& (2454.170) & (2457.796) &           \\
-cwelcc_flag                               & 3.504      & 3.473      & 3.156     \\
-& (0.519)    & (0.510)    & (0.436)   \\
-TOTSPACE                                  & 0.013      & 0.013      & 0.014     \\
-& (0.004)    & (0.004)    & (0.003)   \\
-\bottomrule
-\end{tblr}
-\end{table}
+discrimination, underscoring its robust predictive capacity.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-pvo-1.pdf}
+
+}
+
+\caption{\label{fig-pvo}Predicted vs.~Observed Probability}
+
+\end{figure}%
+
+Figure~\ref{fig-pvo} provides a visual representation of the alignment
+between the predicted probabilities generated by the logistic regression
+model and the actual observed binary outcomes. This diagnostic tool is
+crucial for assessing the model's calibration and predictive accuracy,
+as emphasized by Harrell (Harrell 2012). The x-axis shows the predicted
+probabilities ranging from 0 to 1, while the y-axis represents the
+observed outcomes, where 0 indicates the absence of an event and 1
+indicates its presence. The red diagonal line serves as the reference
+for perfect calibration, where predicted probabilities perfectly match
+observed outcomes. The clustering of blue points near 0 and 1 along the
+y-axis indicates that the model effectively distinguishes between the
+two classes, a key goal in binary classification modeling. This
+observation aligns with the high AUC value of 0.8998 observed in the ROC
+curve, which demonstrates the model's excellent discriminative ability.
+Additionally, points near the diagonal line further suggest strong
+calibration, where the predicted probabilities closely align with actual
+outcomes. The concentration of blue points at the extremes of 0 and 1
+highlights that the model makes confident and accurate predictions in
+many cases However, some dispersion is observed at lower predicted
+probabilities, particularly around 0.25 and 0.5. These deviations may
+reflect cases where the model struggles to classify outcomes or makes
+less confident predictions. Such discrepancies could indicate areas
+where further refinement of the model or predictors is necessary. These
+deviations could also be linked to specific subgroups or predictor
+interactions, necessitating additional diagnostics or recalibration, as
+suggested by Steyerberg et al. (Steyerberg et al. 2010). Overall, this
+graph demonstrates that the model is well-calibrated and effective in
+its predictions, with minor limitations at lower probability levels. The
+close alignment of predictions with observed outcomes supports the
+model's reliability in classification tasks. This interpretation aligns
+with other metrics, such as McFadden's R2R2
+(\textbf{mcfadden1972conditional?}) and AUC, which indicate robust
+overall model performance while pointing to opportunities for
+refinement. Including this visualization in the results section provides
+a clear and data-driven assessment of the model's strengths and areas
+for potential improvement.
+
+\#Discussion
+
+Subsidy allocation to licensed child care centres in Toronto addresses
+the critical issue of affordability, making high-quality early childhood
+education accessible to more families as licensed centres must meet
+strict safety, staffing, and programming standards, which foster
+children's cognitive, social, and emotional growth (Cleveland and
+Krashinsky 2009). Without subsidies, the cost of regulated care can be
+prohibitive, particularly for low-income households. This paper
+undertakes a detailed examination of the factors influencing subsidy
+allocation to licensed child care centres in Toronto, leveraging the
+City of Toronto's Licensed Child Care Centres dataset from Open Data
+porta, which includes detailed information about 1,071 licensed
+centers(Gelfand 2022). This study employs a logistic regression
+model-binomial family to identify relationships between key predictor
+variables and the binary dependent variable -- receiving subsidies.
+
+The dataset underwent meticulous preprocessing to ensure reliability and
+accuracy for analysis. This involved several key steps of data cleaning,
+variable transformation and training-test Split. Initially, variables of
+Operating auspice(AUSPICE), ward, building type(bldg\_type), total
+space(TOTSPACE) and participation status in programs(cwelcc\_flag) were
+chosen based their relevance and practical influence subsidy outcomes
+and forecasting supported by scholar literatures. After fitting and
+improving the model using stepwise selection based on the Akaike
+Information Criterion (AIC), non-significant variables (ward and
+building type(bldg\_type)) were removed. The final model retained
+Operating Auspice, CWELCC Participation, and Total Licensed Capacity as
+key predictors. The assumptions underpinning the logistic regression
+model were thoroughly validated, ensuring its statistical rigor and
+reliability. Independence of observations was confirmed, as each data
+point corresponds to a unique child care centre, eliminating concerns of
+clustering or dependency. Linearity between continuous predictors, such
+as Total Licensed Capacity, and the logit transformation was validated
+through component + residual plots, which revealed consistent patterns,
+supporting the appropriateness of the model. Additionally,
+multicollinearity was minimized, with Variance Inflation Factor (VIF)
+values well below the critical threshold of 5, indicating that the
+predictors are independent and the coefficient estimates are stable.
+Together, these validations affirm the robustness of the model and its
+suitability for the analysis.
+
+The result coefficients in table the logistic regression model provide a
+detailed understanding of how key predictors influence the likelihood of
+subsidy allocation to licensed child care centres in Toronto. By
+measuring the change in log-odds of subsidy allocation associated with
+each predictor, the model quantifies the relative importance of
+governance models, program participation, and operational capacity. The
+coefficient for Non-Profit Auspice emerged as strongly positive and
+statistically significant, indicating that non-profit child care centres
+are far more likely to receive subsidies than commercial or public
+centres. This is reflective of policy priorities that favor
+organizations with a social mission over those with profit-oriented
+objectives. Non-profits are often viewed as better aligned with public
+goals of equity and accessibility, as they reinvest surplus revenues
+into improving care quality rather than distributing profits
+(\textbf{hansmann1980role?}). This is consistent with research by
+(\textbf{salamon1995partners?}), who noted that non-profits often fill
+critical gaps in the provision of public services, making them natural
+candidates for targeted funding. In the context of child care,
+non-profits may also be more likely to serve economically vulnerable
+populations, further justifying their prioritization for subsidies. The
+odds ratio derived from this coefficient underscores the strength of
+this relationship, suggesting that non-profit centres are several times
+more likely to receive subsidies compared to commercial centres.
+Participation in the Canada-Wide Early Learning and Child Care (CWELCC)
+program was the most significant predictor in the model, with a highly
+positive coefficient. This result highlights the critical role of policy
+alignment in subsidy allocation. Centres participating in CWELCC
+demonstrate compliance with national and provincial affordability
+initiatives, making them high-priority recipients of government funding.
+Research by (\textbf{bennett2011working?}) supports this finding,
+emphasizing that early childhood programs aligned with broader
+governmental objectives are often better positioned to secure resources.
+The odds ratio for CWELCC participation indicates that such centres are
+substantially more likely to receive subsidies, which is consistent with
+targeted funding strategies aimed at expanding access to high-quality,
+affordable child care (\textbf{kaga2010caring?}). Total Licensed
+Capacity (TOTSPACE), representing the number of spaces a centre is
+licensed to operate, was another important predictor, although its
+coefficient was smaller in magnitude compared to governance and CWELCC
+participation. This positive coefficient suggests that larger centres
+are more likely to receive subsidies, likely due to their capacity to
+serve more families and their operational scale. Larger centres can
+achieve economies of scale and often have greater visibility, making
+them attractive candidates for public funding
+(\textbf{weisbrod1998profit?}). However, the smaller effect size of this
+variable indicates that capacity alone is insufficient to determine
+subsidy allocation. This finding aligns with
+(\textbf{penn2011quality?}), who argues that while capacity is an
+important practical consideration, other factors---such as governance
+and programmatic alignment---carry more weight in funding decisions.
+Interpreting these coefficients through odds ratios further clarifies
+their impact. For instance, the odds ratio for CWELCC participation
+suggests that centres in the program are several times more likely to
+receive subsidies compared to non-participating centres, holding other
+factors constant. Similarly, the odds ratio for non-profit governance
+reinforces the preferential treatment of non-profits in subsidy
+allocation policies. These findings align with the broader literature on
+public funding, which emphasizes the strategic use of subsidies to
+support centres that meet both operational and policy criteria
+(\textbf{penn2011quality?}). The statistical significance of these
+coefficients underscores their reliability as shown in figure. Variables
+such as Non-Profit Auspice and CWELCC Participation demonstrated small
+standard errors and strong significance levels, reinforcing their
+influence on subsidy allocation. In contrast, variables with less
+consistent effects, such as certain building types or governance
+categories in the ``Other'' category, exhibited instability, suggesting
+that their role in funding decisions may be more context-specific or
+secondary. The model's findings highlight a strategic approach to
+subsidy allocation, where funding decisions are guided by alignment with
+policy goals, operational capacity, and governance structures.
+
+The logistic regression model applied in this research proves to be an
+ideal tool for analyzing subsidy allocation to licensed child care
+centres in Toronto, particularly due to its capacity to handle binary
+outcomes effectively. By modeling the log-odds of an event, logistic
+regression ensures predicted probabilities remain between 0 and 1,
+aligning seamlessly with the binary nature of the dependent
+variable---whether a centre receives a subsidy. This feature makes the
+model both statistically appropriate and easy to interpret. A notable
+strength of the model lies in its interpretability. Coefficients can be
+transformed into odds ratios, providing a clear understanding of how
+predictors influence the likelihood of receiving subsidies. For example,
+the positive coefficients for Non-Profit Auspice and CWELCC
+Participation underscore their significant, policy-relevant impact on
+subsidy distribution. This clarity makes the model particularly valuable
+for stakeholders and policymakers who require actionable and easily
+communicated insights. The model's performance metrics further
+demonstrate its effectiveness. A McFadden's R² value of 0.454 indicates
+that the model explains a substantial portion of the variance in subsidy
+allocation. Additionally, the Area Under the Curve (AUC) of 0.8998
+highlights the model's exceptional discriminative ability, confirming
+its capacity to accurately differentiate between subsidized and
+non-subsidized centres. The low Root Mean Squared Error (RMSE) of 0.32
+further attests to the model's strong predictive performance. Together,
+these metrics validate the model's reliability and robustness. Another
+key advantage of logistic regression is its simplicity compared to more
+complex approaches such as random forests or decision trees. While those
+alternatives might offer marginally higher predictive power, they lack
+the transparency and interpretability required for policy-focused
+research. Logistic regression strikes a critical balance between
+accuracy and clarity, making it a practical choice for guiding equitable
+subsidy allocation strategies. Moreover, the flexibility of logistic
+regression allows for extensions to explore more intricate
+relationships. For instance, incorporating interaction terms or temporal
+data could provide deeper insights while maintaining the model's
+usability. This adaptability ensures the model remains relevant and
+applicable as policy environments evolve.
+
+Our model, while effective, has several limitations that warrant
+consideration. One of the primary limitations is its reliance on the
+assumption of linearity between predictors and the log-odds of the
+outcome. Although this assumption is often reasonable, it may
+oversimplify complex, non-linear relationships that can exist in
+real-world phenomena such as subsidy allocation. As
+(\textbf{harrell2015regression?}) notes, failing to capture these
+non-linear relationships can lead to biased estimates and limit the
+model's predictive power. Another limitation is the model's dependence
+on correct specification of predictors. Excluding relevant variables or
+including irrelevant ones in initial variable selection can result in
+omitted variable bias or overfitting, respectively. Additionally, the
+model does not inherently account for higher-order interactions unless
+explicitly included. For instance, the combined effect of Non-Profit
+Auspice and CWELCC Participation could provide valuable insights into
+how policy and governance jointly influence subsidy allocation. (Hosmer
+Jr, Lemeshow, and Sturdivant 2013) highlight that logistic regression
+can oversimplify complex relationships if interaction terms are not
+considered, potentially leading to incomplete conclusions. Finally, the
+static nature of the model is another drawback. Logistic regression
+provides a snapshot of relationships at a single point in time, failing
+to capture temporal dynamics or policy changes that can influence
+subsidy allocation over time. As Singer and
+(\textbf{singer2003applied?}) suggest, incorporating longitudinal data
+could provide a more nuanced understanding of how these relationships
+evolve.
+
+Future studies could address the limitations of this research by
+adopting more advanced modeling techniques and incorporating additional
+data to better capture the complexities of subsidy allocation.
+Introducing non-linear models or machine learning approaches, such as
+random forests or gradient boosting, could uncover hidden patterns and
+interactions between predictors that logistic regression may overlook.
+Additionally, exploring interaction terms, such as the joint effects of
+governance models and program participation, could provide more nuanced
+insights into policy impacts. Longitudinal data would be particularly
+valuable for understanding how subsidy allocation evolves over time,
+especially in response to policy changes or shifts in economic
+conditions. Incorporating time-series or panel data analysis could
+reveal temporal dynamics and provide a richer understanding of causal
+relationships. Geographic disparities, noted but not deeply explored in
+this study, could also be addressed using spatial regression or
+multilevel models to account for regional clustering and unobserved
+local factors influencing subsidy distribution. Finally, integrating
+additional predictors, such as demographic variables, socio-economic
+indicators, or quality ratings of child care centres, could enhance the
+explanatory power of future models. These enhancements would provide a
+more comprehensive view of subsidy allocation and inform strategies to
+ensure equitable and effective distribution of resources.
+
+\section{Appendix A: Observational Data Methodology for Licensed Child
+Care Centres in
+Toronto}\label{appendix-a-observational-data-methodology-for-licensed-child-care-centres-in-toronto}
+
+\subsection{A.1 Population, Frame, and
+Sample}\label{a.1-population-frame-and-sample}
+
+A.1.1 Population The population includes all licensed child care centres
+in Toronto as recorded in the publicly available dataset provided by
+Open Toronto. This population aligns with studies on regulated child
+care, such as (Morrissey 2010), which emphasizes the role of licensing
+in ensuring quality and safety in early childhood education. However,
+the dataset excludes unlicensed child care providers, limiting its
+scope. Represented Groups: Centres adhering to provincial licensing
+requirements, as emphasized by Cleveland and Krashinsky (Cleveland and
+Krashinsky 2003), who note that licensed care is generally associated
+with higher quality standards. Excluded Groups: Informal and unlicensed
+providers, which disproportionately to lower-income families and those
+in rural or underserved urban areas. A.1.2 Frame The dataset represents
+a comprehensive census of licensed child care centres, reflecting
+administrative records compiled by the city. Strengths: Comprehensive
+coverage reduces selection bias and enhances geographic
+representativeness. Limitations: Static data may fail to capture
+temporal variations or operational changes, a common limitation noted in
+administrative datasets. A.1.3 Sample The dataset uses census sampling
+of licensed child care centres, ensuring inclusion of all facilities
+within the licensing framework. Advantages: Census data minimizes
+sampling error and provides a reliable basis for spatial and capacity
+analysis. Drawbacks: Lack of informal care data may lead to
+underrepresentation of actual child care resources, echoing findings by
+(Tekin 2007) that informal care plays a critical role in many families'
+child care arrangements.
+
+\subsection{A.2 Data Collection
+Methodology}\label{a.2-data-collection-methodology}
+
+A.2.1 Observational Data Compilation The dataset is derived from
+municipal administrative records, which are considered reliable for
+policy analysis (Cleveland and Krashinsky 2003). Licensing authorities
+collect this data as part of routine compliance monitoring, ensuring
+high accuracy. Strengths: Administrative data is less prone to recall
+bias compared to survey data. Weaknesses: Lack of qualitative insights
+into service quality or user satisfaction. A.2.2 Non-response Handling
+While the dataset does not involve survey non-response, its exclusion of
+unlicensed providers creates a systematic gap. Research by Fuller et al.
+(Fuller, Holloway, and Liang 1996) shows that informal care often fills
+critical voids in underserved areas, and its exclusion may understate
+the full scope of child care provision.
+
+\subsection{A.3 Sampling Approach and
+Trade-offs}\label{a.3-sampling-approach-and-trade-offs}
+
+A.3.1 Strengths Comprehensive Coverage: Census sampling ensures no
+licensed centres are omitted. Geospatial Precision: Geographic
+coordinates support advanced spatial analysis, aligning with studies
+like (Larsen, El-Geneidy, and Yasmin 2015) on urban accessibility. High
+Validity: Licensing records provide robust validity, as they are subject
+to regulatory verification (Cleveland and Krashinsky 2003). A.3.2
+Limitations Exclusion of Informal Care: Research by Morrissey (Morrissey
+2010) highlights that informal care is often preferred for flexibility
+or affordability, making its exclusion a significant limitation. Static
+Nature: The lack of longitudinal data limits the ability to analyze
+trends. Regulatory Bias: Centers excluded due to non-compliance may
+disproportionately represent marginalized communities.
+
+\subsection{A.4 Observational Bias and Measurement
+Challenges}\label{a.4-observational-bias-and-measurement-challenges}
+
+A.4.1 Observational Bias Biases inherent in observational datasets
+include selection bias (due to licensing criteria) and survivorship bias
+(exclusion of closed centres). A.4.2 Measurement Challenges Geographic
+Aggregation: Aggregating data to broader areas can obscure micro-level
+disparities. Capacity Limitations: Reported capacities may not reflect
+actual utilization or unmet demand, as noted by (Blau and Currie 2006).
+
+\subsection{A.5 Methodological Enhancements and
+Recommendations}\label{a.5-methodological-enhancements-and-recommendations}
+
+A.5.1 Enhancements Incorporating Temporal Data: Adding longitudinal data
+could enable trend analysis, echoing the approach of (Fuller, Holloway,
+and Liang 1996). Integration with Demographics: Linking with census data
+would allow for equity analysis, consistent with the methodology used by
+(Larsen, El-Geneidy, and Yasmin 2015). A.5.2 Recommendations Addressing
+Informal Care: Future studies should integrate data from community
+surveys to include informal providers, as suggested by (Morrissey 2010).
+Dynamic Updates: Regular updates to administrative records would enhance
+relevance, a recommendation supported. Geospatial Enhancements:
+Including data on transit access or neighborhood socioeconomic
+conditions could enrich spatial analyses, aligning with findings by
+(Tekin 2007)
 
@@
 
+\bibitem[\citeproctext]{ref-blau2006preschool}
+Blau, David M., and Janet Currie. 2006. {``Pre-School, Day Care, and
+After-School Care: Who's Minding the Kids?''} In \emph{Handbook of the
+Economics of Education}, edited by Eric A. Hanushek and Finis Welch,
+2:1163--1278. Elsevier.
+\url{https://doi.org/10.1016/S1574-0692(06)02020-4}.
+
 \bibitem[\citeproctext]{ref-burnhammodel}
@@
 
+\bibitem[\citeproctext]{ref-cleveland2003benefits}
+Cleveland, Gordon, and Michael Krashinsky. 2003. \emph{The Benefits and
+Costs of Good Child Care}. Toronto, Canada: University of Toronto Press.
+
 \bibitem[\citeproctext]{ref-cleveland2009nonprofit}
-Cleveland, Gordon, and Michael Krashinsky. 2009. {``The Nonprofit
-Advantage: Producing Quality in Thick and Thin Child Care Markets.''}
-\emph{Journal of Policy Analysis and Management} 28 (3): 440--62.
+---------. 2009. {``The Nonprofit Advantage: Producing Quality in Thick
+and Thin Child Care Markets.''} \emph{Journal of Policy Analysis and
+Management} 28 (3): 440--62.
 
@@
 \url{https://www.john-fox.ca/Companion/}.
+
+\bibitem[\citeproctext]{ref-fuller1996family}
+Fuller, Bruce, Susan D. Holloway, and Xiaoyan Liang. 1996. {``Family
+Selection of Child Care Centers: The Influence of Household Support,
+Ethnicity, and Parental Practices.''} \emph{Child Development} 67 (6):
+3320--37. \url{https://doi.org/10.2307/1131789}.
 
@@
 
+\bibitem[\citeproctext]{ref-larsen2015accessibility}
+Larsen, John, Ahmed El-Geneidy, and Farzana Yasmin. 2015. {``The
+Accessibility of Child Care Services: An Analysis of Toronto.''}
+\emph{Journal of Transport Geography} 48: 41--49.
+\url{https://doi.org/10.1016/j.jtrangeo.2015.08.005}.
+
+\bibitem[\citeproctext]{ref-morrissey2010childcare}
+Morrissey, Taryn W. 2010. {``Child Care and Child Development: What We
+Know and Why We Need to Know More.''} \emph{Child Development
+Perspectives} 4 (2): 87--92.
+\url{https://doi.org/10.1111/j.1750-8606.2010.00123.x}.
+
 \bibitem[\citeproctext]{ref-peng2002introduction}
@@
 \emph{Early Childhood Research Quarterly} 26 (3): 320--31.
+
+\bibitem[\citeproctext]{ref-steyerberg2010assessing}
+Steyerberg, Ewout W, Andrew J Vickers, Nancy R Cook, Thomas Gerds,
+Mithat Gonen, Nancy Obuchowski, Michael J Pencina, and Michael W Kattan.
+2010. {``Assessing the Performance of Prediction Models: A Framework for
+Traditional and Novel Measures.''} \emph{Epidemiology} 21 (1): 128--38.
+
+\bibitem[\citeproctext]{ref-tekin2007childcare}
+Tekin, Erdal. 2007. {``Child Care Subsidies, Wages, and Employment of
+Single Mothers.''} \emph{Journal of Human Resources} 42 (2): 453--87.
+\url{https://doi.org/10.3368/jhr.XLII.2.453}.
 

### 2024-12-04 paper/paper.qmd
retry render

@@
 These discrepancies highlight the need for a data-driven approach to understanding and improving the distribution of subsidies among licensed child care centres, ensuring that resources are allocated equitably to maximize their impact.
+
 This study utilizes the Toronto Open Data: Licensed Child Care Centres dataset to explore the factors that affect subsidy allocation to licensed centres.
@@
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+Using a logistic regression model, the analysis identifies three key predictors of subsidy allocation: non-profit governance, participation in the Canada-Wide Early Learning and Child Care (CWELCC) program, and licensed capacity.
+The findings reveal that centres operated by non-profit organizations are significantly more likely to receive subsidies, reflecting a policy preference for supporting entities that prioritize social objectives over profit motives.
+Participation in the CWELCC program emerges as the strongest predictor, highlighting the importance of alignment with affordability initiatives in determining funding priorities.
+Additionally, larger centres with greater licensed capacity are moderately more likely to receive subsidies, indicating that operational scale plays a role in funding decisions, though it is less significant than governance and policy alignment.
+These findings underscore the need for policies that address disparities in subsidy distribution while ensuring that funding supports accessible, high-quality child care for families across Toronto.
+
+The remainder of this paper is structured as follows.
+@sec-data : This section describes the dataset used for the analysis, including its source, key variables, and preprocessing steps, emphasizing its real-world context and relevance to understanding subsidy allocation in Toronto's child care system.
+@sec-model : This section details the logistic regression model employed in the study, including the rationale for its selection, mathematical formulation, and key predictors.
+The model assumptions, diagnostics, and validation methods are also discussed to ensure robustness and reliability.
+@sec-reult : The results of the logistic regression analysis are presented, highlighting the significant predictors of subsidy allocation, ass well as the model's fit.
+@sec-discussion : This section discusses what was done in this study, giving detailed explanation of implications of the findings, limitations and suggestion for future studies.Furthermore, an appendix including supplementary materials and data collection evaluation is provided to ensure transparency and reproducibility.
 
@@
 By translating real-world phenomena into structured data entries, this dataset enables a comprehensive exploration of equity and efficiency in child care funding.
-Detailed data collection analysis is in  appendix
+Detailed data collection analysis is in  appendix.
+@tbl-overview visualized first 10 rows of cleaned data to be used in this study.
 
-```{r}
+```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
 data <- read.csv("../data/02-analysis_data/cleaned_data.csv")
@@
 ```
-
+@fig-subsidy visualizes the distribution of subsidies among licensed child care centres in Toronto.
+The x-axis represents the subsidy status (0 = No, 1 = Yes), while the y-axis shows the count of centres in each category.
+This distribution highlights the government's prioritization of subsidies to a majority of licensed centres, reflecting efforts to enhance accessibility and affordability.
+However, the remaining non-subsidized centres indicate potential gaps or disparities in resource allocation, which could be further explored to ensure equitable funding.
 ```{r}
@@
 **`knitr`** [@citeknitr]: Dynamically integrated code, results, and plots into the final document for seamless reporting.
+
 ## Measurement
 This analysis focuses on the following variables, with a specific emphasis on subsidy as the dependent variable:
-`subsidy`: The binary dependent variable indicating whether a licensed child care centre receives a government subsidy.
-1: The centre is subsidized.
-0: The centre is not subsidized.
-`ward`: `A numeric variable representing the ward number for child care centres.
-`AUSPICE`: The operating auspice of the child care centre, describing its governance and operational model. Possible values include:
-Non-Profit: Centres operated by non-profit organizations, often reinvesting surplus revenues into quality improvements.
-Commercial: For-profit centres operated by private organizations.
-Public: Centres run by public agencies or school boards.
-`bldg_type`: The type of building where the child care centre operates, reflecting its infrastructure. Examples include:
-bldg_typeCommercial Building
-bldg_typeCommunity College/University     
-bldg_typeCommunity Health Centre
-bldg_typeCommunity Rec/Centre - Board Run
-bldg_typeCommunity/Rec Centre - City
-bldg_typeCommunity/Recreation Centre
-bldg_typeHigh Rise Apartment
-bldg_typeHospital/Health Centre
-bldg_typeHouse
-bldg_typeIndustrial Building
-bldg_typeLow Rise Apartment
-bldg_typeOffice Building
-bldg_typeOther
-bldg_typePlace of Worship
-bldg_typePrivate Elementary School
-bldg_typePublic (school closed)
-bldg_typePublic Elementary Special
-bldg_typePublic High School
-bldg_typePublic Middle School
-bldg_typePurpose Built
-bldg_typeSynagogue
-`cwelcc_flag`: A binary variable indicating participation in the Canada-Wide Early Learning and Child Care (CWELCC) program:
-1: The centre participates in CWELCC, enabling reduced child care fees.
-0: The centre does not participate in CWELCC.
-`TOTSPACE`: A numerical variable representing the total licensed capacity (spaces available) for all age groups at a child care centre.
+- `subsidy`: The binary dependent variable indicating whether a licensed child care centre receives a government subsidy.
+- 1: The centre is subsidized.
+- 0: The centre is not subsidized.
+- `ward`: `A numeric variable representing the ward number for child care centres.
+- `AUSPICE`: The operating auspice of the child care centre, describing its governance and operational model. Possible values include:
+- Non-Profit: Centres operated by non-profit organizations, often reinvesting surplus revenues into quality improvements.
+- Commercial: For-profit centres operated by private organizations.
+- Public: Centres run by public agencies or school boards.
+- `bldg_type`: The type of building where the child care centre operates, reflecting its infrastructure. Examples include:
+- bldg_typeCommercial Building
+- bldg_typeCommunity College/University     
+- bldg_typeCommunity Health Centre
+- bldg_typeCommunity Rec/Centre - Board Run
+- bldg_typeCommunity/Rec Centre - City
+- bldg_typeCommunity/Recreation Centre
+- bldg_typeHigh Rise Apartment
+- bldg_typeHospital/Health Centre
+- bldg_typeHouse
+- bldg_typeIndustrial Building
+- bldg_typeLow Rise Apartment
+- bldg_typeOffice Building
+- bldg_typeOther
+- bldg_typePlace of Worship
+- bldg_typePrivate Elementary School
+- bldg_typePublic (school closed)
+- bldg_typePublic Elementary Special
+- bldg_typePublic High School
+- bldg_typePublic Middle School
+- bldg_typePurpose Built
+- bldg_typeSynagogue
+- `cwelcc_flag`: A binary variable indicating participation in the Canada-Wide Early Learning and Child Care (CWELCC) program:
+- 1: The centre participates in CWELCC, enabling reduced child care fees.
+- 0: The centre does not participate in CWELCC.
+- `TOTSPACE`: A numerical variable representing the total licensed capacity (spaces available) for all age groups at a child care centre.
+
 Detailed information about these variables’ information and data structure is presented in @tbl-overview.
@@
 
-# Model
+# Model {#sec-model}
 ## Model Specification
@@
    - Measures the effect of a center being operated as a non-profit compared to the baseline (e.g., commercial auspice) on the log-odds of subsidy allocation.
-   - A positive \( \beta_1 \) increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.
+   - A positive \( \beta_1\) increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.
 
@@
 The analysis integrates results from visual diagnostics, multicollinearity tests, and statistical measures.
-1. Independence of Observations
+### 1. Independence of Observations
 The logistic regression model assumes that the observations are independent of each other.
@@
 There is no clustering or repeated measures within the dataset, which validates this assumption.
-2. Binary Outcome
+### 2. Binary Outcome
 The logistic regression model assumes a binary dependent variable.
@@
 This aligns with the model's requirement, ensuring the suitability of the binomial family for fitting the data.
-3. Linearity of Predictors with the Logit
+### 3. Linearity of Predictors with the Logit
 The @fig-cr The component + residual plots evaluate the linearity of the continuous variables and the relationship between categorical predictors and the logit transformation.
-graph
 
@@
 #| warning: false
-crPlots(reduced_model_2)  # Generate Component + Residual plots
+# Customizing Component + Residual Plots with concise y-axis label
+crPlots(reduced_model_2, ylab = "Component+Residuals")  # Shortened y-axis label
+
 ```
-`TOTSPACE`: The relationship between the total space (TOTSPACE) and the logit appears approximately linear, as indicated by the flat, consistent pattern of residuals around the horizontal axis.
+- `TOTSPACE`: The relationship between the total space (TOTSPACE) and the logit appears approximately linear, as indicated by the flat, consistent pattern of residuals around the horizontal axis.
 This supports the assumption of linearity.
-`CWELCC Flag`: The plot for CWELCC participation shows a horizontal trend, suggesting no significant deviation from linearity. The data support the inclusion of this variable as a binary predictor.
-`AUSPICE`: The residual patterns for categorical levels of AUSPICE (e.g., "Commercial Agency" and "Other") indicate distinct clusters with consistent variability.
+- `CWELCC Flag`: The plot for CWELCC participation shows a horizontal trend, suggesting no significant deviation from linearity. The data support the inclusion of this variable as a binary predictor.
+- `AUSPICE`: The residual patterns for categorical levels of AUSPICE (e.g., "Commercial Agency" and "Other") indicate distinct clusters with consistent variability.
 This suggests the categorical nature of this variable does not violate linearity assumptions.
@@
 
-4. Multicollinearity Assessment
+### 4. Multicollinearity Assessment
 Variance Inflation Factor (VIF):
-To assess multicollinearity among the predictors, the VIF values for the reduced model variables were calculated.
+To assess multicollinearity among the predictors, the VIF values for the reduced model variables were calculated.All VIF values are below 2, well within the acceptable threshold of 5, indicating minimal multicollinearity among the predictors.
+The independence of the predictors ensures the stability of the coefficient estimates.
 
@@
 
-All VIF values are below 2, well within the acceptable threshold of 5, indicating minimal multicollinearity among the predictors.
-The independence of the predictors ensures the stability of the coefficient estimates.
-
 ## Alternative Models
@@
 
-#Result 
+# Result {#sec-result}
 The logistic regression model’s performance metrics are presented in @tbl-coefresult.
 
-```{r}
+```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
 #| label: tbl-coefresult
@@
 ```
+
 The regression model reveals several key observations regarding the predictors and overall goodness of fit.
@@
 Additionally, the TOTSPACE variable has a small but statistically significant effect, with an estimate of 0.014 and a low standard error of 0.003, reflecting robustness.
+In terms of model fit, the dataset includes 750 observations, and the model's AIC (528.1) and BIC (551.2) suggest a reasonable balance between goodness of fit and complexity, as lower values are generally preferred [@burnhammodel].
+The log-likelihood of -259.035 also supports an adequate fit, with a higher (less negative) value indicating better alignment between the model and the data.
+Finally, the RMSE of 0.32 reflects the model's predictive accuracy, with a low value indicating that the model's predictions closely match the observed data.
+Overall, the model performs well but may require refinement, particularly in addressing instability in the AUSPICE: Other variable.
 @fig-cp further visualizes the significance of predictors.
@@
 ```
-In terms of model fit, the dataset includes 750 observations, and the model's AIC (528.1) and BIC (551.2) suggest a reasonable balance between goodness of fit and complexity, as lower values are generally preferred [@burnhammodel].
-The log-likelihood of -259.035 also supports an adequate fit, with a higher (less negative) value indicating better alignment between the model and the data.
-Finally, the RMSE of 0.32 reflects the model's predictive accuracy, with a low value indicating that the model's predictions closely match the observed data.
-Overall, the model performs well but may require refinement, particularly in addressing instability in the AUSPICE: Other variable.
 
@@
 
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-
-# Create a coefficient table
-model_list <- list(
-  "Full Model" = log_model,
-  "AIC Model" = reduced_model_re,
-  "Simplified Model" = reduced_model_2
-)
-
-# Customize the table to display only AIC and Deviance
-modelsummary(
-  model_list,
-  output = "markdown",
-  gof_map = c("AIC", "Deviance")  # Include only AIC and Deviance in the table
-)
-
-```
-
-#Discussion
+#Discussion {#sec-discussion}
 
@@
 
-# Appendix A: Observational Data Methodology for Licensed Child Care Centres in Toronto
+\newpage
 
-## A.1 Population, Frame, and Sample
-A.1.1 Population
+\appendix
+
+# Appendix A: Model Coefficients in Model Selection Process
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+# Create a coefficient table
+model_list <- list(
+  "Full Model" = log_model,
+  "AIC Model" = reduced_model_re,
+  "Simplified Model" = reduced_model_2
+)
+
+# Customize the table to display only AIC and Deviance
+modelsummary(
+  model_list,
+  output = "markdown",
+  gof_map = c("AIC", "Deviance")  # Include only AIC and Deviance in the table
+)
+
+```
+
+# Appendix B: Observational Data Methodology for Licensed Child Care Centres in Toronto
+
+## B.1 Population, Frame, and Sample
+### B.1.1 Population
 The population includes all licensed child care centres in Toronto as recorded in the publicly available dataset provided by Open Toronto.
@@
 Excluded Groups: Informal and unlicensed providers, which disproportionately to lower-income families and those in rural or underserved urban areas.
-A.1.2 Frame
+### B.1.2 Frame
 The dataset represents a comprehensive census of licensed child care centres, reflecting administrative records compiled by the city. 
@@
 Limitations: Static data may fail to capture temporal variations or operational changes, a common limitation noted in administrative datasets.
-A.1.3 Sample
+### B.1.3 Sample
 The dataset uses census sampling of licensed child care centres, ensuring inclusion of all facilities within the licensing framework.
@@
 
-## A.2 Data Collection Methodology
-A.2.1 Observational Data Compilation
+## B.2 Data Collection Methodology
+### B.2.1 Observational Data Compilation
 The dataset is derived from municipal administrative records, which are considered reliable for policy analysis [@cleveland2003benefits].
@@
 Weaknesses: Lack of qualitative insights into service quality or user satisfaction.
-A.2.2 Non-response Handling
+### B.2.2 Non-response Handling
 While the dataset does not involve survey non-response, its exclusion of unlicensed providers creates a systematic gap.
@@
 
-## A.3 Sampling Approach and Trade-offs
-A.3.1 Strengths
+## B.3 Sampling Approach and Trade-offs
+### B.3.1 Strengths
 Comprehensive Coverage: Census sampling ensures no licensed centres are omitted.
@@
 High Validity: Licensing records provide robust validity, as they are subject to regulatory verification [@cleveland2003benefits].
-A.3.2 Limitations
+### B.3.2 Limitations
 Exclusion of Informal Care: Research by Morrissey [@morrissey2010childcare] highlights that informal care is often preferred for flexibility or affordability, making its exclusion a significant limitation.
@@
 
-## A.4 Observational Bias and Measurement Challenges
-A.4.1 Observational Bias
+## B.4 Observational Bias and Measurement Challenges
+### B.4.1 Observational Bias
 Biases inherent in observational datasets include selection bias (due to licensing criteria) and survivorship bias (exclusion of closed centres). 
-A.4.2 Measurement Challenges
+### B.4.2 Measurement Challenges
 Geographic Aggregation: Aggregating data to broader areas can obscure micro-level disparities.
@@
 
-## A.5 Methodological Enhancements and Recommendations
-A.5.1 Enhancements
+## B.5 Methodological Enhancements and Recommendations
+### B.5.1 Enhancements
 Incorporating Temporal Data: Adding longitudinal data could enable trend analysis, echoing the approach of [@fuller1996family].
 Integration with Demographics: Linking with census data would allow for equity analysis, consistent with the methodology used by [@larsen2015accessibility].
-A.5.2 Recommendations
+### B.5.2 Recommendations
 Addressing Informal Care: Future studies should integrate data from community surveys to include informal providers, as suggested by [@morrissey2010childcare].
@@
 
+\newpage
+
 # References

### 2024-12-05 paper/paper-final.qmd
solving render issue

--- 2024-12-04 paper/paper.qmd
@@
 Research indicates that centres in certain neighborhoods or serving specific populations may receive fewer subsidies, even when demand is high [@Johnson_Ryan_Brooks_2012].
-Additionally, characteristics such as enrollment capacity, accreditation status, and program focus (e.g., infant care versus pre-kindergarten) often influence a centre’s eligibility and prioritization for funding [@vines2020accessin].
+Additionally, characteristics such as enrollment capacity, accreditation status, and program focus (e.g., infant care versus pre-kindergarten) often influence a centre’s eligibility and prioritization for funding.
 These discrepancies highlight the need for a data-driven approach to understanding and improving the distribution of subsidies among licensed child care centres, ensuring that resources are allocated equitably to maximize their impact.
@@
 ## Data Overview
-The dataset used in this study was sourced from the [@Childrens_Services] made publicly available by the City of Toronto.
+
+The dataset used in this study was sourced from the [@citeopendatatoronto] made publicly available by the City of Toronto.
 This original raw dataset provides detailed information about licensed child care centres, including 20 variables capturing aspects of their location, operating auspice (e.g., non-profit, public, or commercial), space usage, building type, participation in government programs such as the Canada-Wide Early Learning and Child Care (CWELCC) system, and other operational details.
@@
   head(10) %>%
-  gt() %>%
-  tab_header(
+  gt::gt() %>%
+  gt::tab_header(
     title = "Overview of Cleaned Data",
@@
 ## Method
+
 The dataset used for this study is the **`Licensed Child Care Centres dataset`**, sourced from the [@citeopendatatoronto] It provides detailed information about licensed child care centres in Toronto, capturing aspects such as their governance, capacity, infrastructure, and subsidy status.
@@
 The following are major packages used for this study:
-**`opendatatoronto`**[@citeopendatatoronto]: Used to access and retrieve the Licensed Child Care Centres dataset directly from the City of Toronto's open data portal.
-**`readr`** [@citereadr]: Simplified the import and parsing of raw data into R.
-**`tidyverse`** [@citetidyverse]: Streamlined data manipulation, cleaning, and visualization processes.
-**`dplyr`** [@citedplyr]: Provided tools for filtering, transforming, and summarizing the dataset effectively.
-**`ggplot2`** [@citeggplot2]: Created powerful and flexible visualizations tailored to the analysis needs.
-**`car`** [@citecar]: Used for diagnostic tools, including Variance Inflation Factor (VIF) tests, to assess multicollinearity.
-**`caret`** [@citecaret]: Enabled the development, validation, and evaluation of machine learning models, including training-test splits and performance metrics.
-**`glmnet`** (Friedman et al., 2010): Applied for fitting regularized regression models and feature selection.
-**`stargazer`** [@citestagazer]: Generated formatted regression tables for outputs.
-**`knitr`** [@citeknitr]: Dynamically integrated code, results, and plots into the final document for seamless reporting.
+
+- `opendatatoronto`[@citeopendatatoronto]: Used to access and retrieve the Licensed Child Care Centres dataset directly from the City of Toronto's open data portal.
+
+- `readr` [@citereadr]: Simplified the import and parsing of raw data into R.
+
+- `tidyverse` [@citetidyverse]: Streamlined data manipulation, cleaning, and visualization processes.
+
+- `dplyr` [@citedplyr]: Provided tools for filtering, transforming, and summarizing the dataset effectively.
+
+- `ggplot2` [@citeggplot2]: Created powerful and flexible visualizations tailored to the analysis needs.
+
+- `car` [@citecar]: Used for diagnostic tools, including Variance Inflation Factor (VIF) tests, to assess multicollinearity.
+
+- `caret` [@citecaret]: Enabled the development, validation, and evaluation of machine learning models, including training-test splits and performance metrics.
+
+- `glmnet` (Friedman et al., 2010): Applied for fitting regularized regression models and feature selection.
+
+- `stargazer` [@citestagazer]: Generated formatted regression tables for outputs.
+
+- `knitr` [@citeknitr]: Dynamically integrated code, results, and plots into the final document for seamless reporting.
 
 ## Measurement
+
 This analysis focuses on the following variables, with a specific emphasis on subsidy as the dependent variable:
+
 - `subsidy`: The binary dependent variable indicating whether a licensed child care centre receives a government subsidy.
@@
 ```
+
 @fig-key a heatmap illustrates the correlations between three variables: TOTSPACE (likely representing total space or capacity), subsidy (indicating subsidy status or amount), and cwelcc_flag (potentially denoting eligibility for a specific program or funding).
@@
 # Model {#sec-model}
+
 ## Model Specification
+
 To investigate the factors influencing subsidy allocation to licensed child care centres, a reduced logistic regression model was specified.
@@
 Larger centres are hypothesized to have higher odds of subsidy allocation, as they can accommodate more families and align with policy goals of maximizing access (Forry et al., 2010).
+
 The logistic regression model can be expressed mathematically as follows:
@@
 ### Parameters:
+
 1. **\( \beta_0 \) (Intercept):**
@@
 5. **\( \epsilon \) (Error Term):**
-   - Accounts for unexplained variation in the log-odds of subsidy allocation not captured by the predictors.
+   - Accounts for unexplained variation in the log-odds of subsidy allocation not captured by the predictors
 
 ## Model Justification
+
 The logistic regression model was chosen for this analysis because it is well-suited to the binary nature of the dependent variable, subsidy status (1 = Subsidized, 0 = Not Subsidized).
@@
 ```
+
 ## Model Assumptions
+
 To ensure the validity of the logistic regression model, several key assumptions were assessed, including independence of observations, the appropriateness of a binary outcome, the linearity of predictors with the logit and absence of multicollinearity.
 The analysis integrates results from visual diagnostics, multicollinearity tests, and statistical measures.
+
 ### 1. Independence of Observations
+
 The logistic regression model assumes that the observations are independent of each other.
@@
 There is no clustering or repeated measures within the dataset, which validates this assumption.
+
 ### 2. Binary Outcome
+
 The logistic regression model assumes a binary dependent variable.
@@
 This aligns with the model's requirement, ensuring the suitability of the binomial family for fitting the data.
+
 ### 3. Linearity of Predictors with the Logit
+
 The @fig-cr The component + residual plots evaluate the linearity of the continuous variables and the relationship between categorical predictors and the logit transformation.
@@
 
-```{r}
+```{r,echo=FALSE, results='hide', message=FALSE, warning=FALSE}
 # Calculate VIF
@@
 
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
+```{r,echo=FALSE, message=FALSE, warning=FALSE}
 #| label: tbl-coefresult
@@
   model_list, 
-  output = "markdown", 
   statistic = c("std.error", "p.value")
@@
 This value suggests that the model explains 45.4% of the variance in the outcome variable, indicating a well-fitting model.
-McFadden [@mcfadden1972conditional] proposed this metric as a reliable measure for logistic regression, where values between 0.2 and 0.4 are considered indicative of a good model fit, and values above 0.4 demonstrate an excellent fit.
+Values between 0.2 and 0.4 are considered indicative of a good model fit, and values above 0.4 demonstrate an excellent fit.
 Thus, the model's R^2 value strongly supports its utility in predicting the outcome.
+
 ```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
@@
 ```
+
 The ROC curve in @fig-roc shown further validates the model's classification ability, with an AUC of 0.8998.
@@
 ```
+
 @fig-pvo provides a visual representation of the alignment between the predicted probabilities generated by the logistic regression model and the actual observed binary outcomes.
@@
 The concentration of blue points at the extremes of 0 and 1 highlights that the model makes confident and accurate predictions in many cases
+
 However, some dispersion is observed at lower predicted probabilities, particularly around 0.25 and 0.5.
@@
 The close alignment of predictions with observed outcomes supports the model's reliability in classification tasks.
-This interpretation aligns with other metrics, such as McFadden’s R2R2 [@mcfadden1972conditional] and AUC, which indicate robust overall model performance while pointing to opportunities for refinement.
+This interpretation aligns with other metrics, such as McFadden’s R^2 and AUC, which indicate robust overall model performance while pointing to opportunities for refinement.
 Including this visualization in the results section provides a clear and data-driven assessment of the model's strengths and areas for potential improvement.
 
-#Discussion {#sec-discussion}
+# Discussion {#sec-discussion}
 
@@
 # Appendix A: Model Coefficients in Model Selection Process
+
 ```{r}
@@
   model_list,
-  output = "markdown",
   gof_map = c("AIC", "Deviance")  # Include only AIC and Deviance in the table
@@
 ## B.1 Population, Frame, and Sample
+
 ### B.1.1 Population
+
 The population includes all licensed child care centres in Toronto as recorded in the publicly available dataset provided by Open Toronto.
@@
 Excluded Groups: Informal and unlicensed providers, which disproportionately to lower-income families and those in rural or underserved urban areas.
+
 ### B.1.2 Frame
+
 The dataset represents a comprehensive census of licensed child care centres, reflecting administrative records compiled by the city. 
@@
 Limitations: Static data may fail to capture temporal variations or operational changes, a common limitation noted in administrative datasets.
+
 ### B.1.3 Sample
+
 The dataset uses census sampling of licensed child care centres, ensuring inclusion of all facilities within the licensing framework.
@@
 ## B.2 Data Collection Methodology
+
 ### B.2.1 Observational Data Compilation
+
 The dataset is derived from municipal administrative records, which are considered reliable for policy analysis [@cleveland2003benefits].
@@
 Weaknesses: Lack of qualitative insights into service quality or user satisfaction.
+
 ### B.2.2 Non-response Handling
+
 While the dataset does not involve survey non-response, its exclusion of unlicensed providers creates a systematic gap.
@@
 ## B.3 Sampling Approach and Trade-offs
+
 ### B.3.1 Strengths
+
 Comprehensive Coverage: Census sampling ensures no licensed centres are omitted.
 Geospatial Precision: Geographic coordinates support advanced spatial analysis, aligning with studies like [@larsen2015accessibility] on urban accessibility.
+
 High Validity: Licensing records provide robust validity, as they are subject to regulatory verification [@cleveland2003benefits].
+
 ### B.3.2 Limitations
+
 Exclusion of Informal Care: Research by Morrissey [@morrissey2010childcare] highlights that informal care is often preferred for flexibility or affordability, making its exclusion a significant limitation.
@@
 ## B.4 Observational Bias and Measurement Challenges
+
 ### B.4.1 Observational Bias
+
 Biases inherent in observational datasets include selection bias (due to licensing criteria) and survivorship bias (exclusion of closed centres).
+
 ### B.4.2 Measurement Challenges
+
 Geographic Aggregation: Aggregating data to broader areas can obscure micro-level disparities.
@@
 ## B.5 Methodological Enhancements and Recommendations
+
 ### B.5.1 Enhancements
+
 Incorporating Temporal Data: Adding longitudinal data could enable trend analysis, echoing the approach of [@fuller1996family].
 Integration with Demographics: Linking with census data would allow for equity analysis, consistent with the methodology used by [@larsen2015accessibility].
+
 ### B.5.2 Recommendations
+
 Addressing Informal Care: Future studies should integrate data from community surveys to include informal providers, as suggested by [@morrissey2010childcare].
+
 Dynamic Updates: Regular updates to administrative records would enhance relevance, a recommendation supported.

### 2024-12-10 paper/paper-final.qmd
refine paper

@@
 thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
-date: 2024.12.03
+date: today
 date-format: long
@@
 library(modelsummary)
+library(here)
+library(gt)
+library(arrow)
+library(ggcorrplot)
+```
 
-```
 # Introduction
@@
 Understanding the factors that determine which licensed centres receive subsidies is crucial for policymakers and stakeholders to promote equitable resource allocation and maximize the benefits of early childhood programs.
+
 Licensed child care centres in urban settings like Toronto play a pivotal role in delivering high-quality, structured child care.
 These centres adhere to stringent regulations, ensuring compliance with standards for safety, staffing, and curriculum.
-Research highlights that children attending licensed centres, particularly those supported by subsidies, experience better developmental outcomes (Adams et al., 2013).
-Subsidized centres provide professional environments with trained educators, comprehensive programming, and age-appropriate resources, offering children a strong foundation for lifelong learning and success (Herbst, 2014).
-Subsidies are a cornerstone of this ecosystem, enabling licensed centres to cover operational costs, retain qualified staff, and maintain compliance with regulatory standards, all of which enhance the quality of care provided [@ryan2011impact].
+Research highlights that children attending licensed centres, particularly those supported by subsidies, experience better developmental outcomes.
+Subsidized centres provide professional environments with trained educators, comprehensive programming, and age-appropriate resources, offering children a strong foundation for lifelong learning and success.
+Subsidies are a cornerstone of this ecosystem, enabling licensed centres to cover operational costs, retain qualified staff, and maintain compliance with regulatory standards, all of which enhance the quality of care provided.
+
 Despite their importance, disparities in the allocation of subsidies remain a significant concern.
@@
 The remainder of this paper is structured as follows.
-@sec-data : This section describes the dataset used for the analysis, including its source, key variables, and preprocessing steps, emphasizing its real-world context and relevance to understanding subsidy allocation in Toronto's child care system.
-@sec-model : This section details the logistic regression model employed in the study, including the rationale for its selection, mathematical formulation, and key predictors.
+@sec-data describes the dataset used for the analysis, including its source, key variables, and preprocessing steps, emphasizing its real-world context and relevance to understanding subsidy allocation in Toronto's child care system.
+@sec-model details the logistic regression model employed in the study, including the rationale for its selection, mathematical formulation, and key predictors.
 The model assumptions, diagnostics, and validation methods are also discussed to ensure robustness and reliability.
-@sec-reult : The results of the logistic regression analysis are presented, highlighting the significant predictors of subsidy allocation, ass well as the model's fit.
-@sec-discussion : This section discusses what was done in this study, giving detailed explanation of implications of the findings, limitations and suggestion for future studies.Furthermore, an appendix including supplementary materials and data collection evaluation is provided to ensure transparency and reproducibility.
+@sec-results contains the results of the logistic regression analysis are presented, highlighting the significant predictors of subsidy allocation, ass well as the model's fit.
+@sec-discussion discusses what was done in this study, giving detailed explanation of implications of the findings, limitations and suggestion for future studies.Furthermore, an appendix including supplementary materials and data collection evaluation is provided to ensure transparency and reproducibility.
 
@@
 
-The dataset used in this study was sourced from the [@citeopendatatoronto] made publicly available by the City of Toronto.
+The dataset used in this study was sourced from the [@citeopendatatoronto; @] made publicly available by the City of Toronto.
 This original raw dataset provides detailed information about licensed child care centres, including 20 variables capturing aspects of their location, operating auspice (e.g., non-profit, public, or commercial), space usage, building type, participation in government programs such as the Canada-Wide Early Learning and Child Care (CWELCC) system, and other operational details.
@@
 By translating real-world phenomena into structured data entries, this dataset enables a comprehensive exploration of equity and efficiency in child care funding.
-Detailed data collection analysis is in  appendix.
+Detailed data collection analysis is in the Appendix.
 @tbl-overview visualized first 10 rows of cleaned data to be used in this study.
@@
 ```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-data <- read.csv("../data/02-analysis_data/cleaned_data.csv")
+data <- read_parquet(here("data","02-analysis_data","analysis_data.parquet"))
 ```
@@
 #| tbl-cap: "Sample of Cleaned Data"
-library(gt)
 
@@
   )
+```
 
-```
 @fig-subsidy visualizes the distribution of subsidies among licensed child care centres in Toronto.
@@
 However, the remaining non-subsidized centres indicate potential gaps or disparities in resource allocation, which could be further explored to ensure equitable funding.
+
+所有 table caption fig-cap 要更长，要解释是什么图和图传递的主要信息。
+
 ```{r}
@@
 #| warning: false
+
 # Calculate percentages
@@
 
+few more graphs showing relationship between outcome and predictors
+
 ## Method
@@
 The dependent variable **`subsidy`**, originally recorded as "Yes"/"No," was encoded as 1 for subsidized and 0 for non-subsidized centres.
-Similarly, the **`cwelcc_flag`** variable was converted into a binary format (1 =Y, 0 =N).
-Categorical variables such as **`bldg_type`** and **`AUSPICE`** were consolidated to simplify analysis and address sparse categories.
+Similarly, the **cwelcc_flag** variable was converted into a binary format (1 =Y, 0 =N).
+Categorical variables such as **building type** and **`AUSPICE`** were consolidated to simplify analysis and address sparse categories.
 Additionally, missing and irrelevant records were removed to ensure the dataset was both accurate and meaningful for the research objectives.
@@
 
-- `glmnet` (Friedman et al., 2010): Applied for fitting regularized regression models and feature selection.
+- `glmnet` [@]: Applied for fitting regularized regression models and feature selection.
 
@@
 - Public: Centres run by public agencies or school boards.
-- `bldg_type`: The type of building where the child care centre operates, reflecting its infrastructure. Examples include:
+- `bldg_type`: The type of building where the child care centre operates, reflecting its infrastructure.
+
+Examples include:
+
 - bldg_typeCommercial Building
@@
 - bldg_typeSynagogue
+
 - `cwelcc_flag`: A binary variable indicating participation in the Canada-Wide Early Learning and Child Care (CWELCC) program:
@@
 #| warning: false
+
 ggplot(data, aes(x = AUSPICE, fill = as.factor(subsidy))) +
@@
   )
-
 ```
@@
 #| warning: false
-library(ggcorrplot)
+
 cor_matrix <- cor(data %>% select(TOTSPACE, subsidy, cwelcc_flag), use = "complete.obs")
@@
 The model includes three key predictors:
+
 `Operating Auspice (AUSPICE)`: A categorical variable indicating the governance model of the child care centre (e.g., Non-Profit Agency, Other).
 Non-profit agencies are hypothesized to be positively associated with subsidy allocation, consistent with previous research emphasizing their prioritization in funding schemes (Cleveland & Krashinsky, 2005).
+
 `Participation in the CWELCC Program (cwelcc_flag)`: A binary variable capturing whether the centre participates in the Canada-Wide Early Learning and Child Care program (1 = participates, 0 = does not participate).
 Centres participating in this initiative are expected to have higher odds of receiving subsidies due to their alignment with government objectives of affordability and accessibility (Friendly & Ballantyne, 2022).
+
 `Total Space (TOTSPACE)`: A continuous variable representing the number of licensed spaces available in the centre.
-Larger centres are hypothesized to have higher odds of subsidy allocation, as they can accommodate more families and align with policy goals of maximizing access (Forry et al., 2010).
+Larger centres are hypothesized to have higher odds of subsidy allocation, as they can accommodate more families and align with policy goals of maximizing access [@].
 
 The logistic regression model can be expressed mathematically as follows:
-\[
-\text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{CWELCC Participation}) + \beta_3 (\text{Total Space}) + \epsilon
-\]
+
+$$
+\text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{CWELCC Participation}) + \beta_3 (\text{Total Space})
+$$
 
 Where:
+
 \begin{itemize}
@@
 
-1. **\( \beta_0 \) (Intercept):**
+1. **$\beta_0$ (Intercept):**
+
    - Represents the baseline log-odds of subsidy allocation when all predictors are set to their reference categories or zero values.
@@
 
-2. **\( \beta_1 (\text{Non-Profit Auspice}) \):**
+2. **$\beta_1$ (Non-Profit Auspice):**
+
    - Measures the effect of a center being operated as a non-profit compared to the baseline (e.g., commercial auspice) on the log-odds of subsidy allocation.
-   - A positive \( \beta_1\) increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.
+   - A positive $\beta_1$ increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.
 
-3. **\( \beta_2 (\text{CWELCC Participation}) \):**
+3. **$\beta_2$ (CWELCC Participation):**
    - Captures the influence of participating in the Canada-Wide Early Learning and Child Care (CWELCC) program on the log-odds of subsidy allocation.
 
-4. **\( \beta_3 (\text{Total Space}) \):**
+4. **$\beta_3$ (Total Space):**
    - Represents the effect of the number of licensed child care spaces (a continuous variable) on the log-odds of subsidy allocation.
 
-5. **\( \epsilon \) (Error Term):**
+5. **$\epsilon$ (Error Term):**
    - Accounts for unexplained variation in the log-odds of subsidy allocation not captured by the predictors
@@
 This makes it particularly useful for guiding policy decisions, as coefficients can be directly converted into odds ratios for actionable insights [@peng2002introduction].
+
 The ward variable was excluded because it lacked statistical significance and added redundancy, as its effects were captured by other predictors like CWELCC participation and total space.
@@
 Excluding it improved parsimony and interpretability.
+
 The final model retained operating auspice, CWELCC participation, and total space, as these predictors are strongly supported by theory and data.
@@
 
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Encode categorical variables
-data$AUSPICE <- as.factor(data$AUSPICE)
-data$bldg_type <- as.factor(data$bldg_type)
-
-# Split the data into training and testing sets
-set.seed(1008047418)
-train_index <- createDataPartition(data$subsidy, p = 0.7, list = FALSE)
-train_data <- data[train_index, ]
-test_data <- data[-train_index, ]
-
-# Fit logistic regression model
-log_model <- glm(subsidy ~ ., data = train_data, family = binomial)
-
-# Summary of the model
-summary(log_model)
-
-```
-
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Stepwise selection based on AIC
-step_model_aic <- step(log_model, direction = "both", trace = TRUE)
-
-# Summary of models
-summary(step_model_aic)  # AIC-based selected model
-```
-
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Create a binary variable for "Non Profit Agency"
-train_data$AUSPICE_NonProfit <- ifelse(train_data$AUSPICE == "Non Profit Agency", 1, 0)
-
-# Refit the model with the binary variable for AUSPICE
-reduced_model_re2 <- glm(formula = subsidy ~ AUSPICE_NonProfit + bldg_type + cwelcc_flag + TOTSPACE, 
-                       family = binomial, data = train_data)
-
-# Summary of the updated model
-summary(reduced_model_re2)
-
-```
-
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-
-# Refit the best aic model
-reduced_model_re <- glm(formula = subsidy ~ AUSPICE + bldg_type + cwelcc_flag + TOTSPACE, 
-    family = binomial, data = train_data)
-summary(reduced_model_re)
-
-```
-
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Refit model by removing non-significant variables
-reduced_model_2 <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE, 
-    family = binomial, data = train_data)
-summary(reduced_model_2)
-```
-
 ## Model Assumptions
 
-To ensure the validity of the logistic regression model, several key assumptions were assessed, including independence of observations, the appropriateness of a binary outcome, the linearity of predictors with the logit and absence of multicollinearity.
-The analysis integrates results from visual diagnostics, multicollinearity tests, and statistical measures.
-
-### 1. Independence of Observations
-
-The logistic regression model assumes that the observations are independent of each other.
-In this analysis, each data point corresponds to an individual child care center, ensuring independence.
-There is no clustering or repeated measures within the dataset, which validates this assumption.
-
-### 2. Binary Outcome
-
-The logistic regression model assumes a binary dependent variable.
-In this case, the outcome variable, `subsidy`, is binary, indicating whether a child care center receives a subsidy (1 = Subsidized, 0 = Not Subsidized).
-This aligns with the model's requirement, ensuring the suitability of the binomial family for fitting the data.
-
-### 3. Linearity of Predictors with the Logit
-
-The @fig-cr The component + residual plots evaluate the linearity of the continuous variables and the relationship between categorical predictors and the logit transformation.
-
-```{r}
-#| label: fig-cr
-#| fig-cap: "CR Plot for Linearity Chekck"
-#| echo: false
-#| message: false
-#| warning: false
-# Customizing Component + Residual Plots with concise y-axis label
-crPlots(reduced_model_2, ylab = "Component+Residuals")  # Shortened y-axis label
-
-```
-- `TOTSPACE`: The relationship between the total space (TOTSPACE) and the logit appears approximately linear, as indicated by the flat, consistent pattern of residuals around the horizontal axis.
-This supports the assumption of linearity.
-- `CWELCC Flag`: The plot for CWELCC participation shows a horizontal trend, suggesting no significant deviation from linearity. The data support the inclusion of this variable as a binary predictor.
-- `AUSPICE`: The residual patterns for categorical levels of AUSPICE (e.g., "Commercial Agency" and "Other") indicate distinct clusters with consistent variability.
-This suggests the categorical nature of this variable does not violate linearity assumptions.
-Overall, the visual inspection suggests that the linearity assumption for the predictors with the logit is met.
-
-### 4. Multicollinearity Assessment
-Variance Inflation Factor (VIF):
-To assess multicollinearity among the predictors, the VIF values for the reduced model variables were calculated.All VIF values are below 2, well within the acceptable threshold of 5, indicating minimal multicollinearity among the predictors.
-The independence of the predictors ensures the stability of the coefficient estimates.
-
-```{r,echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Calculate VIF
-vif_values <- vif(reduced_model_2)
-```
+Detailed model assumption check is in @sec-model-details.
 
 ## Alternative Models
+
 Alternative models like decision trees and random forests were considered but were found less interpretable for policy-focused analyses.
@@
 
-# Result {#sec-result}
+# Results {#sec-results}
+
 The logistic regression model’s performance metrics are presented in @tbl-coefresult.
@@
 #| tbl-cap: "Regression Result"
+
+# Load model 
+model <- readRDS(file = here("models","final_model.rds"))
+
 # Regression table with standard errors and p-values
 model_list <- list(
-  "Final Model" = reduced_model_2
+  "Final Model" = model
 )
@@
 # Extract coefficients and confidence intervals
-tidy_model <- broom::tidy(reduced_model_2, conf.int = TRUE)
+tidy_model <- broom::tidy(model, conf.int = TRUE)
 
@@
 
-The evaluation of the logistic regression model shows strong performance based on McFadden’s R^2 and the Area Under the Receiver Operating Characteristic Curve (AUC).
-McFadden’s R^2 which is a pseudo-R^2 metric specifically designed for logistic regression, was calculated as 0.454.
+The evaluation of the logistic regression model shows strong performance based on McFadden’s $R^2$ and the Area Under the Receiver Operating Characteristic Curve (AUC).
+McFadden’s $R^2$ which is a pseudo-$R^2$ metric specifically designed for logistic regression, was calculated as 0.454.
 This value suggests that the model explains 45.4% of the variance in the outcome variable, indicating a well-fitting model.
 Values between 0.2 and 0.4 are considered indicative of a good model fit, and values above 0.4 demonstrate an excellent fit.
-Thus, the model's R^2 value strongly supports its utility in predicting the outcome.
-
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Calculate log-likelihood of the fitted model
-log_likelihood_fitted <- logLik(reduced_model_2)
-# Fit the null model (model with intercept only)
-null_model <- glm(subsidy ~ 1, data = train_data, family = binomial)
-log_likelihood_null <- logLik(null_model)
-# McFadden's R-squared
-mcfadden_r2 <- 1 - as.numeric(log_likelihood_fitted / log_likelihood_null)
-# Print the result
-print(paste("McFadden's R-squared:", round(mcfadden_r2, 6)))
-```
+Thus, the model's $R^2$ value strongly supports its utility in predicting the outcome.
 
@@
 # ROC Curve and AUC
-roc_curve <- roc(test_data$subsidy, predict(reduced_model_2, newdata = test_data, type = "response"))
-plot(roc_curve, main = "ROC Curve")
-auc(roc_curve)
-
+roc_curve <- roc(data$subsidy, 
+                 predict(model, 
+                         newdata = data, type = "response"))
+plot(roc_curve, main = "ROC Curve", print.auc=T)
 ```
@@
 # Generate predicted probabilities for the test dataset
-test_data$predicted_prob <- predict(reduced_model_2, newdata = test_data, type = "response")
+data$predicted_prob <- predict(model, newdata = data, type = "response")
 
 # Predicted vs. Observed Scatterplot
-ggplot(test_data, aes(x = predicted_prob, y = subsidy)) +
+ggplot(data, aes(x = predicted_prob, y = subsidy)) +
   geom_jitter(width = 0.02, height = 0.02, alpha = 0.6, color = "blue") +
@@
 The red diagonal line serves as the reference for perfect calibration, where predicted probabilities perfectly match observed outcomes.
+
 The clustering of blue points near 0 and 1 along the y-axis indicates that the model effectively distinguishes between the two classes, a key goal in binary classification modeling.
@@
 Such discrepancies could indicate areas where further refinement of the model or predictors is necessary.
-These deviations could also be linked to specific subgroups or predictor interactions, necessitating additional diagnostics or recalibration, as suggested by Steyerberg et al.
-[@steyerberg2010assessing].
+These deviations could also be linked to specific subgroups or predictor interactions, necessitating additional diagnostics or recalibration [@steyerberg2010assessing].
+
 Overall, this graph demonstrates that the model is well-calibrated and effective in its predictions, with minor limitations at lower probability levels.
 The close alignment of predictions with observed outcomes supports the model's reliability in classification tasks.
-This interpretation aligns with other metrics, such as McFadden’s R^2 and AUC, which indicate robust overall model performance while pointing to opportunities for refinement.
+This interpretation aligns with other metrics, such as McFadden’s $R^2$ and AUC, which indicate robust overall model performance while pointing to opportunities for refinement.
 Including this visualization in the results section provides a clear and data-driven assessment of the model's strengths and areas for potential improvement.
@@
 
-# Appendix A: Model Coefficients in Model Selection Process
+# Appendix {-}
+
+# Model Assumption {#sec-model-details}
+
+To ensure the validity of the logistic regression model, several key assumptions were assessed, including independence of observations, the appropriateness of a binary outcome, the linearity of predictors with the logit and absence of multicollinearity.
+The analysis integrates results from visual diagnostics, multicollinearity tests, and statistical measures.
+
+### 1. Independence of Observations
+
+The logistic regression model assumes that the observations are independent of each other.
+In this analysis, each data point corresponds to an individual child care center, ensuring independence.
+There is no clustering or repeated measures within the dataset, which validates this assumption.
+
+### 2. Binary Outcome
+
+The logistic regression model assumes a binary dependent variable.
+In this case, the outcome variable, `subsidy`, is binary, indicating whether a child care center receives a subsidy (1 = Subsidized, 0 = Not Subsidized).
+This aligns with the model's requirement, ensuring the suitability of the binomial family for fitting the data.
+
+### 3. Linearity of Predictors with the Logit
+
+The @fig-cr The component + residual plots evaluate the linearity of the continuous variables and the relationship between categorical predictors and the logit transformation.
 
 ```{r}
+#| label: fig-cr
+#| fig-cap: "CR Plot for Linearity Chekck"
 #| echo: false
+#| message: false
 #| warning: false
-#| message: false
-# Create a coefficient table
-model_list <- list(
-  "Full Model" = log_model,
-  "AIC Model" = reduced_model_re,
-  "Simplified Model" = reduced_model_2
-)
-
-# Customize the table to display only AIC and Deviance
-modelsummary(
-  model_list,
-  gof_map = c("AIC", "Deviance")  # Include only AIC and Deviance in the table
-)
-
+# Customizing Component + Residual Plots with concise y-axis label
+crPlots(model, ylab = "Component+Residuals")  # Shortened y-axis label
 ```
 
-# Appendix B: Observational Data Methodology for Licensed Child Care Centres in Toronto
+- `TOTSPACE`: The relationship between the total space (TOTSPACE) and the logit appears approximately linear, as indicated by the flat, consistent pattern of residuals around the horizontal axis.
+This supports the assumption of linearity.
 
-## B.1 Population, Frame, and Sample
+- `CWELCC Flag`: The plot for CWELCC participation shows a horizontal trend, suggesting no significant deviation from linearity. The data support the inclusion of this variable as a binary predictor.
 
-### B.1.1 Population
+- `AUSPICE`: The residual patterns for categorical levels of AUSPICE (e.g., "Commercial Agency" and "Other") indicate distinct clusters with consistent variability.
+This suggests the categorical nature of this variable does not violate linearity assumptions.
+Overall, the visual inspection suggests that the linearity assumption for the predictors with the logit is met.
+
+### 4. Multicollinearity Assessment
+
+Variance Inflation Factor (VIF):
+
+To assess multicollinearity among the predictors, the VIF values for the reduced model variables were calculated.All VIF values are below 2, well within the acceptable threshold of 5, indicating minimal multicollinearity among the predictors.
+The independence of the predictors ensures the stability of the coefficient estimates.
+
+```{r,echo=FALSE, results='hide', message=FALSE, warning=FALSE}
+# Calculate VIF
+vif_values <- vif(model)
+```
+
+# Observational Data Methodology for Licensed Child Care Centres in Toronto
+
+## Population, Frame, and Sample
+
+### Population
 
@@
 Represented Groups: Centres adhering to provincial licensing requirements, as emphasized by Cleveland and Krashinsky [@cleveland2003benefits], who note that licensed care is generally associated with higher quality standards.
+
 Excluded Groups: Informal and unlicensed providers, which disproportionately to lower-income families and those in rural or underserved urban areas.
 
-### B.1.2 Frame
+### Frame
 
 The dataset represents a comprehensive census of licensed child care centres, reflecting administrative records compiled by the city.
+
 Strengths: Comprehensive coverage reduces selection bias and enhances geographic representativeness.
+
 Limitations: Static data may fail to capture temporal variations or operational changes, a common limitation noted in administrative datasets.
 
-### B.1.3 Sample
+### Sample
 
 The dataset uses census sampling of licensed child care centres, ensuring inclusion of all facilities within the licensing framework.
+
 Advantages: Census data minimizes sampling error and provides a reliable basis for spatial and capacity analysis.
+
 Drawbacks: Lack of informal care data may lead to underrepresentation of actual child care resources, echoing findings by [@tekin2007childcare] that informal care plays a critical role in many families’ child care arrangements.
 
-## B.2 Data Collection Methodology
+## Data Collection Methodology
 
-### B.2.1 Observational Data Compilation
+### Observational Data Compilation
 
@@
 Licensing authorities collect this data as part of routine compliance monitoring, ensuring high accuracy.
+
 Strengths: Administrative data is less prone to recall bias compared to survey data.
+
 Weaknesses: Lack of qualitative insights into service quality or user satisfaction.
 
-### B.2.2 Non-response Handling
+### Non-response Handling
 
@@
 
-## B.3 Sampling Approach and Trade-offs
+## Sampling Approach and Trade-offs
 
-### B.3.1 Strengths
+### Strengths
 
@@
 
-### B.3.2 Limitations
+### Limitations
 
@@
 
-## B.4 Observational Bias and Measurement Challenges
+## Observational Bias and Measurement Challenges
 
-### B.4.1 Observational Bias
+### Observational Bias
 
@@
 
-### B.4.2 Measurement Challenges
+### Measurement Challenges
 
@@
 
-## B.5 Methodological Enhancements and Recommendations
+## Methodological Enhancements and Recommendations
 
-### B.5.1 Enhancements
+### Enhancements
 
 Incorporating Temporal Data: Adding longitudinal data could enable trend analysis, echoing the approach of [@fuller1996family].
+
 Integration with Demographics: Linking with census data would allow for equity analysis, consistent with the methodology used by [@larsen2015accessibility].
 
-### B.5.2 Recommendations
+### Recommendations
 
@@
 Dynamic Updates: Regular updates to administrative records would enhance relevance, a recommendation supported.
+
 Geospatial Enhancements: Including data on transit access or neighborhood socioeconomic conditions could enrich spatial analyses, aligning with findings by [@tekin2007childcare]

### 2024-12-10 models/plumber.R

@@ -1,0 +1,46 @@
+library(plumber)
+library(tidyverse)
+
+# Load the model
+model <- readRDS("final_model.rds")
+
+# Define the model version
+version_number <- "0.0.1"
+
+# Define the predictors for the model
+variables <- list(
+  AUSPICE = "The type of agency: 'Commercial Agency', 'Non Profit Agency', or 'Other'.",
+  cwelcc_flag = "A binary flag indicating CWELCC participation (0 or 1).",
+  TOTSPACE = "The total space available (numeric)."
+)
+
+#* @param AUSPICE The type of agency: 'Commercial Agency', 'Non Profit Agency', or 'Other'.
+#* @param cwelcc_flag The CWELCC flag (0 or 1).
+#* @param TOTSPACE The total space available (numeric).
+#* @get /predict_subsidy
+predict_subsidy <- function(AUSPICE = "Non Profit Agency", cwelcc_flag = 1, TOTSPACE = 100) {
+  # Convert inputs to appropriate types
+  AUSPICE <- as.character(AUSPICE)
+  cwelcc_flag <- as.numeric(cwelcc_flag)
+  TOTSPACE <- as.numeric(TOTSPACE)
+  
+  # Prepare the payload as a data frame
+  payload <- data.frame(
+    AUSPICE = AUSPICE,
+    cwelcc_flag = cwelcc_flag,
+    TOTSPACE = TOTSPACE
+  )
+  
+  # Use the logistic regression model to predict probabilities
+  predicted_probability <- predict(model, newdata = payload, type = "response")
+  
+  # Classify based on probability threshold of 0.5
+  predicted_class <- ifelse(predicted_probability > 0.5, "Yes", "No")
+  
+  # Return results as a list
+  result <- list(
+    "Predicted to receive subsidy or not" = predicted_class
+  )
+  
+  return(result)
+}

### 2024-12-10 scripts/00-simulate_data.R

@@ -7,12 +7,9 @@
 # Pre-requisites: The `dplyr` package must be installed and loaded
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
-
 #### Workspace setup ####
-
 # Load necessary library
 library(dplyr)
-
 
 #### Simulate data ####
 
@@ -47,9 +44,5 @@ simulated_data <- data.frame(
 # Display first few rows of the simulated dataset
 head(simulated_data)
 
-
-
-
-
 #### Save data ####
-write_csv(simulated_data, "../data/00-simulated_data/simulated_data1.csv")
+write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")

### 2024-12-10 scripts/01-test_simulated_data.R

@@ -13,7 +13,7 @@
 #### Workspace setup ####
 library(tidyverse)
 
-data <- read_csv("../data/00-simulated_data/simulated_data1.csv")
+data <- read_csv("data/00-simulated_data/simulated_data.csv")
 
 # Test if the data was successfully loaded
 if (exists("data")) {

### 2024-12-10 scripts/02-download_data.R

@@ -13,25 +13,19 @@ library(opendatatoronto)
 library(tidyverse)
 library(readr)
 
-
 #### Download data ####
-# Search for a specific package on OpenDataToronto by keyword ("Marriage Licence Statistics")
-marriage_licence_packages <- search_packages("Licensed Child Care Centres")
-marriage_licence_packages
+# Search for a specific package on OpenDataToronto by keyword ("childcare Licence Statistics")
+childcare_licence_packages <- search_packages("Licensed Child Care Centres")
+childcare_licence_packages
 # Retrieve a list of all resources (datasets) available within the found package
-marriage_licence_resources <- marriage_licence_packages %>%
+childcare_licence_resources <- childcare_licence_packages %>%
   list_package_resources()
-# Display the list of resources available in the "Marriage Licence Statistics" package
-marriage_licence_resources
+# Display the list of resources available in the "childcare Licence Statistics" package
+childcare_licence_resources
 # Download the .csv dataset
-marriage_licence_statistics <- marriage_licence_resources[3,] %>%
+childcare_licence_statistics <- childcare_licence_resources[3,] %>%
   get_resource()
-marriage_licence_statistics
-write_csv(marriage_licence_statistics, "../data/01-raw_data/raw_data.csv")
-
+childcare_licence_statistics
 
 #### Save data ####
-marriage_licence_statistics
-write_csv(marriage_licence_statistics, "../data/01-raw_data/raw_data.csv")
-
-         
+write_csv(childcare_licence_statistics, "data/01-raw_data/raw_data.csv")

### 2024-12-10 scripts/03-clean_data.R

@@ -4,15 +4,16 @@
 # Date: 25 November 2024 
 # Contact: minglu.ma@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: The `dplyr` and 'readr' packages must be installed and loaded
+# Pre-requisites: The `dplyr`, `arrow`, and 'readr' packages must be installed and loaded
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 #### Workspace setup ####
 library(dplyr)
 library(readr)
-#### Clean data ####
-data <- read.csv("../data/01-raw_data/raw_data.csv")
+library(arrow)
 
+#### Clean data ####
+data <- read.csv("data/01-raw_data/raw_data.csv")
 
 # Relevant columns
 relevant_columns <- c("ward", "AUSPICE", "bldg_type", "cwelcc_flag", "TOTSPACE", "subsidy")
@@ -39,4 +40,4 @@ cleaned_data <- data %>%
   )
 
 #### Save data ####
-write_csv(cleaned_data, "../data/02-analysis_data/cleaned_data.csv")
+write_parquet(cleaned_data, "data/02-analysis_data/analysis_data.parquet")

### 2024-12-10 scripts/05-exploratory_data_analysis.R

@@ -7,15 +7,16 @@
 # Pre-requisites: The `dplyr`,'readr', 'ggplot2', 'reshape' and 'gridExtra'packages must be installed and loaded
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
-
 #### Workspace setup ####
 library(dplyr)
 library(readr)
 library(ggplot2)
 library(reshape2)
 library(gridExtra)
+library(arrow)
+
 #### Read data ####
-data <- read_csv("../data/02-analysis_data/cleaned_data.csv")
+data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 ### EDA ####
 head(data)
@@ -66,6 +67,7 @@ plot4 <- ggplot(data, aes(x = reorder(bldg_type, -table(bldg_type)[bldg_type])))
   theme_minimal() +
   theme(axis.text.y = element_text(size = 5),
         plot.title = element_text(size = 8))  # Reduce title text size
+
 # 5. Distribution of Ward (Bar Plot)
 # Create a bar plot for ward variable
 plot5 <-ggplot(data, aes(x = ward)) +
@@ -80,7 +82,7 @@ plot5 <-ggplot(data, aes(x = ward)) +
     axis.text.x = element_text(size = 8),  # Rotate x-axis labels for readability
     plot.title = element_text(size = 8)
   )
+
 # Increase plot area and use grid.arrange
 combined_plot <- grid.arrange(plot1, plot2, plot3, plot4, plot5, ncol = 2)
-
 

### 2024-12-10 scripts/06-model_data.R

@@ -4,13 +4,15 @@
 # Date: 28 November 2024 
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `caret` and 'ggplot2' package must be installed and loaded
+# Pre-requisites: The `caret`, `arrow`, and 'ggplot2' package must be installed and loaded
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 #### Workspace setup ####
 library(caret)
 library(ggplot2)
-data <- read.csv("../data/02-analysis_data/cleaned_data.csv")
+library(arrow)
+
+data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 #full model
 # Encode categorical variables
 data$AUSPICE <- as.factor(data$AUSPICE)
@@ -39,3 +41,80 @@ reduced_model_2 <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE,
                        family = binomial, data = train_data)
 summary(reduced_model_2)
 
+anova(reduced_model_2, step_model_aic)
+
+reduced_model_2 <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE, 
+                       family = binomial, data = data)
+saveRDS(reduced_model_2, file="models/final_model.rds")
+
+# 1.
+#Encode categorical variables
+data$AUSPICE <- as.factor(data$AUSPICE)
+data$bldg_type <- as.factor(data$bldg_type)
+
+# Split the data into training and testing sets
+set.seed(1008047418)
+train_index <- createDataPartition(data$subsidy, p = 0.7, list = FALSE)
+train_data <- data[train_index, ]
+test_data <- data[-train_index, ]
+
+# Fit logistic regression model
+log_model <- glm(subsidy ~ ., data = train_data, family = binomial)
+
+# Summary of the model
+summary(log_model)
+
+# 2.
+# Stepwise selection based on AIC
+step_model_aic <- step(log_model, direction = "both", trace = TRUE)
+
+# Summary of models
+summary(step_model_aic)  # AIC-based selected model
+
+# 3.
+# Create a binary variable for "Non Profit Agency"
+train_data$AUSPICE_NonProfit <- ifelse(train_data$AUSPICE == "Non Profit Agency", 1, 0)
+
+# Refit the model with the binary variable for AUSPICE
[…]

### 2024-12-11 scripts/01-test_simulated_data.R
update 01,04,06 scripts

@@ -5,13 +5,14 @@
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
+  # - The `tidyverse` and `testthat` packages must be installed and loaded
   # - 00-simulate_data.R must have been run
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(testthat)
 
 data <- read_csv("data/00-simulated_data/simulated_data.csv")
 
@@ -24,26 +25,22 @@ if (exists("data")) {
 
 
 #### Test data ####
+# Test if values in `ward` are greater than 0
+test_that("All values in 'ward' are greater than 0", {
+  expect_true(all(data$ward > 0))
+})
 
-# 1. Test if values in `ward` are greater than 0
-ward_test <- all(data$ward > 0)
-cat("Test 1: All values in 'ward' are greater than 0:", ward_test, "\n")
+# Test if values in `TOTSPACE` (Total Space) are greater than 0
+test_that("All values in 'TOTSPACE' are greater than 0", {
+  expect_true(all(data$TOTSPACE > 0))
+})
 
-# 2. Test if values in `TOTSPACE` (Total Space) are greater than 0
-totspace_test <- all(data$TOTSPACE > 0)
-cat("Test 2: All values in 'TOTSPACE' are greater than 0:", totspace_test, "\n")
+# Test if values in `subsidy` are either 0 or 1
+test_that("All values in 'subsidy' are either 0 or 1", {
+  expect_true(all(data$subsidy %in% c(0, 1)))
+})
 
-# 3. Test if values in `subsidy` are either 0 or 1
-subsidy_test <- all(data$subsidy %in% c(0, 1))
-cat("Test 3: All values in 'subsidy' are either 0 or 1:", subsidy_test, "\n")
-
-# 4. Test if values in `cwelcc_flag` are either 0 or 1
-cwelcc_flag_test <- all(data$cwelcc_flag %in% c(0, 1))
-cat("Test 4: All values in 'cwelcc_flag' are either 0 or 1:", cwelcc_flag_test, "\n")
-
-# Combine results
-if (ward_test & totspace_test & subsidy_test & cwelcc_flag_test) {
-  cat("All tests passed! The dataset meets the specified conditions.\n")
-} else {
[…]

### 2024-12-11 scripts/04-test_analysis_data.R

@@ -5,13 +5,14 @@
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-# - The `readr` package must be installed and loaded
+# - The `arrow` and `testthat` packages must be installed and loaded
 # - 03-clean_data.R must have been run
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 #### Workspace setup ####
-library("readr")
-data <- read_csv("../data/02-analysis_data/cleaned.csv")
+library("arrow")
+
+data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 
 #### Test data ####
@@ -24,26 +25,24 @@ if (exists("data")) {
 
 
 #### Test data ####
+# Test if values in `ward` are greater than 0
+test_that("All values in 'ward' are greater than 0", {
+  expect_true(all(data$ward > 0))
+})
 
-# 1. Test if values in `ward` are greater than 0
-ward_test <- all(data$ward > 0)
-cat("Test 1: All values in 'ward' are greater than 0:", ward_test, "\n")
+# Test if values in `TOTSPACE` (Total Space) are greater than 0
+test_that("All values in 'TOTSPACE' are greater than 0", {
+  expect_true(all(data$TOTSPACE > 0))
+})
 
-# 2. Test if values in `TOTSPACE` (Total Space) are greater than 0
-totspace_test <- all(data$TOTSPACE > 0)
-cat("Test 2: All values in 'TOTSPACE' are greater than 0:", totspace_test, "\n")
+# Test if values in `subsidy` are either 0 or 1
+test_that("All values in 'subsidy' are either 0 or 1", {
+  expect_true(all(data$subsidy %in% c(0, 1)))
+})
 
-# 3. Test if values in `subsidy` are either 0 or 1
-subsidy_test <- all(data$subsidy %in% c(0, 1))
-cat("Test 3: All values in 'subsidy' are either 0 or 1:", subsidy_test, "\n")
+# Test if values in `cwelcc_flag` are either 0 or 1
+test_that("All values in 'cwelcc_flag' are either 0 or 1", {
+  expect_true(all(data$cwelcc_flag %in% c(0, 1)))
+})
 
-# 4. Test if values in `cwelcc_flag` are either 0 or 1
-cwelcc_flag_test <- all(data$cwelcc_flag %in% c(0, 1))
[…]

### 2024-12-11 scripts/06-model_data.R

@@ -4,16 +4,16 @@
 # Date: 28 November 2024 
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `caret`, `arrow`, and 'ggplot2' package must be installed and loaded
+# Pre-requisites: The `caret`, `arrow`, `modelsummary` and 'ggplot2' package must be installed and loaded
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 #### Workspace setup ####
 library(caret)
 library(ggplot2)
 library(arrow)
+library(modelsummary)
 
 data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
-#full model
 # Encode categorical variables
 data$AUSPICE <- as.factor(data$AUSPICE)
 data$bldg_type <- as.factor(data$bldg_type)
@@ -24,82 +24,33 @@ train_index <- createDataPartition(data$subsidy, p = 0.7, list = FALSE)
 train_data <- data[train_index, ]
 test_data <- data[-train_index, ]
 
-# Fit logistic regression model
-log_model <- glm(subsidy ~ ., data = train_data, family = binomial)
-
+# Fit logistic regression model (full model)
+full_model <- glm(subsidy ~ ., data = train_data, family = binomial)
 # Summary of the model
-summary(log_model)
+summary(full_model)
 
 # Stepwise selection based on AIC
-step_model_aic <- step(log_model, direction = "both", trace = TRUE)
-
-# Summary of models
+step_model_aic <- step(full_model, direction = "both", trace = TRUE)
 summary(step_model_aic)  # AIC-based selected model
 
-# Refit model by removing non-significant variables
-reduced_model_2 <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE, 
+# Refit model by removing non-significant variables to obtain the reduced model
+reduced_model <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE, 
                        family = binomial, data = train_data)
-summary(reduced_model_2)
+summary(reduced_model)
 
-anova(reduced_model_2, step_model_aic)
-
-reduced_model_2 <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE, 
-                       family = binomial, data = data)
-saveRDS(reduced_model_2, file="models/final_model.rds")
-
-# 1.
-#Encode categorical variables
[…]

### 2024-12-11 paper/paper.qmd
fix readme

@@
   - Claire Ma
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
-date: 2024.12.03
+thanks: "Code and data are available at: [https://github.com/ClaireMa0311/Toronto-licensed-child-centers.git]."
+date: today
 date-format: long
@@
 Understanding the factors that determine which licensed centres receive subsidies is crucial for policymakers and stakeholders to promote equitable resource allocation and maximize the benefits of early childhood programs.
+
 Licensed child care centres in urban settings like Toronto play a pivotal role in delivering high-quality, structured child care.
 These centres adhere to stringent regulations, ensuring compliance with standards for safety, staffing, and curriculum.
-Research highlights that children attending licensed centres, particularly those supported by subsidies, experience better developmental outcomes (Adams et al., 2013).
-Subsidized centres provide professional environments with trained educators, comprehensive programming, and age-appropriate resources, offering children a strong foundation for lifelong learning and success (Herbst, 2014).
-Subsidies are a cornerstone of this ecosystem, enabling licensed centres to cover operational costs, retain qualified staff, and maintain compliance with regulatory standards, all of which enhance the quality of care provided [@ryan2011impact].
+Research highlights that children attending licensed centres, particularly those supported by subsidies, experience better developmental outcomes.
+Subsidized centres provide professional environments with trained educators, comprehensive programming, and age-appropriate resources, offering children a strong foundation for lifelong learning and success.
+Subsidies are a cornerstone of this ecosystem, enabling licensed centres to cover operational costs, retain qualified staff, and maintain compliance with regulatory standards, all of which enhance the quality of care provided.
+
 Despite their importance, disparities in the allocation of subsidies remain a significant concern.
 Research indicates that centres in certain neighborhoods or serving specific populations may receive fewer subsidies, even when demand is high [@Johnson_Ryan_Brooks_2012].
-Additionally, characteristics such as enrollment capacity, accreditation status, and program focus (e.g., infant care versus pre-kindergarten) often influence a centre’s eligibility and prioritization for funding [@vines2020accessin].
+Additionally, characteristics such as enrollment capacity, accreditation status, and program focus (e.g., infant care versus pre-kindergarten) often influence a centre’s eligibility and prioritization for funding.
 These discrepancies highlight the need for a data-driven approach to understanding and improving the distribution of subsidies among licensed child care centres, ensuring that resources are allocated equitably to maximize their impact.
@@
 The remainder of this paper is structured as follows.
-@sec-data : This section describes the dataset used for the analysis, including its source, key variables, and preprocessing steps, emphasizing its real-world context and relevance to understanding subsidy allocation in Toronto's child care system.
-@sec-model : This section details the logistic regression model employed in the study, including the rationale for its selection, mathematical formulation, and key predictors.
+@sec-data describes the dataset used for the analysis, including its source, key variables, and preprocessing steps, emphasizing its real-world context and relevance to understanding subsidy allocation in Toronto's child care system.
+@sec-model details the logistic regression model employed in the study, including the rationale for its selection, mathematical formulation, and key predictors.
 The model assumptions, diagnostics, and validation methods are also discussed to ensure robustness and reliability.
-@sec-reult : The results of the logistic regression analysis are presented, highlighting the significant predictors of subsidy allocation, ass well as the model's fit.
-@sec-discussion : This section discusses what was done in this study, giving detailed explanation of implications of the findings, limitations and suggestion for future studies.Furthermore, an appendix including supplementary materials and data collection evaluation is provided to ensure transparency and reproducibility.
+@sec-results contains the results of the logistic regression analysis are presented, highlighting the significant predictors of subsidy allocation, ass well as the model's fit.
+@sec-discussion discusses what was done in this study, giving detailed explanation of implications of the findings, limitations and suggestion for future studies.
+Furthermore, an appendix including supplementary materials and data collection evaluation is provided to ensure transparency and reproducibility.
 
@@
 ## Data Overview
-The dataset used in this study was sourced from the [@Childrens_Services] made publicly available by the City of Toronto.
+
+The dataset used in this study was sourced from the [@citeopendatatoronto; @toronto2024licensed] made publicly available by the City of Toronto.
 This original raw dataset provides detailed information about licensed child care centres, including 20 variables capturing aspects of their location, operating auspice (e.g., non-profit, public, or commercial), space usage, building type, participation in government programs such as the Canada-Wide Early Learning and Child Care (CWELCC) system, and other operational details.
@@
 #| message: false
-#| tbl-cap: "Sample of Cleaned Data"
-library(gt)
 
@@
 However, the remaining non-subsidized centres indicate potential gaps or disparities in resource allocation, which could be further explored to ensure equitable funding.
+
 ```{r}
 #| label: fig-subsidy
-#| fig-cap: "Subsidy Allocation Distribution"
+#| fig-cap: "Distribution of Subsidy Allocation: Disparities Exist"
 #| echo: false
@@
 # Create the bar plot with percentage labels
-plot1 <- ggplot(data_summary, aes(x = as.factor(subsidy), y = count)) +
+plot1 <- ggplot(data_summary, aes(x = factor(subsidy, labels = c("No", "Yes")), y = count)) +
   geom_bar(stat = "identity", fill = c("skyblue", "coral"), alpha = 0.8) +
@@
     title = "Distribution of Subsidy",
-    x = "Subsidy (0 = No, 1 = Yes)",
+    x = "Subsidy",
     y = "Count"
@@
 ## Method
-The dataset used for this study is the **`Licensed Child Care Centres dataset`**, sourced from the [@citeopendatatoronto] It provides detailed information about licensed child care centres in Toronto, capturing aspects such as their governance, capacity, infrastructure, and subsidy status.
+
+The dataset used for this study is the **`Licensed Child Care Centres dataset`**, sourced from the [@citeopendatatoronto; @toronto2024licensed] It provides detailed information about licensed child care centres in Toronto, capturing aspects such as their governance, capacity, infrastructure, and subsidy status.
 The original dataset consisted of 1071 records for all licensed child care centres within the city.
@@
 The dependent variable **`subsidy`**, originally recorded as "Yes"/"No," was encoded as 1 for subsidized and 0 for non-subsidized centres.
-Similarly, the **`cwelcc_flag`** variable was converted into a binary format (1 =Y, 0 =N).
-Categorical variables such as **`bldg_type`** and **`AUSPICE`** were consolidated to simplify analysis and address sparse categories.
+Similarly, the **CWELCC participation** variable was converted into a binary format (1 =Y, 0 =N).
+Categorical variables such as **building type** and **`operational AUSPICE`** were consolidated to simplify analysis and address sparse categories.
 Additionally, missing and irrelevant records were removed to ensure the dataset was both accurate and meaningful for the research objectives.
@@
 The following are major packages used for this study:
-**`opendatatoronto`**[@citeopendatatoronto]: Used to access and retrieve the Licensed Child Care Centres dataset directly from the City of Toronto's open data portal.
-**`readr`** [@citereadr]: Simplified the import and parsing of raw data into R.
-**`tidyverse`** [@citetidyverse]: Streamlined data manipulation, cleaning, and visualization processes.
-**`dplyr`** [@citedplyr]: Provided tools for filtering, transforming, and summarizing the dataset effectively.
-**`ggplot2`** [@citeggplot2]: Created powerful and flexible visualizations tailored to the analysis needs.
-**`car`** [@citecar]: Used for diagnostic tools, including Variance Inflation Factor (VIF) tests, to assess multicollinearity.
-**`caret`** [@citecaret]: Enabled the development, validation, and evaluation of machine learning models, including training-test splits and performance metrics.
-**`glmnet`** (Friedman et al., 2010): Applied for fitting regularized regression models and feature selection.
-**`stargazer`** [@citestagazer]: Generated formatted regression tables for outputs.
-**`knitr`** [@citeknitr]: Dynamically integrated code, results, and plots into the final document for seamless reporting.
+
+- `opendatatoronto`[@citeopendatatoronto]: Used to access and retrieve the Licensed Child Care Centres dataset directly from the City of Toronto's open data portal.
+
+-`arrow` [@citearrow]: Provided efficient tools for reading and writing Parquet files, enabling fast and memory-efficient handling of large datasets during analysis.
+
+- `here` [@citehere]: Simplified file referencing by creating relative paths, ensuring reproducibility and consistency in accessing datasets, scripts, and outputs across different working environments.
+
+- `readr` [@citereadr]: Simplified the import and parsing of raw data into R.
+
+- `tidyverse` [@citetidyverse]: Streamlined data manipulation, cleaning, and visualization processes.
+
+- `dplyr` [@citedplyr]: Provided tools for filtering, transforming, and summarizing the dataset effectively.
+
+- `tidyr` [@citetidyr]: Enabled data tidying processes such as reshaping, separating, or combining, and handling missing values to structure the dataset into a clean and analyzable format.
+
+- `ggplot2` [@citeggplot2]: Created powerful and flexible visualizations tailored to the analysis needs.
+
+- `ggcorrplot` [@citeggcorrplot]: Simplified the visualization of correlation matrices with customizable heatmaps, including options for labeling and styling to enhance interpretability and presentation.
+
+- `glmnet` [@]: Applied for fitting regularized regression models and feature selection.
+
+- `modelsummary` [@citemodelsummary]: Streamlined the creation of comprehensive and customizable summary tables for regression models, including key statistics such as AIC, BIC, and coefficient estimates, to facilitate clear model comparisons and reporting.
+
+- `stats` [@citestats]: Provided core statistical functions to fit models, perform hypothesis testing, and calculate measures such as p-values, log-likelihoods, and AIC for model evaluation.
+
+- `car` [@citecar]: Used for diagnostic tools, including Variance Inflation Factor (VIF) tests, to assess multicollinearity.
+
+- `caret` [@citecaret]: Enabled the development, validation, and evaluation of machine learning models, including training-test splits and performance metrics.
+
+- `pROC` [@citeproc]: Facilitated the computation and visualization of Receiver Operating Characteristic (ROC) curves and Area Under the Curve (AUC) metrics, enabling robust evaluation of the model's classification performance.
+
+- `stargazer` [@citestagazer]: Generated formatted regression tables for outputs.
+
+- `broom` [@citebroom]: Simplified the process of converting model outputs into tidy data frames, enabling seamless integration of statistical results with visualization and reporting workflows.
+
+- `kableExtra` [@citekableExtra]:Enhanced the presentation of tables by adding advanced formatting options, including captions, headers, and styling, for polished and professional reporting.
+
+- `gt` [@citegt]: Enabled the creation of aesthetically pleasing and highly customizable tables for presenting data and model summaries in a clean and professional format.
+
+- `knitr` [@citeknitr]: Dynamically integrated code, results, and plots into the final document for seamless reporting.
 
 ## Measurement
+
 This analysis focuses on the following variables, with a specific emphasis on subsidy as the dependent variable:
-- `subsidy`: The binary dependent variable indicating whether a licensed child care centre receives a government subsidy.
+
+- `Subsidy`: The binary dependent variable indicating whether a licensed child care centre receives a government subsidy.
 - 1: The centre is subsidized.
@@
 - `ward`: `A numeric variable representing the ward number for child care centres.
-- `AUSPICE`: The operating auspice of the child care centre, describing its governance and operational model. Possible values include:
+- `Operating Auspice`: The operating auspice of the child care centre, describing its governance and operational model. Possible values include:
 - Non-Profit: Centres operated by non-profit organizations, often reinvesting surplus revenues into quality improvements.
@@
 - Public: Centres run by public agencies or school boards.
-- `bldg_type`: The type of building where the child care centre operates, reflecting its infrastructure. Examples include:
-- bldg_typeCommercial Building
-- bldg_typeCommunity College/University     
-- bldg_typeCommunity Health Centre
-- bldg_typeCommunity Rec/Centre - Board Run
-- bldg_typeCommunity/Rec Centre - City
-- bldg_typeCommunity/Recreation Centre
-- bldg_typeHigh Rise Apartment
-- bldg_typeHospital/Health Centre
-- bldg_typeHouse
-- bldg_typeIndustrial Building
-- bldg_typeLow Rise Apartment
-- bldg_typeOffice Building
-- bldg_typeOther
-- bldg_typePlace of Worship
-- bldg_typePrivate Elementary School
-- bldg_typePublic (school closed)
-- bldg_typePublic Elementary Special
-- bldg_typePublic High School
-- bldg_typePublic Middle School
-- bldg_typePurpose Built
-- bldg_typeSynagogue
-- `cwelcc_flag`: A binary variable indicating participation in the Canada-Wide Early Learning and Child Care (CWELCC) program:
+- `Building Type`: The type of building where the child care centre operates, reflecting its infrastructure.
+
+Examples include:
+
+- Commercial Building
+- Community College/University
+- Community Health Centre
+- Community Rec/Centre - Board Run
+- Community/Rec Centre - City
+- Community/Recreation Centre
+- High Rise Apartment
+- Hospital/Health Centre
+- House
+- Industrial Building
+- Low Rise Apartment
+- Office Building 
+- Place of Worship
+- Private Elementary School
+- Public (school closed)
+- Public Elementary Special
+- Public High School
+- Public Middle School
+- Purpose Built
+- Synagogue
+- Other
+- `CWELCC Participation`: A binary variable indicating participation in the Canada-Wide Early Learning and Child Care (CWELCC) program:
 - 1: The centre participates in CWELCC, enabling reduced child care fees.
 - 0: The centre does not participate in CWELCC.
-- `TOTSPACE`: A numerical variable representing the total licensed capacity (spaces available) for all age groups at a child care centre.
+- `Total Space`: A numerical variable representing the total licensed capacity (spaces available) for all age groups at a child care centre.
 
@@
 #| label: fig-relationbldgtype
-#| fig-cap: "Proportional Distribution of Subsidy Status Across Building Types"
+#| fig-cap: "Subsidy Allocation by Building Type: Higher Subsidy Proportions in Public and Purpose-Built Facilities"
 #| echo: false
@@
 #| warning: false
+# Update the plot to use descriptive labels for the subsidy legend
 ggplot(data, aes(x = bldg_type, fill = as.factor(subsidy))) +
   geom_bar(position = "fill", alpha = 0.8) +
-  scale_fill_manual(values = c("blue", "red")) +
+  scale_fill_manual(
+    values = c("blue", "red"),
+    labels = c("No", "Yes")  # Replace 0/1 with No/Yes
+  ) +
   labs(
@@
 #| label: fig-relationAuspice
-#| fig-cap: "Proportional Distribution of Subsidy Status by Auspice"
+#| fig-cap: "Subsidy Allocation by Operating Auspice: Non-Profit Agencies and 'Other' Predominantly Subsidized"
 #| echo: false
@@
 #| warning: false
+
 ggplot(data, aes(x = AUSPICE, fill = as.factor(subsidy))) +
   geom_bar(position = "fill", alpha = 0.8) +
-  scale_fill_manual(values = c("blue", "red")) +
+  scale_fill_manual(
+    values = c("blue", "red"),
+    labels = c("No", "Yes")  # Change legend labels to No/Yes
+  ) +
   labs(
@@
   )
+```
 
-```
-@fig-key a heatmap illustrates the correlations between three variables: TOTSPACE (likely representing total space or capacity), subsidy (indicating subsidy status or amount), and cwelcc_flag (potentially denoting eligibility for a specific program or funding).
-The positive correlation between TOTSPACE and subsidy (0.25) suggests that larger facilities are modestly more likely to receive subsidies, reflecting their capacity to serve larger populations or provide greater public benefits.
-This aligns with research indicating that larger organizations often have the resources and visibility to secure subsidies (Hansmann, 1980;  Salamon, 2002).
-Additionally, the stronger correlation between subsidy and cwelcc_flag (0.48) highlights that subsidy allocation may target entities meeting specific programmatic or policy criteria, consistent with the literature emphasizing strategic targeting of subsidies to maximize societal impact (Weisbrod, 1998).
-The weaker correlation between TOTSPACE and cwelcc_flag (0.17) suggests that program eligibility is less dependent on size and more on qualitative factors like service type or demographic focus, which is supported by Anheier’s (2005) analysis of non-profit funding models.
-Together, these correlations emphasize the nuanced role of subsidies in balancing operational scale and policy alignment, underscoring the importance of strategic allocation in public funding (Salamon, 1995).
+@fig-key a heatmap illustrates the correlations between three variables: total space, CWELCC participation and subsidy.
+The positive correlation between total space and subsidy (0.25) suggests that larger facilities are modestly more likely to receive subsidies, reflecting their capacity to serve larger populations or provide greater public benefits.
+This aligns with research indicating that larger organizations often have the resources and visibility to secure subsidies [@hansmann1980role; @salamon2002tools].
+Additionally, the stronger correlation between CWELCC participation and subsidy (0.48) highlights that subsidy allocation may target entities meeting specific programmatic or policy criteria, consistent with the literature emphasizing strategic targeting of subsidies to maximize societal impact [@weisbrod1998profit].
+The weaker correlation between total space and CWELCC oarticipation (0.16) suggests that program eligibility is less dependent on size and more on qualitative factors like service type or demographic focus, which is supported by [@anheier2005nonprofit] analysis of non-profit funding models.
+Together, these correlations emphasize the nuanced role of subsidies in balancing operational scale and policy alignment, underscoring the importance of strategic allocation in public funding [@salamon1995partners].
 
@@
 #| label: fig-key
-#| fig-cap: "Correlation Heatmap of Key Variables: TOTSPACE, Subsidy, and CWELCC Flag"
+#| fig-cap: "Correlation Between Total Space, Subsidy Allocation, and CWELCC Participation"
 #| echo: false
@@
 #| warning: false
-library(ggcorrplot)
-cor_matrix <- cor(data %>% select(TOTSPACE, subsidy, cwelcc_flag), use = "complete.obs")
-ggcorrplot(cor_matrix, lab = TRUE)
+
+# Define new labels for the graph without renaming the original columns
+new_labels <- c("Total Space", "Subsidy", "CWELCC Participation")
+
+# Plot the heatmap without axis labels
+ggcorrplot(cor_matrix, lab = TRUE) +
+  scale_x_discrete(labels = c("Total Space", "Subsidy", "CWELCC Participation")) +  # Update x-axis labels
+  scale_y_discrete(labels = c("Total Space", "Subsidy", "CWELCC Participation")) +  # Update y-axis labels
+  labs(
+    title = "Correlation Heatmap of Key Variables",
+    caption = "Key Variables: Total Space, Subsidy, and CWELCC Participation"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.title.x = element_blank(),  # Remove x-axis title
+    axis.title.y = element_blank()   # Remove y-axis title
+  )
 
@@
 # Model {#sec-model}
+
 ## Model Specification
+
 To investigate the factors influencing subsidy allocation to licensed child care centres, a reduced logistic regression model was specified.
-The dependent variable,`subsidy`, is a binary indicator representing whether a child care centre receives government subsidy (1 = subsidized, 0 = not subsidized).
+The dependent variable,`Subsidy`, is a binary indicator representing whether a child care centre receives government subsidy (1 = subsidized, 0 = not subsidized).
 The model includes three key predictors:
-`Operating Auspice (AUSPICE)`: A categorical variable indicating the governance model of the child care centre (e.g., Non-Profit Agency, Other).
-Non-profit agencies are hypothesized to be positively associated with subsidy allocation, consistent with previous research emphasizing their prioritization in funding schemes (Cleveland & Krashinsky, 2005).
-`Participation in the CWELCC Program (cwelcc_flag)`: A binary variable capturing whether the centre participates in the Canada-Wide Early Learning and Child Care program (1 = participates, 0 = does not participate).
-Centres participating in this initiative are expected to have higher odds of receiving subsidies due to their alignment with government objectives of affordability and accessibility (Friendly & Ballantyne, 2022).
-`Total Space (TOTSPACE)`: A continuous variable representing the number of licensed spaces available in the centre.
-Larger centres are hypothesized to have higher odds of subsidy allocation, as they can accommodate more families and align with policy goals of maximizing access (Forry et al., 2010).
+
+`Operating Auspice`: A categorical variable indicating the governance model of the child care centre (e.g., Non-Profit Agency, Other).
+Non-profit agencies are hypothesized to be positively associated with subsidy allocation, consistent with previous research emphasizing their prioritization in funding schemes [@cleveland2005benefits].
+
+`CWELCC participation`: A binary variable capturing whether the centre participates in the Canada-Wide Early Learning and Child Care program (1 = participates, 0 = does not participate).
+Centres participating in this initiative are expected to have higher odds of receiving subsidies due to their alignment with government objectives of affordability and accessibility [@friendly2022affordable].
+
+`Total Space`: A continuous variable representing the number of licensed spaces available in the centre.
+Larger centres are hypothesized to have higher odds of subsidy allocation, as they can accommodate more families and align with policy goals of maximizing access [@hansmann1980role; @salamon2002tools].
+
 The logistic regression model can be expressed mathematically as follows:
-\[
-\text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{CWELCC Participation}) + \beta_3 (\text{Total Space}) + \epsilon
-\]
+
+$$
+\text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{CWELCC Participation}) + \beta_3 (\text{Total Space})
+$$
 
 Where:
+
 \begin{itemize}
@@
 ### Parameters:
-1. **\( \beta_0 \) (Intercept):**
+
+1. **$\beta_0$ (Intercept):**
+
    - Represents the baseline log-odds of subsidy allocation when all predictors are set to their reference categories or zero values.
@@
 
-2. **\( \beta_1 (\text{Non-Profit Auspice}) \):**
+2. **$\beta_1$ (Non-Profit Auspice):**
+
    - Measures the effect of a center being operated as a non-profit compared to the baseline (e.g., commercial auspice) on the log-odds of subsidy allocation.
-   - A positive \( \beta_1\) increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.
+   - A positive $\beta_1$ increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.
 
-3. **\( \beta_2 (\text{CWELCC Participation}) \):**
+3. **$\beta_2$ (CWELCC Participation):**
    - Captures the influence of participating in the Canada-Wide Early Learning and Child Care (CWELCC) program on the log-odds of subsidy allocation.
 
-4. **\( \beta_3 (\text{Total Space}) \):**
+4. **$\beta_3$ (Total Space):**
    - Represents the effect of the number of licensed child care spaces (a continuous variable) on the log-odds of subsidy allocation.
 
-5. **\( \epsilon \) (Error Term):**
-   - Accounts for unexplained variation in the log-odds of subsidy allocation not captured by the predictors.
+5. **$\epsilon$ (Error Term):**
+   - Accounts for unexplained variation in the log-odds of subsidy allocation not captured by the predictors
 
 ## Model Justification
+
 The logistic regression model was chosen for this analysis because it is well-suited to the binary nature of the dependent variable, subsidy status (1 = Subsidized, 0 = Not Subsidized).
@@
 This makes it particularly useful for guiding policy decisions, as coefficients can be directly converted into odds ratios for actionable insights [@peng2002introduction].
-The ward variable was excluded because it lacked statistical significance and added redundancy, as its effects were captured by other predictors like CWELCC participation and total space.
+
+The modeling process follows a detailed and methodical approach to ensure the development of a robust logistic regression model for predicting subsidy allocation in licensed child care centers.
+Initially, the categorical variables operating auspice and building type were encoded as factors to ensure proper interpretation of their qualitative nature by the model.
+The dataset was then split into training (70%) and testing (30%) sets, allowing for model validation on unseen data to assess generalizability.
+A full logistic regression model was first fit to include all predictors (subsidy ~ .), providing a baseline for further analysis.
+To refine the model, stepwise selection based on the Akaike Information Criterion (AIC) was employed, balancing goodness of fit with model parsimony by penalizing unnecessary complexity.
+This process resulted in the selection of the most significant predictors for subsidy allocation.
+
+To further simplify and enhance interpretability, the ward variable was excluded because it lacked statistical significance and added redundancy, as its effects were captured by other predictors like CWELCC participation and total space.
 Additionally, ward had no strong theoretical justification as a direct determinant of subsidy allocation.
@@
 
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Encode categorical variables
-data$AUSPICE <- as.factor(data$AUSPICE)
-data$bldg_type <- as.factor(data$bldg_type)
+Multiple models, including the full model, the AIC-based model, and the simplified model, were compared using goodness-of-fit metrics such as AIC and Deviance to ensure the best-performing model was selected.
+Additionally, McFadden’s R-squared was calculated to evaluate the explanatory power of the model, comparing the log-likelihood of the fitted model to a null model.
+A higher McFadden’s R-squared value confirmed the model’s ability to explain a significant portion of the variance in subsidy allocation.
 
-# Split the data into training and testing sets
-set.seed(1008047418)
-train_index <- createDataPartition(data$subsidy, p = 0.7, list = FALSE)
-train_data <- data[train_index, ]
-test_data <- data[-train_index, ]
+By training and testing the models on separate subsets of the data, the process ensured validation and minimized the risk of overfitting.
+The final model was chosen for its simplicity, interpretability, and ability to retain statistically significant predictors that align with theoretical expectations.
+This rigorous process not only ensures robust prediction but also aligns with real-world phenomena in subsidy allocation, making the model both practical and reliable.
 
-# Fit logistic regression model
-log_model <- glm(subsidy ~ ., data = train_data, family = binomial)
+## Model Assumptions
 
-# Summary of the model
-summary(log_model)
-
-```
-
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Stepwise selection based on AIC
-step_model_aic <- step(log_model, direction = "both", trace = TRUE)
-
-# Summary of models
-summary(step_model_aic)  # AIC-based selected model
-```
-
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Create a binary variable for "Non Profit Agency"
-train_data$AUSPICE_NonProfit <- ifelse(train_data$AUSPICE == "Non Profit Agency", 1, 0)
-
-# Refit the model with the binary variable for AUSPICE
-reduced_model_re2 <- glm(formula = subsidy ~ AUSPICE_NonProfit + bldg_type + cwelcc_flag + TOTSPACE, 
-                       family = binomial, data = train_data)
-
-# Summary of the updated model
-summary(reduced_model_re2)
-
-```
-
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-
-# Refit the best aic model
-reduced_model_re <- glm(formula = subsidy ~ AUSPICE + bldg_type + cwelcc_flag + TOTSPACE, 
-    family = binomial, data = train_data)
-summary(reduced_model_re)
-
-```
-
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Refit model by removing non-significant variables
-reduced_model_2 <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE, 
-    family = binomial, data = train_data)
-summary(reduced_model_2)
-```
-## Model Assumptions
-To ensure the validity of the logistic regression model, several key assumptions were assessed, including independence of observations, the appropriateness of a binary outcome, the linearity of predictors with the logit and absence of multicollinearity.
-The analysis integrates results from visual diagnostics, multicollinearity tests, and statistical measures.
-### 1. Independence of Observations
-The logistic regression model assumes that the observations are independent of each other.
-In this analysis, each data point corresponds to an individual child care center, ensuring independence.
-There is no clustering or repeated measures within the dataset, which validates this assumption.
-### 2. Binary Outcome
-The logistic regression model assumes a binary dependent variable.
-In this case, the outcome variable, `subsidy`, is binary, indicating whether a child care center receives a subsidy (1 = Subsidized, 0 = Not Subsidized).
-This aligns with the model's requirement, ensuring the suitability of the binomial family for fitting the data.
-### 3. Linearity of Predictors with the Logit
-The @fig-cr The component + residual plots evaluate the linearity of the continuous variables and the relationship between categorical predictors and the logit transformation.
-
-```{r}
-#| label: fig-cr
-#| fig-cap: "CR Plot for Linearity Chekck"
-#| echo: false
-#| message: false
-#| warning: false
-# Customizing Component + Residual Plots with concise y-axis label
-crPlots(reduced_model_2, ylab = "Component+Residuals")  # Shortened y-axis label
-
-```
-- `TOTSPACE`: The relationship between the total space (TOTSPACE) and the logit appears approximately linear, as indicated by the flat, consistent pattern of residuals around the horizontal axis.
-This supports the assumption of linearity.
-- `CWELCC Flag`: The plot for CWELCC participation shows a horizontal trend, suggesting no significant deviation from linearity. The data support the inclusion of this variable as a binary predictor.
-- `AUSPICE`: The residual patterns for categorical levels of AUSPICE (e.g., "Commercial Agency" and "Other") indicate distinct clusters with consistent variability.
-This suggests the categorical nature of this variable does not violate linearity assumptions.
-Overall, the visual inspection suggests that the linearity assumption for the predictors with the logit is met.
-
-### 4. Multicollinearity Assessment
-Variance Inflation Factor (VIF):
-To assess multicollinearity among the predictors, the VIF values for the reduced model variables were calculated.All VIF values are below 2, well within the acceptable threshold of 5, indicating minimal multicollinearity among the predictors.
-The independence of the predictors ensures the stability of the coefficient estimates.
-
-```{r}
-# Calculate VIF
-vif_values <- vif(reduced_model_2)
-```
+Detailed model assumption check is in @sec-model-details.
 
 ## Alternative Models
+
 Alternative models like decision trees and random forests were considered but were found less interpretable for policy-focused analyses.
@@
 
-# Result {#sec-result}
+# Results {#sec-results}
+
 The logistic regression model’s performance metrics are presented in @tbl-coefresult.
 
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
+```{r,echo=FALSE, message=FALSE, warning=FALSE}
 #| label: tbl-coefresult
@@
   model_list, 
-  output = "markdown", 
   statistic = c("std.error", "p.value")
 )
-
 ```
@@
 The regression model reveals several key observations regarding the predictors and overall goodness of fit.
-The intercept, estimated at -4.967, represents the baseline log-odds of the outcome when all predictors are at their reference or zero level.
+The intercept, estimated at -4.818, represents the baseline log-odds of the outcome when all predictors are at their reference or zero level.
 While not directly interpretable, it serves as a baseline reference for the model.
-Among the predictors, the AUSPICE: Non-Profit Agency category significantly increases the log-odds of the outcome, with an estimate of 2.883 and a small standard error of 0.234, indicating a strong and reliable positive effect.
-However, the AUSPICE: Other category shows an unusually large coefficient (18.772) paired with a very high standard error (686.847), suggesting instability.
-The CWELCC Flag variable also exhibits a strong and reliable positive effect, with an estimate of 3.156 and a standard error of 0.436, indicating that being flagged as CWELCC significantly increases the log-odds of the outcome.
-Additionally, the TOTSPACE variable has a small but statistically significant effect, with an estimate of 0.014 and a low standard error of 0.003, reflecting robustness.
-In terms of model fit, the dataset includes 750 observations, and the model's AIC (528.1) and BIC (551.2) suggest a reasonable balance between goodness of fit and complexity, as lower values are generally preferred [@burnhammodel].
-The log-likelihood of -259.035 also supports an adequate fit, with a higher (less negative) value indicating better alignment between the model and the data.
+Among the predictors, the operating auspice: non-profit Agency category significantly increases the log-odds of the outcome, with an estimate of 2.937 and a small standard error of 0.192, indicating a strong and reliable positive effect.
+However, the operating auspice: other category shows an unusually large coefficient (18.680) paired with a very high standard error (631.207), suggesting instability.
+The CWELCC participation variable also exhibits a strong and reliable positive effect, with an estimate of 3.101 and a standard error of 0.346, indicating that being flagged as CWELCC significantly increases the log-odds of the outcome.
+Additionally, the total space variable has a small but statistically significant effect, with an estimate of 0.013 and a low standard error of 0.003, reflecting robustness.
+In terms of model fit, the dataset includes 750 observations, and the model's AIC (760.8) and BIC (785.7) suggest a reasonable balance between goodness of fit and complexity, as lower values are generally preferred [@burnhammodel].
+The log-likelihood of -375.414 also supports an adequate fit, with a higher (less negative) value indicating better alignment between the model and the data.
 Finally, the RMSE of 0.32 reflects the model's predictive accuracy, with a low value indicating that the model's predictions closely match the observed data.
@@
 #| label: fig-cp
-#| fig-cap: "Coefficient Plot"
+#| fig-cap: "Coefficient Estimates for Predictors of Subsidy Allocation"
 #| echo: false
@@
 
-The evaluation of the logistic regression model shows strong performance based on McFadden’s R^2 and the Area Under the Receiver Operating Characteristic Curve (AUC).
-McFadden’s R^2 which is a pseudo-R^2 metric specifically designed for logistic regression, was calculated as 0.454.
+The evaluation of the logistic regression model shows strong performance based on McFadden’s $R^2$ and the Area Under the Receiver Operating Characteristic Curve (AUC).
+McFadden’s $R^2$ which is a pseudo-$R^2$ metric specifically designed for logistic regression, was calculated as 0.454.
 This value suggests that the model explains 45.4% of the variance in the outcome variable, indicating a well-fitting model.
-McFadden [@mcfadden1972conditional] proposed this metric as a reliable measure for logistic regression, where values between 0.2 and 0.4 are considered indicative of a good model fit, and values above 0.4 demonstrate an excellent fit.
-Thus, the model's R^2 value strongly supports its utility in predicting the outcome.
-```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-# Calculate log-likelihood of the fitted model
-log_likelihood_fitted <- logLik(reduced_model_2)
-# Fit the null model (model with intercept only)
-null_model <- glm(subsidy ~ 1, data = train_data, family = binomial)
-log_likelihood_null <- logLik(null_model)
-# McFadden's R-squared
-mcfadden_r2 <- 1 - as.numeric(log_likelihood_fitted / log_likelihood_null)
-# Print the result
-print(paste("McFadden's R-squared:", round(mcfadden_r2, 6)))
-```
+Values between 0.2 and 0.4 are considered indicative of a good model fit, and values above 0.4 demonstrate an excellent fit.
+Thus, the model's $R^2$ value strongly supports its utility in predicting the outcome.
 
@@
 #| label: fig-roc
-#| fig-cap: "ROC Curve for Model Performance"
+#| fig-cap: "ROC Curve for Model Performance: Strong Model Performance with AUC 0.906"
 #| echo: false
@@
 # ROC Curve and AUC
-roc_curve <- roc(test_data$subsidy, predict(reduced_model_2, newdata = test_data, type = "response"))
-plot(roc_curve, main = "ROC Curve")
-auc(roc_curve)
+roc_curve <- roc(data$subsidy, 
+                 predict(model, 
+                         newdata = data, type = "response"))
+plot(roc_curve, main = "ROC Curve", print.auc=T)
+```
 
-```
-The ROC curve in @fig-roc shown further validates the model's classification ability, with an AUC of 0.8998.
+The ROC curve in @fig-roc shown further validates the model's classification ability, with an AUC of 0.906.
 An AUC value close to 1 indicates excellent discriminative power, where the model effectively separates true positives from false positives.
@@
 #| label: fig-pvo
-#| fig-cap: " Predicted vs. Observed Probability"
+#| fig-cap: " Predicted vs. Observed Probability Plot: Model Calibration and Accuracy"
 #| echo: false
@@
 Such discrepancies could indicate areas where further refinement of the model or predictors is necessary.
-These deviations could also be linked to specific subgroups or predictor interactions, necessitating additional diagnostics or recalibration, as suggested by Steyerberg et al.
-[@steyerberg2010assessing].
+These deviations could also be linked to specific subgroups or predictor interactions, necessitating additional diagnostics or recalibration [@steyerberg2010assessing].
+
 Overall, this graph demonstrates that the model is well-calibrated and effective in its predictions, with minor limitations at lower probability levels.
 The close alignment of predictions with observed outcomes supports the model's reliability in classification tasks.
-This interpretation aligns with other metrics, such as McFadden’s R2R2 [@mcfadden1972conditional] and AUC, which indicate robust overall model performance while pointing to opportunities for refinement.
+This interpretation aligns with other metrics, such as McFadden’s $R^2$ and AUC, which indicate robust overall model performance while pointing to opportunities for refinement.
 Including this visualization in the results section provides a clear and data-driven assessment of the model's strengths and areas for potential improvement.
 
-#Discussion {#sec-discussion}
+# Discussion {#sec-discussion}
 
@@
 This involved several key steps of data cleaning, variable transformation and training-test Split.
-Initially, variables of Operating auspice(AUSPICE), ward, building type(bldg_type), total space(TOTSPACE) and participation status in programs(cwelcc_flag) were chosen based their relevance and practical influence subsidy outcomes and forecasting supported by scholar literatures.
-After fitting and improving the model using stepwise selection based on the Akaike Information Criterion (AIC), non-significant variables (ward and building type(bldg_type)) were removed.
-The final model retained Operating Auspice, CWELCC Participation, and Total Licensed Capacity as key predictors.
+Initially, variables of operating auspice, ward, building type, total space and CWELCC participation were chosen based their relevance and practical influence subsidy outcomes and forecasting supported by scholar literatures.
+After fitting and improving the model using stepwise selection based on the Akaike Information Criterion (AIC), non-significant variables (ward and building type) were removed.
+The final model retained operating auspice, CWELCC participation, and total space as key predictors.
 The assumptions underpinning the logistic regression model were thoroughly validated, ensuring its statistical rigor and reliability.
 Independence of observations was confirmed, as each data point corresponds to a unique child care centre, eliminating concerns of clustering or dependency.
-Linearity between continuous predictors, such as Total Licensed Capacity, and the logit transformation was validated through component + residual plots, which revealed consistent patterns, supporting the appropriateness of the model.
+Linearity between continuous predictors, such as total space, and the logit transformation was validated through component + residual plots, which revealed consistent patterns, supporting the appropriateness of the model.
 Additionally, multicollinearity was minimized, with Variance Inflation Factor (VIF) values well below the critical threshold of 5, indicating that the predictors are independent and the coefficient estimates are stable.
@@
 By measuring the change in log-odds of subsidy allocation associated with each predictor, the model quantifies the relative importance of governance models, program participation, and operational capacity.
-The coefficient for Non-Profit Auspice emerged as strongly positive and statistically significant, indicating that non-profit child care centres are far more likely to receive subsidies than commercial or public centres.
+The coefficient for non-profit auspice emerged as strongly positive and statistically significant, indicating that non-profit child care centres are far more likely to receive subsidies than commercial or public centres.
 This is reflective of policy priorities that favor organizations with a social mission over those with profit-oriented objectives.
@@
 The odds ratio for CWELCC participation indicates that such centres are substantially more likely to receive subsidies, which is consistent with targeted funding strategies aimed at expanding access to high-quality, affordable child care [@kaga2010caring].
-Total Licensed Capacity (TOTSPACE), representing the number of spaces a centre is licensed to operate, was another important predictor, although its coefficient was smaller in magnitude compared to governance and CWELCC participation.
+Total space, representing the number of spaces a centre is licensed to operate, was another important predictor, although its coefficient was smaller in magnitude compared to operating auspice and CWELCC participation.
 This positive coefficient suggests that larger centres are more likely to receive subsidies, likely due to their capacity to serve more families and their operational scale.
@@
 The statistical significance of these coefficients underscores their reliability as shown in figure.
-Variables such as Non-Profit Auspice and CWELCC Participation demonstrated small standard errors and strong significance levels, reinforcing their influence on subsidy allocation.
-In contrast, variables with less consistent effects, such as certain building types or governance categories in the "Other" category, exhibited instability, suggesting that their role in funding decisions may be more context-specific or secondary.
+Variables such as non-profit auspice and CWELCC Participation demonstrated small standard errors and strong significance levels, reinforcing their influence on subsidy allocation.
+In contrast, variables with less consistent effects, such as certain building types or governance categories in the "other" category, exhibited instability, suggesting that their role in funding decisions may be more context-specific or secondary.
 The model's findings highlight a strategic approach to subsidy allocation, where funding decisions are guided by alignment with policy goals, operational capacity, and governance structures.
@@
 Coefficients can be transformed into odds ratios, providing a clear understanding of how predictors influence the likelihood of receiving subsidies.
-For example, the positive coefficients for Non-Profit Auspice and CWELCC Participation underscore their significant, policy-relevant impact on subsidy distribution.
+For example, the positive coefficients for non-profit auspice and CWELCC Participation underscore their significant, policy-relevant impact on subsidy distribution.
 This clarity makes the model particularly valuable for stakeholders and policymakers who require actionable and easily communicated insights.
 The model's performance metrics further demonstrate its effectiveness.
-A McFadden's R² value of 0.454 indicates that the model explains a substantial portion of the variance in subsidy allocation.
-Additionally, the Area Under the Curve (AUC) of 0.8998 highlights the model’s exceptional discriminative ability, confirming its capacity to accurately differentiate between subsidized and non-subsidized centres.
-The low Root Mean Squared Error (RMSE) of 0.32 further attests to the model’s strong predictive performance.
+A McFadden's $R^2$ value of 0.454 indicates that the model explains a substantial portion of the variance in subsidy allocation.
+Additionally, the Area Under the Curve (AUC) of 0.906 highlights the model’s exceptional discriminative ability, confirming its capacity to accurately differentiate between subsidized and non-subsidized centres.
+The low Root Mean Squared Error (RMSE) further attests to the model’s strong predictive performance.
 Together, these metrics validate the model's reliability and robustness.
@@
 
-# Appendix A: Model Coefficients in Model Selection Process
+# Appendix {-}
+
+# Model Assumption {#sec-model-details}
+
+To ensure the validity of the logistic regression model, several key assumptions were assessed, including independence of observations, the appropriateness of a binary outcome, the linearity of predictors with the logit and absence of multicollinearity.
+The analysis integrates results from visual diagnostics, multicollinearity tests, and statistical measures.
+
+### 1. Independence of Observations
+
+The logistic regression model assumes that the observations are independent of each other.
+In this analysis, each data point corresponds to an individual child care center, ensuring independence.
+There is no clustering or repeated measures within the dataset, which validates this assumption.
+
+### 2. Binary Outcome
+
+The logistic regression model assumes a binary dependent variable.
+In this case, the outcome variable, `subsidy`, is binary, indicating whether a child care center receives a subsidy (1 = Subsidized, 0 = Not Subsidized).
+This aligns with the model's requirement, ensuring the suitability of the binomial family for fitting the data.
+
+### 3. Linearity of Predictors with the Logit
+
+The @fig-cr The component + residual plots evaluate the linearity of the continuous variables and the relationship between categorical predictors and the logit transformation.
+
 ```{r}
+#| label: fig-cr
+#| fig-cap: "CR Plot for Linearity Chekck: No Violate of Linearity Assumptions"
 #| echo: false
+#| message: false
 #| warning: false
-#| message: false
-# Create a coefficient table
-model_list <- list(
-  "Full Model" = log_model,
-  "AIC Model" = reduced_model_re,
-  "Simplified Model" = reduced_model_2
-)
-
-# Customize the table to display only AIC and Deviance
-modelsummary(
-  model_list,
-  output = "markdown",
-  gof_map = c("AIC", "Deviance")  # Include only AIC and Deviance in the table
-)
-
+# Customizing Component + Residual Plots with concise y-axis label
+crPlots(model, ylab = "Component+Residuals")  # Shortened y-axis label
 ```
 
-# Appendix B: Observational Data Methodology for Licensed Child Care Centres in Toronto
+- `TOTSPACE`: The relationship between the total space (TOTSPACE) and the logit appears approximately linear, as indicated by the flat, consistent pattern of residuals around the horizontal axis.
+This supports the assumption of linearity.
 
-## B.1 Population, Frame, and Sample
-### B.1.1 Population
+- `CWELCC Flag`: The plot for CWELCC participation shows a horizontal trend, suggesting no significant deviation from linearity. The data support the inclusion of this variable as a binary predictor.
+
+- `AUSPICE`: The residual patterns for categorical levels of AUSPICE (e.g., "Commercial Agency" and "Other") indicate distinct clusters with consistent variability.
+This suggests the categorical nature of this variable does not violate linearity assumptions.
+Overall, the visual inspection suggests that the linearity assumption for the predictors with the logit is met.
+
+### 4. Multicollinearity Assessment
+
+Variance Inflation Factor (VIF):
+
+To assess multicollinearity among the predictors, the VIF values for the reduced model variables were calculated.All VIF values are below 2, well within the acceptable threshold of 5, indicating minimal multicollinearity among the predictors.
+The independence of the predictors ensures the stability of the coefficient estimates.
+
+```{r,echo=FALSE, results='hide', message=FALSE, warning=FALSE}
+# Calculate VIF
+vif_values <- vif(model)
+vif_values
+```
+
+# Observational Data Methodology for Licensed Child Care Centres in Toronto
+
+## Population, Frame, and Sample
+
+### Population
+
 The population includes all licensed child care centres in Toronto as recorded in the publicly available dataset provided by Open Toronto.
@@
 Represented Groups: Centres adhering to provincial licensing requirements, as emphasized by Cleveland and Krashinsky [@cleveland2003benefits], who note that licensed care is generally associated with higher quality standards.
+
 Excluded Groups: Informal and unlicensed providers, which disproportionately to lower-income families and those in rural or underserved urban areas.
-### B.1.2 Frame
+
+### Frame
+
 The dataset represents a comprehensive census of licensed child care centres, reflecting administrative records compiled by the city.
+
 Strengths: Comprehensive coverage reduces selection bias and enhances geographic representativeness.
+
 Limitations: Static data may fail to capture temporal variations or operational changes, a common limitation noted in administrative datasets.
-### B.1.3 Sample
+
+### Sample
+
 The dataset uses census sampling of licensed child care centres, ensuring inclusion of all facilities within the licensing framework.
+
 Advantages: Census data minimizes sampling error and provides a reliable basis for spatial and capacity analysis.
+
 Drawbacks: Lack of informal care data may lead to underrepresentation of actual child care resources, echoing findings by [@tekin2007childcare] that informal care plays a critical role in many families’ child care arrangements.
 
-## B.2 Data Collection Methodology
-### B.2.1 Observational Data Compilation
+## Data Collection Methodology
+
+### Observational Data Compilation
+
 The dataset is derived from municipal administrative records, which are considered reliable for policy analysis [@cleveland2003benefits].
 Licensing authorities collect this data as part of routine compliance monitoring, ensuring high accuracy.
+
 Strengths: Administrative data is less prone to recall bias compared to survey data.
+
 Weaknesses: Lack of qualitative insights into service quality or user satisfaction.
-### B.2.2 Non-response Handling
+
+### Non-response Handling
+
 While the dataset does not involve survey non-response, its exclusion of unlicensed providers creates a systematic gap.
@@
 
-## B.3 Sampling Approach and Trade-offs
-### B.3.1 Strengths
+## Sampling Approach and Trade-offs
+
+### Strengths
+
 Comprehensive Coverage: Census sampling ensures no licensed centres are omitted.
 Geospatial Precision: Geographic coordinates support advanced spatial analysis, aligning with studies like [@larsen2015accessibility] on urban accessibility.
+
 High Validity: Licensing records provide robust validity, as they are subject to regulatory verification [@cleveland2003benefits].
-### B.3.2 Limitations
+
+### Limitations
+
 Exclusion of Informal Care: Research by Morrissey [@morrissey2010childcare] highlights that informal care is often preferred for flexibility or affordability, making its exclusion a significant limitation.
@@
 
-## B.4 Observational Bias and Measurement Challenges
-### B.4.1 Observational Bias
+## Observational Bias and Measurement Challenges
+
+### Observational Bias
+
 Biases inherent in observational datasets include selection bias (due to licensing criteria) and survivorship bias (exclusion of closed centres).
-### B.4.2 Measurement Challenges
+
+### Measurement Challenges
+
 Geographic Aggregation: Aggregating data to broader areas can obscure micro-level disparities.
@@
 
-## B.5 Methodological Enhancements and Recommendations
-### B.5.1 Enhancements
+## Methodological Enhancements and Recommendations
+
+### Enhancements
+
 Incorporating Temporal Data: Adding longitudinal data could enable trend analysis, echoing the approach of [@fuller1996family].
+
 Integration with Demographics: Linking with census data would allow for equity analysis, consistent with the methodology used by [@larsen2015accessibility].
-### B.5.2 Recommendations
+
+### Recommendations
+
 Addressing Informal Care: Future studies should integrate data from community surveys to include informal providers, as suggested by [@morrissey2010childcare].
+
 Dynamic Updates: Regular updates to administrative records would enhance relevance, a recommendation supported.
+
 Geospatial Enhancements: Including data on transit access or neighborhood socioeconomic conditions could enrich spatial analyses, aligning with findings by [@tekin2007childcare]

### 2024-12-11 paper/paper.qmd
updated model specification in paper

@@
 plot1
-
 ```
@@
 
-- `glmnet` [@]: Applied for fitting regularized regression models and feature selection.
+- `glmnet` [@citeglmnet]: Applied for fitting regularized regression models and feature selection.
 
@@
 
+cor_matrix <- cor(data %>% select(TOTSPACE, subsidy, cwelcc_flag), use = "complete.obs")
+
 # Plot the heatmap without axis labels
@@
 $$
-\text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{CWELCC Participation}) + \beta_3 (\text{Total Space})
+\text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{Other Auspice}) + \\ \beta_3 (\text{CWELCC Participation}) + \beta_4 (\text{Total Space})
 $$
@@
 - Measures the effect of a center being operated as a non-profit compared to the baseline (e.g., commercial auspice) on the log-odds of subsidy allocation.
-   - A positive $\beta_1$ increases the likelihood of receiving a subsidy for non-profit centers relative to the reference group.
 
-3. **$\beta_2$ (CWELCC Participation):**
+- A positive $\beta_1$ increases the likelihood of receiving a subsidy for non-profit centers relative to commercial centers.
+
+3. **$\beta_2$ (Other Auspice):**
+
+- Measures the effect of a center being operated as "other type" compared to the baseline (e.g., commercial auspice) on the log-odds of subsidy allocation.
+
+- A positive $\beta_2$ increases the likelihood of receiving a subsidy for other-type centers relative to commercial centers.
+
+4. **$\beta_3$ (CWELCC Participation):**
+
 - Captures the influence of participating in the Canada-Wide Early Learning and Child Care (CWELCC) program on the log-odds of subsidy allocation.
 
-4. **$\beta_3$ (Total Space):**
+5. **$\beta_4$ (Total Space):**
+
 - Represents the effect of the number of licensed child care spaces (a continuous variable) on the log-odds of subsidy allocation.
-
-5. **$\epsilon$ (Error Term):**
-   - Accounts for unexplained variation in the log-odds of subsidy allocation not captured by the predictors
 

### 2024-12-11 paper/paper.qmd
updated citation
updated figure caption and beautified graphs and tables

@@
 ```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
-data <- read_parquet(here("data","02-analysis_data","analysis_data.parquet"))
+data <- read_parquet(here("data", "02-analysis_data", "analysis_data.parquet"))
 ```
@@
 data %>%
+  rename(
+    Ward = ward,
+    `Operating Auspice` = AUSPICE,
+    `Building Type` = bldg_type,
+    `CWELCC Participation` = cwelcc_flag,
+    `Total Space` = TOTSPACE,
+    Subsidy = subsidy
+  ) %>%
   head(10) %>%
-  gt::gt() %>%
-  gt::tab_header(
-    title = "Overview of Cleaned Data",
-    subtitle = "Displaying the first 10 rows"
-  )
+  gt::gt()
 ```
@@
 #| label: fig-subsidy
-#| fig-cap: "Distribution of Subsidy Allocation: Disparities Exist"
+#| fig-cap: "Distribution of subsidy allocation among licensed child care centres, indicating that 67.3% of centres receive subsidies while 32.7% do not."
 #| echo: false
@@
   labs(
-    title = "Distribution of Subsidy",
     x = "Subsidy",
@@
 
-- `pROC` [@citeproc]: Facilitated the computation and visualization of Receiver Operating Characteristic (ROC) curves and Area Under the Curve (AUC) metrics, enabling robust evaluation of the model's classification performance.
+- `pROC` [@citepROC]: Facilitated the computation and visualization of Receiver Operating Characteristic (ROC) curves and Area Under the Curve (AUC) metrics, enabling robust evaluation of the model's classification performance.
 
@@
     y = "Proportion",
-    fill = "Subsidy Status"
+    fill = "Subsidy"
   ) +
@@
   scale_y_discrete(labels = c("Total Space", "Subsidy", "CWELCC Participation")) + # Update y-axis labels
-  labs(
-    title = "Correlation Heatmap of Key Variables",
-    caption = "Key Variables: Total Space, Subsidy, and CWELCC Participation"
-  ) +
   theme_minimal() +
@@
    - Represents the baseline log-odds of subsidy allocation when all predictors are set to their reference categories or zero values.
+
    - It provides the starting point for predicting subsidy probabilities.
@@
 # Load model
-model <- readRDS(file = here("models","final_model.rds"))
+model <- readRDS(file = here("models", "final_model.rds"))
 
@@
 Overall, the model performs well but may require refinement, particularly in addressing instability in the AUSPICE: Other variable.
+
 @fig-cp further visualizes the significance of predictors.
@@
   labs(
-    title = "Coefficient Plot",
     x = "Coefficient Estimate",
@@
 # ROC Curve and AUC
-roc_curve <- roc(data$subsidy, 
+roc_curve <- roc(
+  data$subsidy,
   predict(model,
-                         newdata = data, type = "response"))
-plot(roc_curve, main = "ROC Curve", print.auc=T)
+    newdata = data %>%
+      rename(
+        Ward = ward,
+        `Operating_Auspice` = AUSPICE,
+        `Building_Type` = bldg_type,
+        `CWELCC_Participation` = cwelcc_flag,
+        `Total_Space` = TOTSPACE
+      ), type = "response"
+  )
+)
+plot(roc_curve, main = "ROC Curve", print.auc = T)
 ```
@@
 # Generate predicted probabilities for the test dataset
-data$predicted_prob <- predict(model, newdata = data, type = "response")
+data$predicted_prob <- predict(model, newdata = data %>%
+  rename(
+    Ward = ward,
+    `Operating_Auspice` = AUSPICE,
+    `Building_Type` = bldg_type,
+    `CWELCC_Participation` = cwelcc_flag,
+    `Total_Space` = TOTSPACE
+  ), type = "response")
 

### 2024-12-11 scripts/00-simulate_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Simulate Licened Child Care Centers dataset 
+# Purpose: Simulate Licened Child Care Centers dataset
 # Author: Claire Ma
-# Date: 25 November 2024 
-# Contact: minglu.ma@mail.utoronto.ca 
+# Date: 25 November 2024
+# Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `dplyr` package must be installed and loaded
 # Any other information needed? Make sure you are in the `starter_folder` rproj
@@ -17,28 +17,32 @@ library(dplyr)
 set.seed(1008047418)
 
 # Simulate dataset
-n <- 1000  # Number of observations
+n <- 1000 # Number of observations
 simulated_data <- data.frame(
-  ward = sample(1:25, n, replace = TRUE),  # Wards ranging from 1 to 25
+  ward = sample(1:25, n, replace = TRUE), # Wards ranging from 1 to 25
   AUSPICE = sample(
-    c("Non Profit Agency", "Commercial Agency", "Other"), 
-    n, replace = TRUE, prob = c(0.7, 0.2, 0.1)  # Adjust probabilities for three categories
-  ),  # AUSPICE categories
+    c("Non Profit Agency", "Commercial Agency", "Other"),
+    n,
+    replace = TRUE, prob = c(0.7, 0.2, 0.1) # Adjust probabilities for three categories
+  ), # AUSPICE categories
   bldg_type = sample(
-    c("Catholic Elementary (French)", "Catholic Elementary School", 
-      "Catholic High School", "Church", "Commercial Building", 
-      "Community College/University", "Community Health Centre", 
-      "Community Rec/Centre - Board Run", "Community/Rec Centre - City", 
+    c(
+      "Catholic Elementary (French)", "Catholic Elementary School",
+      "Catholic High School", "Church", "Commercial Building",
+      "Community College/University", "Community Health Centre",
+      "Community Rec/Centre - Board Run", "Community/Rec Centre - City",
       "Community/Recreation Centre", "High Rise Apartment", "Hospital/Health Centre",
-      "House", "Industrial Building", "Low Rise Apartment", "Office Building", "Other", 
-      "Place of Worship", "Private Elementary School", "Public (school closed)", 
[…]

### 2024-12-11 scripts/01-test_simulated_data.R

@@ -4,9 +4,9 @@
 # Date: 25 November 2024
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-  # - The `tidyverse` and `testthat` packages must be installed and loaded
-  # - 00-simulate_data.R must have been run
+# Pre-requisites:
+# - The `tidyverse` and `testthat` packages must be installed and loaded
+# - 00-simulate_data.R must have been run
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 

### 2024-12-11 scripts/02-download_data.R

@@ -23,7 +23,7 @@ childcare_licence_resources <- childcare_licence_packages %>%
 # Display the list of resources available in the "childcare Licence Statistics" package
 childcare_licence_resources
 # Download the .csv dataset
-childcare_licence_statistics <- childcare_licence_resources[3,] %>%
+childcare_licence_statistics <- childcare_licence_resources[3, ] %>%
   get_resource()
 childcare_licence_statistics
 

### 2024-12-11 scripts/03-clean_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: Cleans the raw data 
+# Purpose: Cleans the raw data
 # Author: Claire Ma
-# Date: 25 November 2024 
-# Contact: minglu.ma@mail.utoronto.ca 
+# Date: 25 November 2024
+# Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `dplyr`, `arrow`, and 'readr' packages must be installed and loaded
 # Any other information needed? Make sure you are in the `starter_folder` rproj
@@ -25,8 +25,10 @@ cleaned_data <- data %>%
   mutate(
     # Collapse sparse levels in bldg_type
     bldg_type = case_when(
-      bldg_type %in% c("Public Elementary (French)", "Community/Rec Centre - Private", 
-                       "Community/Rec Centre AOCC", "Multi Human Services Facility") ~ "Other",
+      bldg_type %in% c(
+        "Public Elementary (French)", "Community/Rec Centre - Private",
+        "Community/Rec Centre AOCC", "Multi Human Services Facility"
+      ) ~ "Other",
       TRUE ~ bldg_type
     ),
     # Collapse sparse levels in AUSPICE
@@ -35,8 +37,8 @@ cleaned_data <- data %>%
       TRUE ~ AUSPICE
     ),
     # Convert binary flags to numeric
-    cwelcc_flag = ifelse(cwelcc_flag == "Y", 1, 0),  # Convert to numeric 0/1
-    subsidy = ifelse(subsidy == "Y", 1, 0)           # Ensure numeric 0/1 encoding for subsidy
+    cwelcc_flag = ifelse(cwelcc_flag == "Y", 1, 0), # Convert to numeric 0/1
+    subsidy = ifelse(subsidy == "Y", 1, 0) # Ensure numeric 0/1 encoding for subsidy
   )
 
 #### Save data ####

### 2024-12-11 scripts/04-test_analysis_data.R

@@ -4,7 +4,7 @@
 # Date: 25 November 2024
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
+# Pre-requisites:
 # - The `arrow` and `testthat` packages must be installed and loaded
 # - 03-clean_data.R must have been run
 # Any other information needed? Make sure you are in the `starter_folder` rproj
@@ -44,5 +44,3 @@ test_that("All values in 'subsidy' are either 0 or 1", {
 test_that("All values in 'cwelcc_flag' are either 0 or 1", {
   expect_true(all(data$cwelcc_flag %in% c(0, 1)))
 })
-
-

### 2024-12-11 scripts/05-exploratory_data_analysis.R

@@ -1,8 +1,8 @@
 #### Preamble ####
-# Purpose: EDA 
+# Purpose: EDA
 # Author: Claire Ma
-# Date: 25 November 2024 
-# Contact: minglu.ma@mail.utoronto.ca 
+# Date: 25 November 2024
+# Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `dplyr`,'readr', 'ggplot2', 'reshape' and 'gridExtra'packages must be installed and loaded
 # Any other information needed? Make sure you are in the `starter_folder` rproj
@@ -25,52 +25,68 @@ summary(data)
 # 1. Distribution of the Target Variable (subsidy)
 plot1 <- ggplot(data, aes(x = as.factor(subsidy))) +
   geom_bar(fill = c("skyblue", "coral"), alpha = 0.8) +
-  labs(title = "Distribution of Subsidy",
-       x = "Subsidy (0 = No, 1 = Yes)",
-       y = "Count") +
+  labs(
+    title = "Distribution of Subsidy",
+    x = "Subsidy (0 = No, 1 = Yes)",
+    y = "Count"
+  ) +
   theme_minimal() +
-  theme(plot.title = element_text(size = 9),  # Reduce title size
-        axis.title = element_text(size = 10),  # Reduce axis title size
-        axis.text = element_text(size = 8))    # Reduce axis text size
+  theme(
+    plot.title = element_text(size = 9), # Reduce title size
+    axis.title = element_text(size = 10), # Reduce axis title size
+    axis.text = element_text(size = 8)
+  ) # Reduce axis text size
 
 # 2. Distribution of TOTSPACE (Histogram + Density)
 plot2 <- ggplot(data, aes(x = TOTSPACE)) +
   geom_histogram(aes(y = ..density..), bins = 30, fill = "skyblue", alpha = 0.8) +
   geom_density(color = "blue", size = 1) +
-  labs(title = "Distribution of TOTSPACE",
-       x = "TOTSPACE",
-       y = "Density") +
+  labs(
+    title = "Distribution of TOTSPACE",
+    x = "TOTSPACE",
+    y = "Density"
+  ) +
   theme_minimal() +
-  theme(plot.title = element_text(size = 9),
-        axis.title = element_text(size = 10),
-        axis.text = element_text(size = 8))
+  theme(
+    plot.title = element_text(size = 9),
+    axis.title = element_text(size = 10),
[…]

### 2024-12-11 scripts/06-model_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Models
 # Author: Minglu Ma
-# Date: 28 November 2024 
+# Date: 28 November 2024
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `caret`, `arrow`, `modelsummary` and 'ggplot2' package must be installed and loaded
@@ -31,18 +31,22 @@ summary(full_model)
 
 # Stepwise selection based on AIC
 step_model_aic <- step(full_model, direction = "both", trace = TRUE)
-summary(step_model_aic)  # AIC-based selected model
+summary(step_model_aic) # AIC-based selected model
 
 # Refit model by removing non-significant variables to obtain the reduced model
-reduced_model <- glm(formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE, 
-                       family = binomial, data = train_data)
+reduced_model <- glm(
+  formula = subsidy ~ AUSPICE + cwelcc_flag + TOTSPACE,
+  family = binomial, data = train_data
+)
 summary(reduced_model)
 
 # Create a binary variable for "Non Profit Agency"
 train_data$AUSPICE_NonProfit <- ifelse(train_data$AUSPICE == "Non Profit Agency", 1, 0)
 # Fit a simplified model with the binary variable for AUSPICE
-simplified_model <- glm(formula = subsidy ~ AUSPICE_NonProfit + bldg_type + cwelcc_flag + TOTSPACE, 
-                      family = binomial, data = train_data)
+simplified_model <- glm(
+  formula = subsidy ~ AUSPICE_NonProfit + bldg_type + cwelcc_flag + TOTSPACE,
+  family = binomial, data = train_data
+)
 summary(simplified_model)
 
 # Create a coefficient table of all models
@@ -56,21 +60,35 @@ model_list <- list(
 # Customize the table to display only AIC and Deviance
 modelsummary(
   model_list,
-  gof_map = c("AIC", "Deviance")  # Include only AIC and Deviance in the table
+  gof_map = c("AIC", "Deviance") # Include only AIC and Deviance in the table
 )
 
 # Fit models to full analysis data
+# Rename varaible names to beautify model output
+data <- data %>%
+  mutate(AUSPICE_NonProfit = ifelse(AUSPICE == "Non Profit Agency", 1, 0)) %>%
+  rename(
+    Ward = ward,
[…]

### 2024-12-11 paper/paper.qmd
edited paper and rendered succesfully

@@
 
-Licensed child care centres in urban settings like Toronto play a pivotal role in delivering high-quality, structured child care.
-These centres adhere to stringent regulations, ensuring compliance with standards for safety, staffing, and curriculum.
-Research highlights that children attending licensed centres, particularly those supported by subsidies, experience better developmental outcomes.
-Subsidized centres provide professional environments with trained educators, comprehensive programming, and age-appropriate resources, offering children a strong foundation for lifelong learning and success.
-Subsidies are a cornerstone of this ecosystem, enabling licensed centres to cover operational costs, retain qualified staff, and maintain compliance with regulatory standards, all of which enhance the quality of care provided.
+Licensed child care centres in urban areas like Toronto provide high-quality, regulated care, ensuring safety, staffing, and curriculum standards.
+Research shows that subsidized centres, with trained educators and comprehensive programming, support better child development outcomes.
+Subsidies are crucial for covering operational costs, retaining qualified staff, and maintaining regulatory compliance, enhancing the quality of care.
 
@@
 
-This study utilizes the Toronto Open Data: Licensed Child Care Centres dataset to explore the factors that affect subsidy allocation to licensed centres.
-By analyzing variables such as ward, operating auspice (Commercial, Non Profit or Public), CWELCC, type of building, and total space, this research aims to uncover the question - “What factors influence the allocation of subsidies to licensed child care centres in Toronto?”.
-The findings will contribute to informing policies that promote equity and efficiency in subsidy allocation, ultimately supporting the goals of accessible and high-quality child care in Toronto.
-Additionally, these insights can serve as a valuable tool for child care centres to self-assess and enhance their eligibility for subsidies.
+This study analyzes the Toronto Open Data: Licensed Child Care Centres dataset to examine factors influencing subsidy allocation, including ward, operating auspice, CWELCC participation, building type, and total space [@citeopendatatoronto; @toronto2024licensed].
+The findings aim to inform equitable and efficient subsidy policies, support accessible, high-quality child care in Toronto, and help centres enhance their subsidy eligibility.
 
@@
 
-The remainder of this paper is structured as follows.
-@sec-data describes the dataset used for the analysis, including its source, key variables, and preprocessing steps, emphasizing its real-world context and relevance to understanding subsidy allocation in Toronto's child care system.
-@sec-model details the logistic regression model employed in the study, including the rationale for its selection, mathematical formulation, and key predictors.
-The model assumptions, diagnostics, and validation methods are also discussed to ensure robustness and reliability.
-@sec-results contains the results of the logistic regression analysis are presented, highlighting the significant predictors of subsidy allocation, ass well as the model's fit.
-@sec-discussion discusses what was done in this study, giving detailed explanation of implications of the findings, limitations and suggestion for future studies.
-Furthermore, an appendix including supplementary materials and data collection evaluation is provided to ensure transparency and reproducibility.
+The paper is structured as follows: @sec-data introduces the dataset, its source, key variables, and preprocessing steps, highlighting its relevance to understanding subsidy allocation in Toronto's child care system.
+@sec-model outlines the logistic regression model, including its rationale, formulation, key predictors, and validation methods.
+@sec-results presents the analysis results, focusing on significant predictors and model fit.
+@sec-discussion interprets the findings, discusses implications, and outlines limitations and future research directions.
+An appendix with supplementary materials and data evaluation is included for transparency and reproducibility.
 
@@
 
-The dataset used in this study was sourced from the [@citeopendatatoronto; @toronto2024licensed] made publicly available by the City of Toronto.
+The dataset used in this study was sourced from a publicly available site by the City of Toronto [@citeopendatatoronto; @toronto2024licensed].
 This original raw dataset provides detailed information about licensed child care centres, including 20 variables capturing aspects of their location, operating auspice (e.g., non-profit, public, or commercial), space usage, building type, participation in government programs such as the Canada-Wide Early Learning and Child Care (CWELCC) system, and other operational details.
@@
 #| label: tbl-overview
+#| tbl-cap: "Overview of the cleaned dataset for licensed child care centers, summarizing key variables such as governance model (Operating Auspice), building type, CWELCC participation, total licensed space, and subsidy status, providing a snapshot of the dataset's structure and focus"
 #| echo: false
@@
 
-The dataset used for this study is the **`Licensed Child Care Centres dataset`**, sourced from the [@citeopendatatoronto; @toronto2024licensed] It provides detailed information about licensed child care centres in Toronto, capturing aspects such as their governance, capacity, infrastructure, and subsidy status.
+The dataset used for this study is the **`Licensed Child Care Centres dataset`**, sourced from the [@citeopendatatoronto; @toronto2024licensed].
+It provides detailed information about licensed child care centres in Toronto, capturing aspects such as their governance, capacity, infrastructure, and subsidy status.
 The original dataset consisted of 1071 records for all licensed child care centres within the city.
@@
 The data for this study was systematically downloaded, cleaned, analyzed, and visualized using **`R`** [@citeR], a statistical programming language.
-The following are major packages used for this study:
-
-- `opendatatoronto`[@citeopendatatoronto]: Used to access and retrieve the Licensed Child Care Centres dataset directly from the City of Toronto's open data portal.
-
--`arrow` [@citearrow]: Provided efficient tools for reading and writing Parquet files, enabling fast and memory-efficient handling of large datasets during analysis.
-
-- `here` [@citehere]: Simplified file referencing by creating relative paths, ensuring reproducibility and consistency in accessing datasets, scripts, and outputs across different working environments.
-
-- `readr` [@citereadr]: Simplified the import and parsing of raw data into R.
-
-- `tidyverse` [@citetidyverse]: Streamlined data manipulation, cleaning, and visualization processes.
-
-- `dplyr` [@citedplyr]: Provided tools for filtering, transforming, and summarizing the dataset effectively.
-
-- `tidyr` [@citetidyr]: Enabled data tidying processes such as reshaping, separating, or combining, and handling missing values to structure the dataset into a clean and analyzable format.
-
-- `ggplot2` [@citeggplot2]: Created powerful and flexible visualizations tailored to the analysis needs.
-
-- `ggcorrplot` [@citeggcorrplot]: Simplified the visualization of correlation matrices with customizable heatmaps, including options for labeling and styling to enhance interpretability and presentation.
-
-- `glmnet` [@citeglmnet]: Applied for fitting regularized regression models and feature selection.
-
-- `modelsummary` [@citemodelsummary]: Streamlined the creation of comprehensive and customizable summary tables for regression models, including key statistics such as AIC, BIC, and coefficient estimates, to facilitate clear model comparisons and reporting.
-
-- `stats` [@citestats]: Provided core statistical functions to fit models, perform hypothesis testing, and calculate measures such as p-values, log-likelihoods, and AIC for model evaluation.
-
-- `car` [@citecar]: Used for diagnostic tools, including Variance Inflation Factor (VIF) tests, to assess multicollinearity.
-
-- `caret` [@citecaret]: Enabled the development, validation, and evaluation of machine learning models, including training-test splits and performance metrics.
-
-- `pROC` [@citepROC]: Facilitated the computation and visualization of Receiver Operating Characteristic (ROC) curves and Area Under the Curve (AUC) metrics, enabling robust evaluation of the model's classification performance.
-
-- `stargazer` [@citestagazer]: Generated formatted regression tables for outputs.
-
-- `broom` [@citebroom]: Simplified the process of converting model outputs into tidy data frames, enabling seamless integration of statistical results with visualization and reporting workflows.
-
-- `kableExtra` [@citekableExtra]:Enhanced the presentation of tables by adding advanced formatting options, including captions, headers, and styling, for polished and professional reporting.
-
-- `gt` [@citegt]: Enabled the creation of aesthetically pleasing and highly customizable tables for presenting data and model summaries in a clean and professional format.
-
-- `knitr` [@citeknitr]: Dynamically integrated code, results, and plots into the final document for seamless reporting.
+Several `R` packages were utilized in this study and they are described in {@sec-R-package}.
 
@@
 #| label: fig-relationbldgtype
-#| fig-cap: "Subsidy Allocation by Building Type: Higher Subsidy Proportions in Public and Purpose-Built Facilities"
+#| fig-cap: "Proportional distribution of subsidy across building types, highlighting variations in subsidy allocation among different facility categories based on their infrastructure and alignment with eligibility criteria."
 #| echo: false
@@
 #| label: fig-relationAuspice
-#| fig-cap: "Subsidy Allocation by Operating Auspice: Non-Profit Agencies and 'Other' Predominantly Subsidized"
+#| fig-cap: "Proportional distribution of subsidy by operating auspice, illustrating the prevalence of subsidies across different governance models such as commercial, non-profit, and other agencies,  highlighting the high proporation of subsidized centres of non-profit agencies, reflecting the alignment of subsidies with non-profit objectives of affordability and accessibility."
 #| echo: false
@@
 Additionally, the stronger correlation between CWELCC participation and subsidy (0.48) highlights that subsidy allocation may target entities meeting specific programmatic or policy criteria, consistent with the literature emphasizing strategic targeting of subsidies to maximize societal impact [@weisbrod1998profit].
-The weaker correlation between total space and CWELCC oarticipation (0.16) suggests that program eligibility is less dependent on size and more on qualitative factors like service type or demographic focus, which is supported by [@anheier2005nonprofit] analysis of non-profit funding models.
+The weaker correlation between total space and CWELCC oarticipation (0.16) suggests that program eligibility is less dependent on size and more on qualitative factors like service type or demographic focus, which is supported by an established analysis of non-profit funding models [@anheier2005nonprofit].
 Together, these correlations emphasize the nuanced role of subsidies in balancing operational scale and policy alignment, underscoring the importance of strategic allocation in public funding [@salamon1995partners].
@@
 #| label: fig-key
-#| fig-cap: "Correlation Between Total Space, Subsidy Allocation, and CWELCC Participation"
+#| fig-cap: "Correlation heatmap illustrating the relationships between total space, subsidy, and CWELCC participation, showing a moderate positive correlation between subsidy and CWELCC participation (0.48) and weaker correlations with total space (0.25), reflecting the nuanced factors influencing subsidy allocation."
 #| echo: false
@@
 $$
+\begin{aligned}
 \text{logit}(P(Y=1)) = \beta_0 + \beta_1 (\text{Non-Profit Auspice}) + \beta_2 (\text{Other Auspice}) + \\ \beta_3 (\text{CWELCC Participation}) + \beta_4 (\text{Total Space})
+\end{aligned}
 $$
@@
     \]
-    This transformation ensures that the predicted probabilities remain between 0 and 1.
 \end{itemize}
@@
 #| message: false
-#| tbl-cap: "Regression Result"
+#| tbl-cap: "Final logistic regression model results for subsidy allocation, showing significant predictors including operating auspice (Non-Profit Agency), CWELCC participation, and total space, with model fit metrics (AIC = 760.8, BIC = 785.7, RMSE = 0.32) indicating robust performance."
 
@@
 #| label: fig-cp
-#| fig-cap: "Coefficient Estimates for Predictors of Subsidy Allocation"
+#| fig-cap: "Coefficient plot for the logistic regression model, highlighting the significance of predictors with 95% confidence intervals, where most predictors demonstrate strong positive associations with subsidy allocation, exceprt for 'Other' operating auspice lacks statistical significance."
 #| echo: false
@@
 #| label: fig-roc
-#| fig-cap: "ROC Curve for Model Performance: Strong Model Performance with AUC 0.906"
+#| fig-cap: "Receiver Operating Characteristic (ROC) curve demonstrating the model's classification performance, with an Area Under the Curve (AUC) of 0.906, indicating excellent discriminatory ability between subsidized and non-subsidized child care centers."
 #| echo: false
@@
 #| label: fig-pvo
-#| fig-cap: " Predicted vs. Observed Probability Plot: Model Calibration and Accuracy"
+#| fig-cap: " Plot of observed outcomes versus predicted probabilities, illustrating the alignment between model predictions and actual subsidy allocation, with a strong diagonal trend indicating good predictive performance."
 #| echo: false
@@
 
-Subsidy allocation to licensed child care centres in Toronto addresses the critical issue of affordability, making high-quality early childhood education accessible to more families as licensed centres must meet strict safety, staffing, and programming standards, which foster children’s cognitive, social, and emotional growth [@cleveland2009nonprofit].
+Subsidy allocation to licensed child care centres in Toronto addresses the critical issue of affordability, making high-quality early childhood education accessible to more families as licensed centers must meet strict safety, staffing, and programming standards, which foster children’s cognitive, social, and emotional growth [@cleveland2009nonprofit].
 Without subsidies, the cost of regulated care can be prohibitive, particularly for low-income households.
-This paper undertakes a detailed examination of the factors influencing subsidy allocation to licensed child care centres in Toronto, leveraging the City of Toronto's Licensed Child Care Centres dataset from Open Data porta, which includes detailed information about 1,071 licensed centers[@citeopendatatoronto].
+This paper undertakes a detailed examination of the factors influencing subsidy allocation to licensed child care centres in Toronto, leveraging the City of Toronto's Licensed Child Care Centres dataset from Open Data porta, which includes detailed information about 1,071 licensed centers [@citeopendatatoronto].
 This study employs a logistic regression model-binomial family to identify relationships between key predictor variables and the binary dependent variable – receiving subsidies.
 
-The dataset underwent meticulous preprocessing to ensure reliability and accuracy for analysis.
-This involved several key steps of data cleaning, variable transformation and training-test Split.
-Initially, variables of operating auspice, ward, building type, total space and CWELCC participation were chosen based their relevance and practical influence subsidy outcomes and forecasting supported by scholar literatures.
-After fitting and improving the model using stepwise selection based on the Akaike Information Criterion (AIC), non-significant variables (ward and building type) were removed.
-The final model retained operating auspice, CWELCC participation, and total space as key predictors.
-The assumptions underpinning the logistic regression model were thoroughly validated, ensuring its statistical rigor and reliability.
-Independence of observations was confirmed, as each data point corresponds to a unique child care centre, eliminating concerns of clustering or dependency.
-Linearity between continuous predictors, such as total space, and the logit transformation was validated through component + residual plots, which revealed consistent patterns, supporting the appropriateness of the model.
-Additionally, multicollinearity was minimized, with Variance Inflation Factor (VIF) values well below the critical threshold of 5, indicating that the predictors are independent and the coefficient estimates are stable.
-Together, these validations affirm the robustness of the model and its suitability for the analysis.
+The dataset underwent thorough preprocessing to ensure accuracy and reliability, including data cleaning, variable transformation, and a training-test split.
+Key predictors—operating auspice, CWELCC participation, and total space—were selected based on their relevance, supported by literature.
+Stepwise selection using AIC removed non-significant variables (ward and building type).
+Logistic regression assumptions were validated: independence of observations was ensured, linearity of continuous predictors (e.g., total space) was confirmed through residual plots, and multicollinearity was minimized with VIF values below 5.
+These steps affirm the model's statistical rigor and suitability for the analysis.
 
-The result coefficients in table the logistic regression model provide a detailed understanding of how key predictors influence the likelihood of subsidy allocation to licensed child care centres in Toronto.
-By measuring the change in log-odds of subsidy allocation associated with each predictor, the model quantifies the relative importance of governance models, program participation, and operational capacity.
-The coefficient for non-profit auspice emerged as strongly positive and statistically significant, indicating that non-profit child care centres are far more likely to receive subsidies than commercial or public centres.
-This is reflective of policy priorities that favor organizations with a social mission over those with profit-oriented objectives.
-Non-profits are often viewed as better aligned with public goals of equity and accessibility, as they reinvest surplus revenues into improving care quality rather than distributing profits [@hansmann1980role].
-This is consistent with research by [@salamon1995partners], who noted that non-profits often fill critical gaps in the provision of public services, making them natural candidates for targeted funding.
-In the context of child care, non-profits may also be more likely to serve economically vulnerable populations, further justifying their prioritization for subsidies.
-The odds ratio derived from this coefficient underscores the strength of this relationship, suggesting that non-profit centres are several times more likely to receive subsidies compared to commercial centres.
-Participation in the Canada-Wide Early Learning and Child Care (CWELCC) program was the most significant predictor in the model, with a highly positive coefficient.
-This result highlights the critical role of policy alignment in subsidy allocation.
-Centres participating in CWELCC demonstrate compliance with national and provincial affordability initiatives, making them high-priority recipients of government funding.
-Research by [@bennett2011working] supports this finding, emphasizing that early childhood programs aligned with broader governmental objectives are often better positioned to secure resources.
-The odds ratio for CWELCC participation indicates that such centres are substantially more likely to receive subsidies, which is consistent with targeted funding strategies aimed at expanding access to high-quality, affordable child care [@kaga2010caring].
-Total space, representing the number of spaces a centre is licensed to operate, was another important predictor, although its coefficient was smaller in magnitude compared to operating auspice and CWELCC participation.
-This positive coefficient suggests that larger centres are more likely to receive subsidies, likely due to their capacity to serve more families and their operational scale.
-Larger centres can achieve economies of scale and often have greater visibility, making them attractive candidates for public funding [@weisbrod1998profit].
-However, the smaller effect size of this variable indicates that capacity alone is insufficient to determine subsidy allocation.
-This finding aligns with [@penn2011quality], who argues that while capacity is an important practical consideration, other factors—such as governance and programmatic alignment—carry more weight in funding decisions.
-Interpreting these coefficients through odds ratios further clarifies their impact.
-For instance, the odds ratio for CWELCC participation suggests that centres in the program are several times more likely to receive subsidies compared to non-participating centres, holding other factors constant.
-Similarly, the odds ratio for non-profit governance reinforces the preferential treatment of non-profits in subsidy allocation policies.
-These findings align with the broader literature on public funding, which emphasizes the strategic use of subsidies to support centres that meet both operational and policy criteria [@penn2011quality].
-The statistical significance of these coefficients underscores their reliability as shown in figure.
-Variables such as non-profit auspice and CWELCC Participation demonstrated small standard errors and strong significance levels, reinforcing their influence on subsidy allocation.
-In contrast, variables with less consistent effects, such as certain building types or governance categories in the "other" category, exhibited instability, suggesting that their role in funding decisions may be more context-specific or secondary.
-The model's findings highlight a strategic approach to subsidy allocation, where funding decisions are guided by alignment with policy goals, operational capacity, and governance structures.
+The logistic regression model provides insights into key predictors influencing subsidy allocation to licensed child care centres in Toronto, quantifying the impact of governance models, program participation, and operational capacity.
+The coefficient for non-profit auspice is strongly positive and statistically significant, indicating that non-profit centres are far more likely to receive subsidies compared to commercial or public centres.
+This aligns with policy priorities favoring organizations with a social mission, which often serve economically vulnerable populations, as noted by Hansmann [@hansmann1980role] and Salamon et al.
+[@salamon1995partners].
+Non-profits’ alignment with public goals of equity and accessibility underscores their prioritization for funding.
+Participation in the Canada-Wide Early Learning and Child Care (CWELCC) program emerged as the most significant predictor, highlighting the importance of policy alignment.
+Centres in CWELCC, which comply with national affordability initiatives, are significantly more likely to receive subsidies, as emphasized by Bennett et al.
+[@bennett2011working] and Kaga et al.
+[@kaga2010caring].
+This aligns with targeted strategies aimed at expanding affordable, high-quality child care access.
+Total space, representing a centre’s licensed capacity, also positively influences subsidy allocation, although its effect is smaller.
+Larger centres, capable of serving more families, are attractive candidates for funding due to economies of scale and visibility, as noted by Weisbrod [@weisbrod1998profit].
+However, its smaller coefficient indicates that capacity alone does not determine funding, consistent with Penn’s findings that governance and programmatic alignment play a greater role [@penn2011quality].
+Odds ratios further underscore the strength of these predictors, with non-profits and CWELCC participants several times more likely to receive subsidies.
+The statistical significance of these variables, evidenced by small standard errors, reinforces their reliability, while less consistent variables like certain building types exhibited instability, suggesting a secondary role in funding decisions.
+These findings highlight a strategic approach to subsidy allocation, balancing operational capacity with policy goals and governance structures [@penn2011quality].
 
@@
 Although this assumption is often reasonable, it may oversimplify complex, non-linear relationships that can exist in real-world phenomena such as subsidy allocation.
-As [@harrell2015regression] notes, failing to capture these non-linear relationships can lead to biased estimates and limit the model’s predictive power.
+Failing to capture these non-linear relationships can lead to biased estimates and limit the model’s predictive power [@harrell2015regression].
 Another limitation is the model’s dependence on correct specification of predictors.
@@
 For instance, the combined effect of Non-Profit Auspice and CWELCC Participation could provide valuable insights into how policy and governance jointly influence subsidy allocation.
-[@hosmer2013applied] highlight that logistic regression can oversimplify complex relationships if interaction terms are not considered, potentially leading to incomplete conclusions.
+Logistic regression can oversimplify complex relationships if interaction terms are not considered, potentially leading to incomplete conclusions [@hosmer2013applied].
 Finally, the static nature of the model is another drawback.
 Logistic regression provides a snapshot of relationships at a single point in time, failing to capture temporal dynamics or policy changes that can influence subsidy allocation over time.
-As Singer and [@singer2003applied] suggest, incorporating longitudinal data could provide a more nuanced understanding of how these relationships evolve.
+Incorporating longitudinal data could provide a more nuanced understanding of how these relationships evolve [@singer2003applied].
 
@@
 The population includes all licensed child care centres in Toronto as recorded in the publicly available dataset provided by Open Toronto.
-This population aligns with studies on regulated child care, such as [@morrissey2010childcare], which emphasizes the role of licensing in ensuring quality and safety in early childhood education.
-However, the dataset excludes unlicensed child care providers, limiting its scope.
-Represented Groups: Centres adhering to provincial licensing requirements, as emphasized by Cleveland and Krashinsky [@cleveland2003benefits], who note that licensed care is generally associated with higher quality standards.
+This population aligns with studies on regulated child care that  emphasize the role of licensing in ensuring quality and safety in early childhood education [@morrissey2010childcare].
+Licensing sets a minimum standard for safety, staff qualifications, and child-to-provider ratios, thereby offering a benchmark for regulated care.
+However, this dataset inherently excludes unlicensed child care providers, which limits the representativeness of the broader child care system.
+Unlicensed providers often cater to lower-income families or those in rural and underserved urban areas [@cleveland2003benefits].
+These providers may offer affordable or flexible care arrangements but are not bound by the same quality standards, making them a critical but underrepresented part of the child care ecosystem.
 
-Excluded Groups: Informal and unlicensed providers, which disproportionately to lower-income families and those in rural or underserved urban areas.
+- Represented Groups: The dataset focuses on licensed centres that adhere to provincial regulatory requirements, ensuring they meet established standards for infrastructure, safety, and staff qualifications.
+These facilities are more likely to participate in government subsidy programs and policy initiatives, aligning with Cleveland and Krashinsky's findings that licensed child care is generally associated with higher quality standards [@cleveland2003benefits].
+
+- Excluded Groups: The dataset excludes informal and unlicensed providers, which disproportionately serve families with lower socioeconomic status or those living in areas with limited access to licensed centres.
+This exclusion highlights a systemic gap, as research shows that unlicensed care often fills critical needs for flexibility and affordability, especially for families in marginalized communities [@fuller1996family].
 
@@
 
-Strengths: Comprehensive coverage reduces selection bias and enhances geographic representativeness.
+- Strengths: The census-like nature of the dataset significantly reduces selection bias, as it captures all licensed child care centres within Toronto’s boundaries.
+The inclusion of geographic coordinates allows for advanced spatial analysis, making it possible to study access and equity in child care distribution.
+This level of coverage enhances the dataset's utility for policy analysis and urban planning.
 
-Limitations: Static data may fail to capture temporal variations or operational changes, a common limitation noted in administrative datasets.
+- Limitations: While comprehensive, the dataset is static and does not capture temporal changes, such as new centres opening, existing ones closing, or changes in capacity.
+As highlighted in the literature, administrative datasets often fail to account for dynamic operational changes, limiting their applicability for longitudinal analysis [@tekin2007childcare].
+Furthermore, the exclusion of qualitative attributes, such as user satisfaction or service quality, reduces the dataset's ability to capture nuanced aspects of child care provision.
 
@@
 
-The dataset uses census sampling of licensed child care centres, ensuring inclusion of all facilities within the licensing framework.
+The dataset employs census sampling, meaning all licensed child care centres are included.
+This approach ensures that the sample is representative of the licensed child care sector in Toronto, eliminating sampling error associated with random or stratified sampling methods.
 
-Advantages: Census data minimizes sampling error and provides a reliable basis for spatial and capacity analysis.
+- Strengths: By using a census approach, the dataset minimizes sampling error and provides a reliable foundation for spatial and capacity-related analyses.
+Census data allows for a holistic view of the licensed child care system, capturing the full scope of regulated providers within the city.
 
-Drawbacks: Lack of informal care data may lead to underrepresentation of actual child care resources, echoing findings by [@tekin2007childcare] that informal care plays a critical role in many families’ child care arrangements.
+- Limitations: The reliance on census data excludes informal care arrangements, which are often a vital resource for families who face financial or logistical barriers to accessing licensed centers.
+Tekin emphasizes that informal care plays a critical role in many families' child care decisions, and its absence may lead to an underestimation of the actual child care resources available in Toronto [@tekin2007childcare].
 
@@
 
-The dataset is derived from municipal administrative records, which are considered reliable for policy analysis [@cleveland2003benefits].
-Licensing authorities collect this data as part of routine compliance monitoring, ensuring high accuracy.
+The dataset originates from administrative records maintained by the licensing authorities of the City of Toronto.
+These records are generated as part of routine compliance monitoring, ensuring a high degree of accuracy and reliability.
+Administrative data is widely regarded as a robust source for policy and program evaluation [@cleveland2003benefits].
+Such data typically includes detailed information about center capacity, governance models, and geographic location, making it suitable for quantitative analysis.
 
-Strengths: Administrative data is less prone to recall bias compared to survey data.
+- Strengths: Administrative data offers several advantages, including its high accuracy, as it is subject to rigorous regulatory oversight.
+Unlike survey data, it is less prone to recall bias and provides a standardized framework for comparing centres across various dimensions, such as capacity, location, and subsidy participation.
 
-Weaknesses: Lack of qualitative insights into service quality or user satisfaction.
+- Limitations: However, the dataset lacks qualitative insights, such as parental satisfaction or staff perceptions, which are crucial for understanding the broader impact of child care services.
+This limitation underscores the need for supplementary data sources, such as surveys or focus groups, to provide a more comprehensive view.
 
@@
 While the dataset does not involve survey non-response, its exclusion of unlicensed providers creates a systematic gap.
-Research by Fuller et al.
-[@fuller1996family] shows that informal care often fills critical voids in underserved areas, and its exclusion may understate the full scope of child care provision.
+Research shows that informal care often fills critical voids in underserved areas, and its exclusion may understate the full scope of child care provision [@fuller1996family].
 
@@
 
-Comprehensive Coverage: Census sampling ensures no licensed centres are omitted.
-Geospatial Precision: Geographic coordinates support advanced spatial analysis, aligning with studies like [@larsen2015accessibility] on urban accessibility.
+- Comprehensive Coverage: Census sampling ensures that no licensed centers are omitted, providing a complete overview of the licensed child care landscape.
 
-High Validity: Licensing records provide robust validity, as they are subject to regulatory verification [@cleveland2003benefits].
+- Geospatial Precision: The inclusion of geographic coordinates facilitates spatial analyses, such as proximity studies and accessibility evaluations, aligning with methodologies used in urban planning research [@larsen2015accessibility].
+
+- High Validity: Licensing records are validated through routine inspections and compliance monitoring, ensuring the reliability of the dataset [@cleveland2003benefits].
 
@@
 
-Exclusion of Informal Care: Research by Morrissey [@morrissey2010childcare] highlights that informal care is often preferred for flexibility or affordability, making its exclusion a significant limitation.
-Static Nature: The lack of longitudinal data limits the ability to analyze trends.
-Regulatory Bias: Centers excluded due to non-compliance may disproportionately represent marginalized communities.
+- Exclusion of Informal Care: Informal care arrangements, often preferred for their affordability and flexibility, are absent from the dataset.
+This exclusion limits the dataset's applicability for studying the full scope of child care options available to families [@morrissey2010childcare].
+
+- Static Nature: The dataset represents a snapshot in time, limiting its utility for analyzing trends or changes in the child care sector over time.
+
+- Regulatory Bias: Centers excluded due to non-compliance with licensing standards may disproportionately represent marginalized communities, skewing the dataset’s representativeness.
 
@@
 
-Biases inherent in observational datasets include selection bias (due to licensing criteria) and survivorship bias (exclusion of closed centres).
+Selection bias is inherent in observational datasets, as the inclusion criteria (i.e., licensing) inherently exclude certain providers.
+Additionally, survivorship bias may arise from the exclusion of centres that have closed, potentially skewing the analysis toward larger, more established providers.
 
@@
 
-Geographic Aggregation: Aggregating data to broader areas can obscure micro-level disparities.
-Capacity Limitations: Reported capacities may not reflect actual utilization or unmet demand, as noted by [@blau2006preschool].
+- Geographic Aggregation: Aggregating data to broader geographic units, such as wards or neighborhoods, can obscure micro-level disparities in access or service quality.
+
+- Capacity Limitations: Reported capacities may not accurately reflect actual utilization or unmet demand.
+Blau notes that capacity data often fails to account for operational constraints, such as staffing shortages or seasonal fluctuations [@blau2006preschool].
 
@@
 
-Incorporating Temporal Data: Adding longitudinal data could enable trend analysis, echoing the approach of [@fuller1996family].
+- Incorporating Temporal Data: Adding longitudinal data would enable the analysis of trends, such as changes in capacity or subsidy participation [@fuller1996family].
 
-Integration with Demographics: Linking with census data would allow for equity analysis, consistent with the methodology used by [@larsen2015accessibility].
+- Integration with Demographics: Linking the dataset with census data would allow for equity-focused analyses, such as the relationship between socioeconomic status and access to licensed care [@larsen2015accessibility].
 
@@
 
-Addressing Informal Care: Future studies should integrate data from community surveys to include informal providers, as suggested by [@morrissey2010childcare].
+- Addressing Informal Care: Future studies should integrate data from community surveys or focus groups to capture informal care arrangements [@morrissey2010childcare].
 
-Dynamic Updates: Regular updates to administrative records would enhance relevance, a recommendation supported.
+- Dynamic Updates: Regular updates to administrative records would enhance the dataset’s relevance and applicability, addressing limitations related to its static nature.
 
-Geospatial Enhancements: Including data on transit access or neighborhood socioeconomic conditions could enrich spatial analyses, aligning with findings by [@tekin2007childcare]
+- Geospatial Enhancements: Including data on public transit access or neighborhood-level socioeconomic indicators could provide a richer context for spatial analyses, aligning with Tekin’s findings on urban accessibility and equity [@tekin2007childcare].
+
+# R packages {#sec-R-package}
+
+The following are packages used for this study:
+
+- `opendatatoronto`[@citeopendatatoronto]: Used to access and retrieve the Licensed Child Care Centres dataset directly from the City of Toronto's open data portal.
+
+- `arrow` [@citearrow]: Provided efficient tools for reading and writing Parquet files, enabling fast and memory-efficient handling of large datasets during analysis.
+
+- `here` [@citehere]: Simplified file referencing by creating relative paths, ensuring reproducibility and consistency in accessing datasets, scripts, and outputs across different working environments.
+
+- `readr` [@citereadr]: Simplified the import and parsing of raw data into R.
+
+- `tidyverse` [@citetidyverse]: Streamlined data manipulation, cleaning, and visualization processes.
+
+- `dplyr` [@citedplyr]: Provided tools for filtering, transforming, and summarizing the dataset effectively.
+
+- `tidyr` [@citetidyr]: Enabled data tidying processes such as reshaping, separating, or combining, and handling missing values to structure the dataset into a clean and analyzable format.
+
+- `ggplot2` [@citeggplot2]: Created powerful and flexible visualizations tailored to the analysis needs.
+
+- `ggcorrplot` [@citeggcorrplot]: Simplified the visualization of correlation matrices with customizable heatmaps, including options for labeling and styling to enhance interpretability and presentation.
+
+- `glmnet` [@citeglmnet]: Applied for fitting regularized regression models and feature selection.
+
+- `modelsummary` [@citemodelsummary]: Streamlined the creation of comprehensive and customizable summary tables for regression models, including key statistics such as AIC, BIC, and coefficient estimates, to facilitate clear model comparisons and reporting.
+
+- `stats` [@citestats]: Provided core statistical functions to fit models, perform hypothesis testing, and calculate measures such as p-values, log-likelihoods, and AIC for model evaluation.
+
+- `car` [@citecar]: Used for diagnostic tools, including Variance Inflation Factor (VIF) tests, to assess multicollinearity.
+
+- `caret` [@citecaret]: Enabled the development, validation, and evaluation of machine learning models, including training-test splits and performance metrics.
+
+- `pROC` [@citepROC]: Facilitated the computation and visualization of Receiver Operating Characteristic (ROC) curves and Area Under the Curve (AUC) metrics, enabling robust evaluation of the model's classification performance.
+
+- `stargazer` [@citestagazer]: Generated formatted regression tables for outputs.
+
+- `broom` [@citebroom]: Simplified the process of converting model outputs into tidy data frames, enabling seamless integration of statistical results with visualization and reporting workflows.
+
+- `kableExtra` [@citekableExtra]:Enhanced the presentation of tables by adding advanced formatting options, including captions, headers, and styling, for polished and professional reporting.
+
+- `gt` [@citegt]: Enabled the creation of aesthetically pleasing and highly customizable tables for presenting data and model summaries in a clean and professional format.
+
+- `knitr` [@citeknitr]: Dynamically integrated code, results, and plots into the final document for seamless reporting.
 

### 2024-12-11 scripts/00-simulate_data.R
check file paths and update .gitignore

@@ -5,7 +5,7 @@
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `dplyr` package must be installed and loaded
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `Child_Center_Analysis` rproj
 
 #### Workspace setup ####
 # Load necessary library
@@ -49,4 +49,4 @@ simulated_data <- data.frame(
 head(simulated_data)
 
 #### Save data ####
-write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")
+write.csv(simulated_data, "data/00-simulated_data/simulated_data.csv")

### 2024-12-11 scripts/01-test_simulated_data.R

@@ -7,7 +7,7 @@
 # Pre-requisites:
 # - The `tidyverse` and `testthat` packages must be installed and loaded
 # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `Child_Center_Analysis` rproj
 
 
 #### Workspace setup ####

### 2024-12-11 scripts/02-download_data.R

@@ -5,7 +5,7 @@
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `opendatatoronto` and 'tidyverse' packages must be installed and loaded
-# Any other information needed? None
+# Any other information needed? Make sure you are in the `Child_Center_Analysis` rproj
 
 
 #### Workspace setup ####

### 2024-12-11 scripts/03-clean_data.R

@@ -5,7 +5,7 @@
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `dplyr`, `arrow`, and 'readr' packages must be installed and loaded
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `Child_Center_Analysis` rproj
 
 #### Workspace setup ####
 library(dplyr)

### 2024-12-11 scripts/04-test_analysis_data.R

@@ -7,13 +7,13 @@
 # Pre-requisites:
 # - The `arrow` and `testthat` packages must be installed and loaded
 # - 03-clean_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `Child_Center_Analysis` rproj
 
 #### Workspace setup ####
-library("arrow")
+library(arrow)
+library(testthat)
 
 data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
-
 
 #### Test data ####
 # Test if the data was successfully loaded

### 2024-12-11 scripts/05-exploratory_data_analysis.R

@@ -5,7 +5,7 @@
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `dplyr`,'readr', 'ggplot2', 'reshape' and 'gridExtra'packages must be installed and loaded
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed?  Make sure you are in the `Child_Center_Analysis rproj
 
 #### Workspace setup ####
 library(dplyr)

### 2024-12-11 scripts/06-model_data.R

@@ -5,7 +5,7 @@
 # Contact: minglu.ma@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `caret`, `arrow`, `modelsummary` and 'ggplot2' package must be installed and loaded
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed?  Make sure you are in the `Child_Center_Analysis rproj
 
 #### Workspace setup ####
 library(caret)
@@ -14,6 +14,7 @@ library(arrow)
 library(modelsummary)
 
 data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
+
 # Encode categorical variables
 data$AUSPICE <- as.factor(data$AUSPICE)
 data$bldg_type <- as.factor(data$bldg_type)

### 2024-12-11 paper/paper.qmd
change github hyperlink

@@
   - Claire Ma
-thanks: "Code and data are available at: [https://github.com/ClaireMa0311/Toronto-licensed-child-centers.git]."
+thanks: "Code and data are available at: [https://github.com/ClaireMa0311/Toronto-licensed-child-centers](https://github.com/ClaireMa0311/Toronto-licensed-child-centers)"
 date: today
